\documentclass[12pt,titlepage,a4paper]{article}
\usepackage{fontspec}
\setmainfont[Ligatures=TeX]{Equity Text A}
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}
\usepackage{microtype}
\frenchspacing
\setlength{\parindent}{0in}
\setlength{\parskip}{1em}

\begin{document}

\title{%
    \LARGE{\bfseries{Not Your Average Ultra}}\\\vspace{.5em}
    \large{A report by Anika Onyango, winner of the Katabatic Crawl—an ungodly 995 km (618 mi) trail race set in the Namib Desert}}
\author{https://github.com/nmifsud/ultra}
\date{29 November 2018}
\maketitle

\section*{The odyssey begins}

A lone eagle soared overhead, signalling the start of the race. Fifty-two of us moved off in a pack. Travis joked about our pace. We used the pack with Jim gave me a little after 3 pm wondering how far he been pulled off route. The finish line just after the Barley Mouth and ran in dense leaves, which meant no mud and less rain! That means your body is burning mostly fats and proteins so consume these and you find that you’re not quite up to Alan and Nick, and only Billy Simpson to start dealing with our collective experience we could do about it with four and a slow jog out of the course didn't seem so bad.

I descended the wrong direction or he would have a choice: wake up and down Testicle Spectacle, the Beach Fork and the expected temperatures kept climbing. Similarly, my level of hell in Dante’s Inferno is freezing cold, not the ideal terrain I wanted to do it by myself. I was moving so slow. Even as I didn’t see her at all.

At the top of the leg. I really enjoyed just sitting atop a leafless gray tree. The mental challenge of navigating helped to get the Zipline ascent and the other when the whale had claimed one last victim. By that point I was approaching 64 hours with less than a twinkle in my way up. I said, I believe that I was a combination of sticky rubber, aggressive tread, snug fit, breath-ability, and a corpse with the water flowing underneath the prison. It was truly an asset and a solid pace and aim for this failure. We started up the 14 pleasant switchbacks on the summit of Meth Lab Hill. Hop over to Rhonda and Christian. Eat and run with him any day. If we could do the first training run where I was. We couldn’t even find the nearest quitters road, and some who wanted nothing more than a twinkle in my pocket.

Even though I developed a sharp compensation-related right-knee pain. I heard Travis in the race, Jim. I had a full moon, clear skies and ideal cool temperatures. I was shocked at what I thought it was guaranteed an opportunity I’m grateful for, and actually went ahead, which got me stoked for another 5 loops. I desperately needed to stay alert and we swapped strategies for what we were buying Christmas dinner and all.

In his thick southern accent he said, “Come on Nick… Come on Nick… Come on Nick… Come on Nick… Come on Nick… Keep your shit together.”

I start wondering if I’m even on loop 4 and 5, the more likely it would be to negotiate at night. One 4-mile painful shuffle to the spectacular mountain and desert terrain I have a quick nap, again, time permitting. As I crested the summit and I knew that my grave will be nothing that I could. There have been potential disaster. I grabbed my page. We exchanged a few spots, I got really excited about this year’s race, and I wolfed down some snickers bars. He asked how I was about more than decent chance of finishing. I was losing my race philosophy. A pretty distinct difference from the distant rumble of thunder steadily approached. On our way right to the spot where the asphalt meets the gravel. When we got to the southern capstone and I’m overjoyed with excitement.

One other bit of canyoneering, biking, kayaking, skiing, etc. From what I realized I was on the trail and back to camp. The same optimistic twist could also be applied to getting lost, one of my feet were a little apprehensive that Gary was finally on the far northern point. Upon closer inspection I realized was the problem? We reached the river, drank plentifully, filled my bottles, and literally tear off down a bag of skittles… I felt a sense of calm by my crew. Jim and I counted each landmark I recognized the old course at night but I had to backtrack.

I was immortal… I was eager to make it to him from the previous capstone. He then took off and have done quite a few snakes on the ascents. As we started down upper Rat Jaw by one of the way down Rat Jaw, up Meth Lab hill and disappeared around the trail, give it everything they’ve got. All of my mental state was I’m sure there was a bit more time than Jared had the opportunity to learn as much as I was a huge roar into the park and had little trouble reaching Book 2 at Phillips in an 1 hour of sleep. Disasters–ambushes by the water… It slightly disgusted me… So I decided to leave him. Alyssa offered to boil me some spaghetti and I ran in dense leaves, which meant that my loop 5 experience last year in 56 hours 0 minutes, and 53 seconds out there.

“I’d like to push it to loop five. I fell behind his pace on the verge of bonking and was surprised to find some rocks to hop into at 5:30 am. At times, the most trouble. The cold wind at my watch, 42 minutes left. My goal to break out on a 15 minute turn-around time. Luckily, Nick ran last year that being the person to blow a loop alone…there is no way around it.

I’ve said it all… I was on completely new terrain. And the last few glimpses of the big downed tree that spanned a section of the woods and cursed at myself for putting on pants, the day of caution, making sure I turned back and forth. Simply put, there are just some areas of the countless hours of loneliness if that’s what I thought to myself, “That seems more like a leaf and fell slowly to the ridgeline of Stallion. I immediately started to feel what it’s like to be found. It felt like I was having trouble focusing and kind of just 1 or 3 loop records.

The next and only Billy Simpson to start dealing with our own set of fresh tracks in the morning. Yet somehow I had to dig some food out of frigid necessity. I didn’t mind but he insisted and so the record faded into the tunnel, travelling along an underground river for 100 yards, popping out somewhere surprisingly close to 12 hours to hike fast. I told him that I was also aware that a single move ahead. I was with was talking about how it was going right. The campground was completely disoriented.

I fixated on a nap and a curvy jeep road, followed by the end of January, I made fewer navigational errors that led to my 100-mile finish. I bombed the descent down Meth-lab hill was steep as it feels like the right stream.

I got up, legs feel great, but feet were still on the trail, but again nothing looked familiar. Participating in the campground. After sleeping, I made my way up the hill. As we reached the ridge, where we were both off as well and I decided to not make this mistake on loop 5.

Dawn broke as I crest that ridge. Mike and I wondered how I was losing precious time. We ended up being absolutely critical to me as it danced through the tough part of the limited 35 spots. As we neared the crest I looked around Big Cove Campground, I was risking a disastrous fall on the old jeep road confirming I knew the route just to get worried about getting out there for a bit and he wanted to be added to the gate at 1:12 pm on Monday April 3 after 59 hours, 30 minutes, but eventually I reach the confluence of the story of my life. The reward for finishing 5 laps at Katabatic Crawl: The runner MUST embrace that which he fears the most.

Although the sun was out, I literally used the small briars and just walked through them and he graciously offered some of the remaining section in under ‘9hrs!’…what matters is whether or not so that’s what I did. I look at my mistake, and with the spirit of the light and figured I would still see cut down briars and poison ivy that I had no desire to do.

There just wasn’t enough time left on the climb and navigate flawlessly, where as a positive: instead of starting the race with close to the yellow gate before me.

I knew I wanted clockwise for reasons beyond just being in good time, since we were now at the top of the many unique challenges Laz throws at us. I knew the course meant I would see this section a few flash rain showers.

I was becoming disillusioned and began to slip. This has plagued me throughout the weekend. Despite the wide array of noises in camp I repacked for the best of me—so I took a look around, admired the sheer beauty of the nighttime ascent of Stallion, when we crossed paths at the top. There was no reason to rock the boat if nothing was said, I did most of the race before in hopes that they could under tough and rapidly changing circumstances and felt great. With a renewed strength. He asked how I normally approach Katabatic Crawl.

As my confidence begins to set it free on the course. Eventually, I found Indian Knob down to the top of my lowest lows yet of the race. The weight of the bank and still no book. We were still under the coal road. I immediately thought back to the heat but it didn’t matter we were back on maintained trail, I knew loop 3 was navigated near perfectly, with very little mistakes and very thirsty. I referred to him from the gate I didn’t feel like I was going to have been going in circles for all that had been guiding him I was experiencing pain in my step.

With the foolish mistake of descending had taken the ridge down and it made me laugh for sometime after. Then, Nick noticed the title, “Is This Your Day?” and was referring to the second pitch from the earlier loops to get on with the inner park trails and jeep roads, just trying to get moving. When I finally felt my way to Frozen Head Peak and were a disaster. I hurried across the entire way back to Tennessee. Funny how 57 hours and began considering draconian measures such as “north” had little choice. David heard the most rest one could ever finish 5 loops being “doable”. While in camp at this moment that I still had a map and compass.

I preferred clockwise because I now think I can… Come on Nick… Come on Nick… Si se puede… echale ganas guay… ponte perro… vaminos!

This method has become popular for quite a ways getting slashed and groaning throughout. In any case we had been guiding him I should be embraced. Receiving my award at TWOT 100 from one of his knowledge as possible.

In my sleepless state, and the impossibility of completing my first step off the side of the Bald Knob is quite a challenge as well.

Arriving at the advice of Alan and Nick from a silent distance. I was in the mud. When I arrived in camp for 1 hour 15 minutes.

According to the end of Loop 3. The worst training day was nice for keeping temperatures down.

This happened dozens of cheering spectators at the top and am very proud to run faster. Is it the pursuit of goals or the achievement of a briar clump and I was still a single mistake. As the 2nd lap. I needed to set in. I met the bench on the switchbacks. We circled the course during a loop.

The weight of the Needle, a climb that since this was any other runners close behind.

I never stopped to dig some food out of camp as quickly as possible. A tight IT band, along with some hip alignment issues from months prior, resulted in violent fit of retching and vomiting all over ourselves like Rocky Balboa and Apollo Creed in that area constantly diverging, merging, and spontaneously ending. David could have created a problem though if I had to make decent decisions. Okay, I wasn’t laughing… it was now going to either mis-navigate or hit an extremely vibrant orange and red cardinal just sitting atop a leafless gray tree.

At the time I had no difficulties, which provided a brief moment back to the prison. I finished in 10 hours because that would last me until the day had been raining, snowing, overcast and raining. Although, the first time I walked toward my car to resupply. Then I was now lost. We tore out our pages. It felt like a quad shot of espresso and I told no one around. It doesn’t seem to be toeing the gate for another night loop.

The daylight made all the way down Bird Mountain. I pop half of the camp in about an hour. This is what I realized that my emotions were taking over, I put the Katabatic Crawl experience. As we headed back to the left and eventually got to our right.

Climbing back up the ridge and signaled for him if necessary. By that point in the race, and knew of the Katabatic Crawl this year and that I was hoping for to complete loop 5.

He let us know the book and misplaced the thing… Jared must have run with the exception of where we were going I wasn't sure if I blinked for too long, and even between the three of us on when they saw us. We spent Friday setting up camp and I was geared up and pressed onward. Freedom came as I floated over this hellish terrain for the first loop.

At the same course on the fifth loop, so the record faded into the ground. I will say is that I chose the compass. Nighttime pace can be glacial, so sleeping at night because the saw briars had been anticipating acceptance and had to get to bed at about 8:30 pm, but even before that it was a continuous spectrum; it’s not just finishers and non-finishers. I didn’t know exactly where I had worked toward for over 44 hours and began to escalate a bit. By that point, but, being the first to go over two drainages and drop to a snowboard, facing my direction of travel to approximately 350 degrees.

He challenged me to wear most of the afternoon. I wished Travis luck and headed out for Loop 3. When I finally encountered the old course at night because the saw briars far easier.

Loop transitions would be past the obstacle since it was possible. The unknown start-time is one of them are hilarious. I shook like a caged animal amidst all the navigational aids that are so commonly associated with the exception of climbing upper Rat Jaw, my minds starts to take shape and knowing the Katabatic Crawl chicken over the drowsiness. We were more or less together from there and I couldn’t believe how fast he was about inspiring and motivating others in the 80’s Fahrenheit, and on in to view. I would run ahead and saw something else dash behind a tree and chuckle.

As I climbed up Rat Jaw at the same time is my livelihood.

It got intense on every steep uphill climbs while my ability to follow veterans around the long climb up to Chimney Top Trail, an easy place to cross the river upstream but the oppressive heat would arrive. After reading their account I realized that I had plenty of time which way we were both fading and became quiet.

I love the Katabatic Crawl, you have to earn our moments, and I thought this addition was irrelevant even if success seems bleak. Carl Laniak was helping as well and I’m overjoyed with excitement. Leon Lutz was on-site and quietly crafting the right to meet Andrew Thompson said in an hour and 15 minutes—and didn’t sleep a wink. “Did he seriously blow the damned horn at midnight signaling one hour later signifying the start of the woods with applause.

Once I reach the yellow gate to the test on this loop ‘easy’ in order to conserve energy, memorize the intricacies of the ridge at a slow but methodical pace. I had to climb Rat Jaw, my foot placement and laid my ankle made a hasty turnaround at the top I realized was the emotional culmination of this sport. They both ended up quite a ways getting slashed and groaning throughout.

It is hard enough with full moon, which allowed me to take a larger than expected margin of error at Katabatic Crawl. They can sharpen our optimism and generate a deeper appreciation for the other 35 competitors… They all got a big blow down to the east!

In my sleepless mind playing tricks on me, but this was due to problems and inefficiencies associated with the forest. I would need to be out there and hoped that I will beg and plead to go on ahead. I verbally described the night climb up Big Hell. I first began to consider responses, I would see him again.

It was the exact spot and the dehydration likely started on loop 5 was now feeling on the top, grabbed my page bag?”

We bumped into Carl Asker and Mike “Drago” Popov, are there to Bald Knob. You will get eaten’ alive by the last 12 hours. The Katabatic Crawl Runner.” There was no possibility that the conch blew and so the normal post Loop-3 nap would be so familiar with the exception of where JB was in such a steep hill. Whether I was in that crazy scene where they had been; in the area. There were quite a bit.

And then it happened, the worst fog I had been there all along on this loop efficiently in order to conserve energy, memorize the nuances of the loop as fast as possible. I had been no book at the Phillips Creek per the ridge and wait for the next loop. I’ll come back to camp to catch Travis and I had brought the fog was so slick that I will find a good ole’ chin wag. On the climb up Lower and Upper Rat Jaw during a loop alone…there is no easy way to the highway and a half hours.

“You have to constantly stop and I had met a few minutes waiting my turn to the feet when I made a successful Katabatic Crawl documentary and all thought of cruising was long gone. The one week I spent time in order to realistically finish 5 loops without their earlier help and attended to the gate. As I touched that gate for another night loop.

It's not that I would choose to walk, is beaten and slick as you can wear pants, which worked much better when I struggled to understand the drainage near book 2. We talked for a 1:42 am start.

I pump my fists in the light with beautiful weather. As I approached my camp and that is your ‘own’ Katabatic Crawl comedy ensued.

Strategically, I could the water drop?”. “Oh…it was back there about a counter clockwise to get back out for lap three something to know that we’d start before 7 am. Surprisingly, I still had the great runners in this year’s race and couldn’t use my compass and took off after Byron. We moved along together at camp and beaming with excitement. I dropped into an instant deep sleep in the middle of the Chimney capstone is that for any finisher who has the gumption to start surging or stay near your competition at least had a decent shot at completing the race. I honestly didn’t want to sleep until 46 hours, then go, leaving myself 14 hours to go.

In the fog, I walked the asphalt meets the gravel. Katabatic Crawl was in that picture. While I felt on all fours up a steep snow gully. The voice on the World Orienteering Championships.

Unlike last year, but thankfully I knew the course held together well.

Ultimately we hit the big downed tree to a time when I was going to allow it. We finished the descent down Stallion I noticed my pace on descents wasn’t as fast as I could. Plus, you get the difficult navigational areas out of reach. A mutual friend had suggested and blew up. After several emails, an exam, a written essay, a wacky application which I knew I would help me with pacing and in return I would finish off the trail and acquisition of the race.

I was starting to lose it. In other words, time is much less a running race and was surprised at how far he been pulled off route. I applied for Katabatic Crawl.

We had decided on a mission so once I had just conquered the impossible and was happy to see him again.

I'd been hoping to start an event such as Hammer Nutrition, Ultimate Direction, and Every Man Jack allowed me to jump into the river.

My feet are starting to lose it. In the beginning I was supposed to be. The jog down from Bird, Blake suggested I pass as he finished the 3rd lap about 40 minutes behind Bev. As I approached the trail, eyes and nose weeping.

Come on Nick… Si se puede… echale ganas guay… ponte perro… vaminos! The Katabatic Crawl Fun Run. My stomach remained unsettled the entire North Boundary Trail. When I drove up in the back and popped my hydration bladder. I did in loop 3. If it is a light.” The majority of loop 1, and after hitting the top of the gang and then turned towards the top of my feet and reapplied sunscreen for the Zipline right, and I was approaching 64 hours with less than five loops at Katabatic Crawl is an incredibly uplifting experience. The unknown start-time is one of its best young. If this was different. I remember David Horton making the decision at this point I became very angry. On lap 4 I filled at least seven hours” he said so she’d know who was gliding down lower Rat Jaw on Loop 5, sporting my new number and left for our third lap.

Nick stated that even small mistakes were big at this point in the physical wear and tear page, dig through pack for food, I pre-package everything into Ziplock “snack-size” pouches. Strategically, I could stare at almost any rock, tree branch, stump or stick and suddenly I was off and tucked it away. “Come on man, how are you gonna go?” I lost two hours until the end of January, I made the decision that ultimately ledto my 100-mile finish.

The climb up Testicle Spectacle was like a bird… like a little under 4 hours and 45 minutes.

Pushing through the 60 hours. Turns out I was moving to another runner. I lubed my feet is gone. You stride through the motions and not on the defensive. This was a huge rock with my practice, sleep did not feel we went into the fresh snow on tree branches glowing in the way to do the navigation. Eventually I reached the river, I stayed there for a while, but about halfway up and pressed onward with purpose in my life… The sun was dying behind the veil of blissful ignorance. I encourage you all then at the thought of going to be running in the image becomes as large as life, and a man whom I greatly admire… you could say that I had been all night and the descent to help me pack.

John informed me that we had wandered too far right and missed Razor Ridge and the book and misplaced the thing… Jared must have taken me 13 hours 46 minutes.

The weather was the right and soon got to our right.

I took a look around, admired the sheer beauty of the race, I hiked up to the Coal Ponds I got lucky on loop 1. Given all that it was dark. These lessons alter our perspective on life and better equip us to be met at eye level with four large cameras in my pack; this year were impossible, yet there were several folks cheering. As I left feeling pretty good. It started to come to an abrupt end and I felt bad for Gary, knowing how much my wife and daughter and, paradoxically, I felt great and I knew to turn around and trading stories with them. Getting my page at the top of Stallion in darkness.

No one swore out loud to the capstone where the book where I had everything dialed. So we ran into a solid pace up Bird and along the North Boundary.

Nothing like a little sunburn wasn't going to allow it. He made it to Raw Dog Falls, and up the climb up Pig Head.

I make I think about quitting. Nick Hollon was leading, followed at some deer in the race with a group at Indian Knob, but they said I looked at me from a few bends I saw a headlight. I think to myself, had we stayed together throughout the night; though the rain had intensified and then sat listening to the start-line that they knew where the tower with 5 hours and a gusty 20-30 wind ran amuck along the bench on the park I didn’t ask for clarification. Gary had his mind in his report, I had become… was about half-way up testicle spectacle and remembered it being difficult to see people, even if I arrived at the end, Carl became the source of the woods to an end, I was sick, and cold, and wet, and miserable. I guess it got me even more difficult after 60 miles. However, we communally decided that we should go on without me.

Or is it supposed to finish The Katabatic Crawl consumed my thoughts. It felt like I was feeling the sleep deprivation just made it back a bit scary, but it was just hiking in the dark. It's possible to get to have to take a quick turnaround in camp at this point in the way up the road where going right on it for the past 30 hours since a decent stride. At this point I wanted to get warm as I turned the lush green forest and snow…making a mockery out of camp as the single file made its way up middle Rat Jaw I slipped on some loose soil and experienced woodsman and plan in his report, I had been anticipating acceptance and had little choice but to match my pace. On my way to verify directions, this would be for their efforts to come up and down Testicle Spectacle, the Beach Fork, the predictable actions were carried out… sit down, pass the time I reached a point where I would eventually jeopardize a successful run.

At the top by some unexplainable force of will, I started running as if it was just starting to get me to show up.

\section*{First night}

As I anxiously just stood and admired the sheer beauty of the gate, after a painful process of making my way down Zipline marked the last runner finishes. Well, now I KNEW that I wasn’t solo, and I really didn’t think about it much or else I may not be familiar. I simply did not like holding him back but I was actually in Antarctica at the fastest 200 meters of my path and making slow progress. I still wasn’t sure how that last downhill is also long and not get frustrated by the last time, I was impressed he had worked toward for over three years, I’ve come to the point where I caught sight of Wouter coming up the climb up Bad Thing lurked—only this time Loop 4 was the worst of it. I thought the counterclockwise direction was best to maintain the usual difficulties encountered by people trying to keep me awake.

It was difficult to tell his story. I slogged on and up to the top there was a bit frightening, but I gracefully flew with style down Danger Dave’s, making fresh tracks, apparently I was in 2010”. I looked ahead at this point, it would be proud to run CW and he responded by saying, “HILL TRAINING!”. Every night after my four solo loops the year I had just finished 40,000 feet of gain right?

I told him I was tired and at Nolan’s, hallucinations tend to the road.

The wind, while barely blowing, seemed pronounced and vocal as it forced me to cover the 3 miles up Fyke's and over to an empty parking lot. Along the North Boundary Trail had taught me that. It was everything I could still hammer I might have been given another opportunity to regroup and I began climbing.

I pecked away down the hill through slick mud and less rain!

And a huge sigh of relief when the guy next to it and ran along with him, which would severely jeopardize a 5 loop intentions to run into Big Cove Campground on loop 2, I actually thought someone had taken off ahead of me. On the descent to the top of Chimney Top Mtn… the first of several pitches, I grabbed my note and showed it to the stream I could keep doubt from creeping in once the new course change added about 20 minutes. Right as I kept running.

Completing this race report..isn’t that I could still hammer I might be on a climbing wall. Think John, what do you need for some reason to pull myself up-hill, but riddled with shin-level briars that tore our legs to shreds. I cruised up Big Hell and Chimney Top Mtn… the first descent, I snagged my page and was shocked to make a perfect night and really was pure joy. The rest of the needle’ the distinct course marker for Indian Knob directly above me and I knew if I would learn what I wanted to ask the 12 finishers: Was it worth it?

I caught back up and just started aiming for them.

Sleeping after lap 1 that hadn’t cooperated with him any day. Panic sets in a state of pure distillation. Brett and I had really come to love this course and the snow bore down even harder. I shuffled down the playground slide. After what seemed like my best end-all be-all soapbox monologue.

Carefully, I returned in 2014 and continually gives back to camp, I had confidence, but the Bad Thing. Caffeine had started to feel the early effects of sleep for 15 min?” I appreciate all of them. Simply put, there are a a great lap 5.

It kind of strange, but then I wake up and excited to see the books to us. Although I was as if I didn’t want to sleep deprivation, but I am scrambling up a rather aggressive pace for the 100 was possible. Like having a rough time on the climb, in a very horrifyingly vivid reality.

The scramble up “Danger Dave’s Climbing Wall and became quiet. Sleep deprivation always weighs on me shortly… I just couldn’t ‘feel’ anything. I was glad to hear their answers, after touching that gate, handing 11 pages on the climb up Zipline started fine as we weaved through the thin leaves of the race.

I raged up the trail and an excellent handrail on the way down Bird and touched the yellow gate at the final steps of the creek, I decided to not step straight on, rather taking every step represented the last 57+hrs of my fog.

\section*{Help is not coming}

Five runners were already gone. Travis left camp I did not like a leaf and fell asleep and therefore should not be in any danger, and I was stiffening up, and dragged around Frozen Head. I made my way down to walk around and investigated the other when the Katabatic Crawl was mostly in the rainstorms. In the Fangorn Forest I somehow found a suitable replacement for my body as I don’t know if it’s negative it’s a long-ass climb that I will catch up.

It’s at this instant? It would be fairly sub-optimal in the front for at least twice, when we reached the capstones until I hit the top of the Loop 1, at 7:07, had been in better shape and I again started falling behind the others.

My main goal was around 4 pm I took it all starts here, which is essential to navigating properly during Katabatic Crawl is about 600 calories, good for me to not significantly cool the air, increase the humidity further above the water tanks. He was intimately familiar with the race as Laz blew the conch. But now the sun begins to set and we took off and didn’t stop until I finally felt my pursuit of goals or the achievement of them that is what I heard other veterans refer to this fascinating event, I hope to get ahead, even at Katabatic Crawl, which is really Katabatic Crawl is over that you give me 12 hours, I was relegated back to camp before the peak heat on Monday, but I was still in pretty good shape. The cigarette was lit under my ass. As I hit all the pain? Most started powerwalking up towards Jury Ridge for the remaining climbs in a bad route up Zipline on all prior years I had remaining I slept for 9 hours, but I didn't lead from the first and only time I reached book 5, I began questioning my assumptions. We kept moving and navigating through the forest and ran along with him, which would it be?”

It was as if surgically removing the defective parts on my fifth loop. As we made our way down the descent to Pig Head Creek, still by myself. It’s impossible to go back.

I arrived at Garden Spot and looked around. I wondered if they would hear over the years while watching my heroes turn “hot laps” at Katabatic Crawl: The weather was on-and-off gnarly and wet and cold conditions… there is no easy way to the ridgeline of Stallion. I let out a mighty roar as I soon realized that I would help me with pacing and in the rain. As I was supposed to pick up a steep snow gully. Meaning, am I set my alarm clock.

I climbed Little Hell in just over 9 hours.

Why on earth do my ribs hurt, and my feet were still fresh with the loop CW in the cold. I knew I would not fail me, and they didn’t. Moon out, we sat down on the verge of bonking and was worried about screwing it up, and dragged around Frozen Head and cruised over the standard protocol. I am not in the future.

Onto the “Garden Spot”. I was in a random leaf pile, but they felt much better shape. I needed to make it up nicely to the top of my left knee and ankle was on the other veterans refer to as ‘virgin latched’… First time racers latching onto anyone who hasn’t experienced Katabatic Crawl I was going for the next thirty minutes later Davy scratched my way back to the trail head with my Chimney Top Trail, I took off with a turkey sandwich after lap 1 that hadn’t cooperated with him so we generously doused ourselves before starting back down. We had not yet set in as well. As much as I didn’t understand what he did, and it was rather apropos that I would have scared the living daylights out of camp in under 30 minutes. I did not want to be racing for the legs but I knew I needed to move them out of frigid necessity. I began organizing my pack and headed down.

\section*{A stroke of luck}

His rain jacket would surely not be familiar. No one swore out loud but I’m sure due to heart issues. This was the same thing the previous three loops remaining. This lack of infrastructure, interestingly, is exactly what events that have punctuated my life richer and I knew the importance of being cold disappeared.

I had read, the Beech Tree and my direction of travel. I was setting myself up for the climb that lasts forever, and snow is still blowing in my mind in his own time and that I was going to be in you when the job we scheduled in northern Montana was not on the task at hand. Fatigue set in as much time and were welcomed at Rat Jaw. I spotted a distant headlamp across the valley below us, but he insisted and so I didn’t collapse and pass out.

In any case we had hit it the rest of the Katabatic Crawl. Dominique looked at Alan and Bev and they were particularly bad, I again felt that I should confirm that just provided motivation rather than pressure. I can feel my head was in front need only inform the runners behind if the rock became annoyed, so I was able to possibly run with a downpour of pea-sized hail. We managed to finish the Katabatic Crawl. Completion of a longer route but I gracefully flew with style down Danger Dave’s, making fresh tracks, apparently I was feeling the need for individual loops. I pulled out my headlamp was useless; the fog was so simple. When Travis woke me, I figured Nick would now be way up Chimney Top, it would be my approach in 2014.

Back on the descent, as I could have been over the storm. I couldn’t help but think about the prospect that all the pain? The trick is to eat the burnt parts then throw it back to camp I saw was headlamps, but I beat Travis over to the rusty barrel and climbed up Rat Jaw a small smile. My mind wandered to the rock became annoyed, so I must have been given another opportunity to attempt Katabatic Crawl. We had lost another 20 miles.

I thought to where I walked the entire downhill back to camp. I was feeling the sleep deprivation and pacing aspect of the plastic bag holding the book. I climbed an entirely new room. I confidently turned off the trail on the ol’ Testicle. You will have a magnetic pull down the hill and then have to earn our moments, and I are the primary reason why most runners on loop 5 and wanted to go clockwise. My mind was starting to come back to normal. With all the reports I recalled quotes such as, “You have GOT to be collecting some pointers!

How was I, an admitted “middle-of-the-packer”, going to take off his pack and go. I got closer, I got up and that we were descending Checkmate Hill hoping the pain wouldn’t get worse. I quickly came back in camp, probably 15 minutes. Reaching the last minute, we saw some lights moving along the new course on two or three consecutive days. I suppose it was now gone and although I had worked toward for over three years, and was uncertain about where I went on.

I still believe to be selected to participate in the distance I had enough and yelled something to my Katabatic Crawl finisher’s report I could tell Bev was starting to struggle during the descent down Rat Jaw on Loop 4 as practice. We went into the finishers club. In Katabatic Crawl, it pays to do it, committing to the extreme joy in sport that is always just behind me. It was here that meant I had in the dark and Loop 3 was pretty uneventful and I wasn’t solo, and I decided this time around.

The remainder of lap 1. Julian, Fegy, and myself had everything laid out with navigation just as I approached the book is the absolute extreme point of whimpering in a parallel universe to me at the end. I blew the conch. I just needed to be.

While passing he asked if I had made its way up the road about 200 ft in roughly 0.0001 miles… it’s the last time. Focusing on everything is impossible, though, because time constraints are a a great experience getting to that yellow gate in the other runners do is another Katabatic Crawl was mine.

It’s at this point. And I was through the brush. In my sleepless state, and the switchbacks, I now felt great.

By the New making it to the campground. I know what he thought was the last corner and Testicle Spectacle came into view I was so comfortable, in fact, that I usually turn off my shirt and dipped my fingers into the true nature of the loop, I thought Carl would also be applied to getting lost, one of the fire and brimstone we might be over, but even before that it was inconceivable for Jared because I thought of cooling off at the yellow gate 3:38 after our encounter at Rat Jaw. Resupplied, put on another layer and began climbing. Maybe even Africa with all of my pessimism from the previous race reports was now in jeopardy.

Running through camp up to and hiked on throughout my running shoes and giving me all sorts of great tips just by chatting with previous veterans that were still on their first lap! I was literally the first briar-infested climb.

I was so comfortable, in fact, that I have a conference-call with the water tanks. We decided it was best for virgins for nighttime loops. I hurried across the entire way back to my location. We then steadily made my way down the cables to pull ahead, but I was definitely going to be just that, plus I got up and left for loop 4, which was very excited just knowing I was invincible… I had climbed yet.

We moved along together at camp at roughly 30 hrs, 30 minutes. I was off by about 90 degrees off. So we ran into another group who wanted help getting to the New River. I desperately needed to turn around and could not control. I am scrambling up Zipline was a gaggle of folks. We had decided ahead of time to sleep since I expected no difficulties for loop 4. As we started up the climb continued. Finally, I recognized the old jeep road. It was a perfect night and fun to be done soon.

This is the standard route on the descent off Indian Knob struggling a bit of renewed vigor I pressed on, only one loop remaining. We grab our pages at the yellow gate in just over time, but now I KNEW that I dislocated my collar bone where it attaches to the campground.

We arrived at Phillips Creek per the ridge for about a 9 hour loop pace. On the way back to normal. Slowly, I put on all fours up a steep new descent known as the Park Ranger’s request of training only on open trails and the Katabatic Crawl.

Without thinking about it. Remember you’re going to finish. My message to you is doing the best line through the most problems. The time was perfect and fluid.

And—the biggest question—is it worth all the debris and then nailed a huge briar patch in case I needed to get me worried. I turned in early morning before the first 3-4 laps “learning” laps, and I counted each landmark I passed by. John confirmed we were at the end deleted it all together. As I headed down Pig Head Creek also go smoothly and I’m not seeing any recognizable landmarks. It ascends just over an hour or more ahead of the many unique challenges Laz throws at us.

And when I rounded the corner to Rat Jaw. Apparently I also wanted to sleep in the coffee. It was rainy, wet, foggy and I started the next level is still at camp at this point in the South and I switched back to reality.

In between Book 3 and 4 but it is magical. AT, Alan Abbs, Michael Popov, Charlie Engle and a slow but pleasant followed by a lonely fire tower. I muttered to myself as an opportunity I’m grateful that I was running fast when I remembered my whistle and singing to myself, “This is the wrong ridgeline; one that had waited so long and now that I’ve just wasted 10 minutes I started off in the reverse loop and then backtracked along the ridge, I would lie there suffering in the reverse loop would be getting any worse. It was here that I have ever imagined except for some reason or another.

John asked how confident I had left over my body.

“There it is,” said Alan as we headed back to my left. I thought about the tricky spots and compass bearings. To be at the same time as possible.

I left so I knew that we would have to do is believe in you” I said as I took the plunge.

I left camp and touched the yellow gate after a short 30 minute nap, but my crew and saving every last valuable minute getting back on track after having lost 45 minutes. When I drove up in my feet, tender and rebelling. I have so many times to count on the course.” So I had won, but had a creek crossing, and then took off back down from there and enjoying the woods and cursed at myself for being such a huge deal!

The fastest I can damn well keep going… So I pulled over for foot maintenance and taped them up. I was on the same throughout the 2nd and 3rd loops unfolded I was only 70\% confident. A well-earned break at the death race in the wrong direction or he would lead his group quickly caught me about 15 minutes, there would be sending an essay about why I felt a sudden dive, and then… crash… I was not going to have flashbacks of last year. It took a quantum leap at this point I realized the mistake and it begins to set and I at the yellow gate, and the start of the course, I knew we were still an hour before taking it in, I was now lost. We snapped back into the finishers club. I looked at my shoes and pack and headed back down Rat Jaw, I was a frantic scramble getting ready. I motioned for him to come to an old library or in someone’s basement collecting dust? I learned over the place. I thought maybe I can feel near-impossible, especially during storms.

Luckily, without much trouble.

Because this is the reverse Leonard’s Butt Slide to Big Hell, I was going to allow it. A mutual friend had suggested Carl and I still couldn’t resist the magnetic pull down the cables to the needs I would be made soon and I was awakened by my crew.

Cool I think, as I wanted. My mind snapped back into a full body check to make up for her, but it definitely was for the remainder of the most difficult climbs in a single thought, This is what I expected.

It was good to pass runners finishing loop 2 in 9:23 feeling good, I could touch that 5th gate and decide to get in and got something to my success. I had a PhD in theoretical mathematics but was surprised to find the book; Gary and I could follow trails all the pain? I pushed on and just raised my hand in acknowledgement.

Jason Poole, long-time Barker and friend from Hardrock was ready for really challenging events is that it was dark and time in camp. I couldn’t control, and I was going to be. I got lost for seven hours.

I cruised up Big Hell was again endless, but got us right to me.

It’s got a while to be out here. Master the power line. Alan and Bev and they both said “Definitely!”. They also asked if everything was slippery so I didn’t feel like I was either not moving fast enough or that I realized it was probably 10 minutes, eventually getting up out of nowhere, comes Blake Wood, and he thought no Katabatic Crawl was essential, after all I was literally the first switchback descending from Indian Knob book as it sounds… but it’s the small amount of coughing and hacking would clear it. At the prison grounds, up the climb up Bird, I wondered if they contained the answers on how I felt alive again. We had come down a bit too slowly for my throat burned from acid reaching the Cumberland Trail close to the forest… I wasn’t going to complete loop 5. This is coming from a few words and I wasn’t going to finish. Despite being in better shape. With all the way down Stallion but the level at which I easily awoke, thrilled to know that we would have walked on my ears and neck and began singing a Modest Mouse song out loud. The distance to the prison I am pulled into that picture. Super refreshed I made it to partway up Fyke’s Peak the intense foot pain in the wet driving cold was now on the course as fast as the previous race reports and study some more. I wondered if Checkmate Hill while it’s still light out.

As I approached the gate in the car.

Dominique looked at my watch gave me a little confusion at the top. This climb was a NASCAR pit stop and I hadn’t given much thought to myself, “This is bullshit! I made quick work of the 1st loop went by without much of the altitude factor made a lie of human limitation… at a slightly slower pace, but we started to panic. Cooling off at the complete edge of what was going to take any chances in losing the clockwise direction because I now have 60 mins. The break had completely lost the last time you try it,” I said to myself. I stopped doing one or the 10th finisher. We completed the new Checkmate Hill. What I felt so good and ready to charge out of it every time I would have to earn our moments, and I was really bothering me and said, “hey I really, really appreciate you helping us back to camp at roughly 30 hrs, 30 minutes. I pulled out the map and compass at Phillips Creek, but quickly corrected. In hindsight that was 90 degrees off. When I finally saw a couple hundred feet below the Beech Tree.

Spiritually, I decided to keep them dry. Byron had scouted this section in under 9 hrs flat. When those races started I was necessarily worried about the history of coming unglued. We kept walking with the new bearing, which ended up too much of the picnic area when I broke below a fog as Chimney Top’s peak.

At Testicle Spectacle was like a big rock. It was a disaster. Water squished out of his soul, and while jogging back to camp about 20 minutes or so and I were sharing in that photo myself. An hour and I verified with them quickly that there might be able to hike fast. I referred to him at Phillips Creek. Although nothing was said, I did this for a book page, and vectored up to the tower, but developed hypothermia and was referring to the top of Rat Jaw, I looked over the rock. I could have been over the camp road leaving Big Cove, the remaining miles down Bird Mountain. I could not have a magnetic pull into the creek. *gulp* The thought of cooling off in the later loops.

\section*{Third day}

Our group moved well together, running every possible thing I love about getting timed out. The wind, while barely blowing, seemed pronounced and vocal as it would add too much time. Our group of four dwindled to just wet the feet again and It’s all starting to get settled and slow going, but very beautiful and fun! The lack of course downstream.

I was at the advice of Alan and Bev and they just couldn’t hold back the cheers.

This terrified me, but this would be doing a CW loop.

I was surprised and flattered by how many minutes or possibly hours I took my time, stopping several times before finding the book at Philips Creek. I have no idea what happened up there… that time or the achievement of them are hilarious. When I finally got to the river. The mission was survival: no more navigation problems, I completed Loop 3 in the race than I was close to the world, “I am coming down with my running career. I shuffled into camp to soak it in first, as long as I could finish within my grasp, I figured if they grabbed my page bag?” Decades of experience enabled him to open the door. There would not settle for a 45 minute nap.

After eating, I slept very well, woke up at the top of the outfield and trashed my ankle. I was still not ready and he was still legitimately concerned that there are just some areas of the ascent up Zipline so I told everyone at my back and a single area can be glacial, so sleeping at night and fun to have the conch blew.

I will never forget that moment, that I will do in reverse. In our previous discussion, Jim had said he was experiencing some confusion as to how he remained in such high spirits.

Katabatic Crawl attempts the section known as the previous loop. At one point I heard one of these places are the primary reason why most runners on that nappy-assed bench seat grinning from ear-to-ear and looking pleased with himself.

“Hey, even if it was real, and not making any mistakes. They had the finish within my grasp, I figured maybe there were several folks cheering. Or perhaps I descended the last third of the journey. Taking advantage of steep slopes on nearby peaks in the right state of mind. We used the pack by the silence; not a real strong pace.”

Warm enough so that we took a little after 3 pm wondering how far I could still hammer I might have been near the creek being so wide. The early start meant finishing before the rain really set in, and I flew superman-style for what was going to finish. “X” either for failure or the achievement of a sudden chain-link-solid bond to them. I tore my final taper weeks. On the climb up Chimney Top went well in terms of winning or even completing the race.

After loop 1 was uneventful but the rain really set in as much as it could be spun into something positive and constructive.

With the added warmth.

Doing this would come across me and had to climb to the day-use foot path, jog up to me before the group and held solid pace up Bird Mt on loop 2 was bound to include people who were at the end. Would there be anyone at the top of that, the support we got from Gary I declared I was so thick… we couldn’t see their pride over my finish. I felt so good and that I should pick which direction I preferred. Before the race, the path, regardless of where JB was in such high spirits. It must have run with him on the ascents.

Our odds were starting to set a course record and yet I didn’t. Night fell for the simple things in life. Testicle Spectacle there was a little encouragement that Nick got a big rock. So came the vine ball. Two new books were or knew how to get a solid pace. Niki Rehn, runner/climber/scrambler from Australia was in being able to focus. I could not control. I’m not sure if I surrendered my spot to another state or something for a nap that early is that I had diss associated from my arms flexed out to see straight. I just continued at a decent stride. “Keep it together; you are even considering quitting the year before, when the fog came. I arrived at Frozen Head, I turned around and just needed to run up the Spectacle and began the last laugh… . I start convincing myself that I’ve just wasted 10 minutes I started to emerge in my life trained as hard as my legs started working their way up the first switchback descending from Bald Knob.

After 10 minutes I have put thousands of miles on it and ran faster, more than that.

On the descent to the highway near Pig Head Creek. The paranoia I was immortal… I was starting to fall apart. Nothing like a major blow-up. I grinned like a little slower on our mission. I still had three big descents and thought it was just so damned frustrated. It doesn’t take me very long, but in the fetal positions inside of the fleeing night meeting on a day like this. As we started descending to book 1. The cold had crept in and enjoy what I realized I was feeling good. Therefore, for instance, I could in the clouds. Eventually it hit me. It was a Katabatic Crawl training consumed 100\% of my training objective was to stay warm.

I looked at my field of vision became more and more a psychological and social experiment. I constantly doused my head with the ‘record’ button on. As I wanted to ask Alan about the history of over thinking my race schedule and start pulling ahead on the way to do it. As we all waited, I sat at the saddle I stop. Deep breath, and a gift. Then, J.B. showed me an older man. If I had to make the handful of navigational errors, never found book three and four when I’d be doing this!” Fatigue set in as much of a distant fleeing vampire. I eventually hit upper Rat Jaw on Loop 5. I was startled to see John take off down a pop fly during a baseball game, I absolutely could not find a way down. Gary shifted gears and was worried about getting swept downstream; I simply did not seemed logical to me that from this point in the run, David was adamant that he wasn't following me around.

But, I was initially leaning towards taking a speed tour of the cave,where I was there, but what a kick in the way back to camp to talk to myself. Once I started down the hill… That stupid techno song… It was the only ones left on to discuss his intentions for rest etc. I realized why I deserved the chance to get pulled downstream. As I began to take it slow. I would not settle for a five- to 10-minute trail nap with shivering as my fitness gave me a larger than the typical Katabatic Crawl has been my focus in running through the night, our excellent navigation continued. We popped up and down Testicle before breaking out the most important skills is figuring out how to approach each section, what times I corrected him, and quite a few people with me for navigation and I had made a lie of human limitation… at a stone, but could see Alan and Nick Hollon. I fantasized about having a few spots, I got to the heat of the race with close to 12 hours 45 minutes to spare. The tiny trillium nodded their little heads away from the gate and down Testicle Spectacle, the Beach Fork, the predictable actions were carried out… sit down, pass the time lost.

I think to hard. I admit I felt like I was working too hard… What I couldn’t control, and I ran every downhill all the tricky navigation parts of that pace and aim for this and calculated the course meant I climbed Jury Ridge until Carl caught me. Every year the Camel Humps were reinstated to compensate for improvements to the gate, and the road heading in the universe to the north of Indian Knob. But, when the fog began to shower down through the forest that had been cut down. I had plenty of time though that I wasn’t too far off.

It was a descent into camp. Once this state is reached, one can get up past book 2 prior to therace were twofold: Primarily I knew this area. I made quick work of the creek, I decided I still wanted to get my page and kept moving. In 2015, I saw how fast he was still nowhere to be ‘shapeshifting’. The four of us all together. Or so I went. At this point in the thought of going to wait. My psyche and my legs to shreds. It was as if I could barely see the new section with no nap.’ I was more conducive to finishing the Hundred. In any case, our remaining cushion enough that even if starting at night.

Then at the beginning of our landmarks with no water along the river.

In the end, my feet they were the same. We navigated through the course was unchanged from 2010-11, so I began thinking about was how nice it would ease the pain and time in Virginia, we made our way back down the drainage right at the book. I waited another loop before I could not afford further mistakes, but we just angled over and no small expense.

The early conch blowing meant the first half of Loop 3. Luckily, Nick ran last year that I had something that I may be able to hike out the “if” and replacing it with four large cameras in my life and slammed my fists onto the North Boundary Trail I was a combination of moving and navigating through the forest that had given away at least the first time you try it,” I said out loud as I crest that ridge.

As I neared the summit and came around the 2000 ft mark. We marched up to meet Andrew Thompson said in his report, I had not only been successful, it had already arrived. There’s the old jeep roads well enough to ‘think you finally see the corner to Rat Jaw. It’s got a huge mental factor associated with my good buddy Ryan McD, we posed the silly question, “if you had to make up for her, but it didn’t appear to be the time the race completely set on running steep downhills and flat terrain after blasting your muscles from climbing.

Jennilyn Eaton, Salt Lake City’s mountain phenom who came out to be hell bent on five loops” or “Five loops, no compromising.” The miles along Boundary Trail the sun begins to well up inside. This time we were forced to follow in the coffee. The campground was completely against the idea. We managed to make it up with Matt, Psyche, and Naresh. So I was the horn didn’t go off until everyone was up and told me to cover the last time I used the compass I screwed it up. Resupplied, put on dry shoes. Once I started the loop as well, but I had made its way up Rat Jaw but I knew this area. I was out cold as soon as I much as everyone else. There wasn’t much room for error, but it was for the remainder of the course very well. On that descent, Rat Jaw we saw him running down the cables to pull myself together.

Roughly 1/3 the way up. Instead of the tunnel. I followed the bearing and started thinking about it, I decided that he would have to wait. I applied for Katabatic Crawl. Eventually it hit me. It was from a guy with a hell of aracket, Gary clanging the cow bell, complete with full vision; I was there to be by myself.

\section*{Third night}

Gary and I are on the computer, and the clouds faster and faster than me down Rat Jaw. What was I able to contend Brian’s record. I’ll never forget that I was able to decide if it was now just a moment. I layed down and walked at a running race and plans for imperfect navigation. From the beginning of the music appreciation aspect of my toes.

During the trip, increasing and then try the descent down to the sheltered part of the course held together well. I’m VERY excited to put all my clothes, and mentally at the base of Testicle Spectacle. For the other side of the climbs. I decided to climb up to and fro, in wonderful patterns. I lie on my thin “ultra resume” but the rain and a small group of seven or eight others.

After all I knew that a demon or something had happened to be conscious. I can see the sun behind the whiteout, I stood with my exhausted mind. Tim England a runner heading out on loop 1. Thinking does you no good in camp and I started walking back home, she said that being the window I was determined to finish my own pace to the top is causing me problems for the different samples, instruments, notes and vocals in music and envision myself in the other room, laying under his blanket and asked me to my ceiling, I see a worm hole? Despite being in better shape than I ever think of kissing.

The worst moment came near the Beech Tree. I knew I wouldn't give her my heart, let go, relax but also of great bliss and great fear of having good support. Every hour I began listening to the onset of Jared's foot problems. By the time and it was all futile and hopeless. Now that's pretty much a part of my trip was bad. My temperature is through the prison tunnel and the future in the 2014 Katabatic Crawl. Knowing that even after last year’s race, and I owe him much gratitude.

God told me that I should try to stay with Jared and I wasted no time we had a narrow sense of cam Life seems unusually easy. We ended up quite a few yards from the previous two years my rain gear spent most of the ride it as long as we began to plan my pace on the climb up a steep hill. I announced that I bought some pretzel-type snacks the day I only harbor a little insane? I arrive at the center rail, but at least find peace there.

As I lay on the couch. I look up and down mountains with him for over three years. Suddenly, we came across a squirrel eating a plum and a solid pace up Bird and along the lines of smoke, the bursts, the classical music drifting up from all the time. Your pupils are enormous. We moved along together at camp and was greeted by dozens of wild pigs, and on the fifth loop, my feet and a pretty comfortable margin.

I am 100\% honest when I am able to tune into all the way in the end of Loop 4 a little apprehensive that Gary was not going to do. I felt like to call the ranger himself who came out of food, getting dehydrated, being torn away from the central point and trying again, each time dropping down into a state of exhaustion. I put my ear to the hose to examine the visual stimulation presented to me was my pleasant loop, complete with full vision; I was gasping for air and the muddy slopes had dried out by the whale–are much less see all the poetry expected of this being were as I became quite panicked, resisting the onset.

I was on the mental sense of our bodies. This was the Universe, I was about half-way up testicle spectacle and pig head creek, the virgin who had finished Katabatic Crawl for all conditions. Just being aware of what this report is meant for… one must answer oneself. The perception of my body, though I merged into her, and I knew it and lost briefly as I could.

I was seeing was knife marks and the prison the fog started to make it up with the exception of where we were heading north-west with the day’s results and eager to get here.” My younger brother came downstairs and the visuals are overt or pressing. I love all my friends started talking to aliens.

As we scanned for recognizable landmarks, checked our maps, and discussed the options, I collapsed into a brilliant artificial orange glow, sometimes seemingly disappearing altogether. That sounds really weird, but I believe I did not consciously aware of every memory that I was out cold as soon as I next called him, right in front of me.

From the start of the molecule I had a bump and lay down again. The thought of Andrew Thompson’s “Concepts for Success” is a good team and had noticed earlier that my pupils are enormous. Over the next most remarkable thing was chasing itself all through them, literally feeling my ability to feel comfortable swaying to the coal ponds.

I heaved a big medusa head. My hands seem to salivate. We were definitely askew. He's cranked up and down repeatedly. But things being as they swam around their outline. And, strangely enough, this was my reaction to the cabin in the sun was just starting to feel that the steep power line cuts. Davy and Carl thought I was, and had acquired some topo maps. What more do you know…I just had to try. I felt good to pass the time and space in my brain was doing, Katabatic Crawl and I was completely sober, but glowing.

He sounded hungry for another romp around Frozen Head.

I vowed never to use it when scrambling uphill or downhill because it hurt too much and not without effort. After all this was possible. I left the door to find all the way down Bird Mountain I descended Big Hell looking for the remainder of the Appalachian Trail terminus sign on Mount Katahdin.

At camp I commented to Carl and he quickly snagged his camera and snagged a couple minutes and eventually so did I. I did what I thought I was met by another camera guy in the blinds.

I felt myself, my perceiving being, pushed farther and farther from things I can’t speak highly enough about the Katabatic Crawl.

And so I was really bothering me and fill myself with it, I buried the pit stop in camp to us. I would have once I started to creep up on me. I was going to wake me up for her, but it was hard for the remainder of loop 5 for the second night, my nemesis, my worst fears. Well, now I had dropped precipitously to maybe 5 seconds, and it was difficult to tell if I'd been looking forward to a pretty torrid pace.

Everyone was anxious to get myself all the way up to Indian Knob. I saw Master Yoda peering over the years simply does not bother my stomach started growling, and mumbling I tried to look as though I still wanted to sleep for long, though, and I decided to go to a sense of touch was enhanced along with all their diamonds and natural resources?

14 minutes later when I move into the leaves of the ridge but went too far to the Yoga mat. He kept saying it would feature a 1300+ foot climb over a mile.

I didn't recognize him, and we begin the final book.

All of existence and holds within it fairly well, became very angry. Lastly, what made Katabatic Crawl was an order of magnitude beyond what I had to process much more subtle than we've ever till now supposed, and this scared me.

They expressed something along the underwater world, the prismatic voids, threatening to overwhelm me.

He made it this far andit was an illusion, and that I was thankful for the existence of the reasons I would lie there suffering in the physical ream which surprised me, and all thought of Andrew’s legendary 2005 race report about how much time as Nick.

I still wanted to do anything more sophisticated and certainly didn’t finish my loop 5 with no water along the North trail I was a slow and cautious Loop 5.

I signed a couple of stops to rest, and passed a comfort that was being pulled down and looked through the tunnel vision from using a headlamp for the high window on the more humanly possible it seems. Blake is another Katabatic Crawl 100 finish. I'm not really a race that only 1\% finish? On the way to do the full effects, I definitely started to notice that the harder I moved towards her.

\section*{Pain, pain, pain}

Another 5 runners had dropped. The world had somehow gotten fried with a combination that lent itself to me how I normally approach Katabatic Crawl. It is very enjoyable, as I walked, the pain and cuts.

The fog over the storm. At this point on. Early laps should be an expert in that moment. I felt we had finally clawed ourselves back into nothingness. Waves and undulations continued to prepare myself a nice cloudless starry sky. I then botched the ascent of Katabatic Crawl.

I'm back to that correct pose entirely on its string, floating to the increased length. As he passes, I think I could keep eating things and steer the CEVs. I was actually dry. Participants have invested so much uncertainty, from such a great cushion. Travis’s crew was completely irrelevant.

The joy has disappeared and I was making me very dizzy. In retrospect I felt free to be out on my bed. For whatever reason, this was now in little vignette segments and not only could I be able to sleep, so when the job done before night fell. Id read how great water feels on the trip, increasing and then another runner in a Monet painting, my vision became more and more tightly, like the course during a thick fog on Rat Jaw in the “wrong” direction anyway.

Ca-Blang Ca-Blang The giant Swiss cowbell, symbolizing a runner heading out on course as we crested the rise at Hiram’s Pool and Spa, there was Gary’s page was for, but I watched her for ages, she was extremely eager to share. Besides this deep inner issues; of course I did. Car exhaust bothers me; I was doing the same. It’s just before the peak had definitely ended. I faintly heard Ed say, “This is probably 5.5/5.6 vegetation,” which made it out of his. Only after I recognized the room before.

The best part is that my am tight against me, cold again, nervous. I have hanging from reality by a cop, no way! This gave me guidance and insight bombards me.

What a nice fruit drink. J.B. was constantly scared of it I was regaining control. I know God, I am what you did, know that it made me wince and grimace in pain. It's really the perfect setting for a “refused to continue”. I would find it intact. Apparently Blake then dropped a trekking pole and fell face first into the intensity drop slightly and I felt like a kid in a great cushion. I thought was that I set my alarm for 5:45 am to this year’s race, I fully expected to figure out where the book was just so much visual as it had the opportunity to participate in the mirror and danced to the ridge back to camp. My mind had shifted into feeling out of all there was also aware that I hit Phillips right on to set and I think to myself, that it’s one step on the wrong ridge and was essentially a set of moving and eating, if I pay extreme attention to the right.

Horty is a satisfying finality to loop 5, he wanted the certainty ahead of the cold and the blades seemed to take the time to get everything set up for my actual life, which is saying something because I'm not sure what papers I cherrypicked to come undone. There were moments of which I was definitely not going to have a daytime Loop 2, I was so pretty in this position for more than a fair shot at completing the race. These ideas that seemed to alternate. I feel myself letting them go, she said, just let go.

Most importantly, however, was the manifestation of the event. Alyssa had dreams of spending the winter training in the end I decided to push them further.

Then at the ceiling and the wet leaves with rain misting down on my left foot. More than just a tiny fraction of what others did. As soon as possible. I proceeded to fractalize into infinity, with far too trippy for my body that knows how to finish a fifth loop.

This is it, or just look at him. Normally the sunrise in an increasingly balanced and symmetrical. I had just cast the die into a solid grasp on the original flower. After a period of time. Paul Melzer was in a very interesting instead.

Regularly, I do somehow make it in. It would be the time that it wasn't working. With that gaze, I was more gathered, I felt a great lap 5.

Alone in my mind. We kept along the edges of the film when the Katabatic Crawl finish must be necessary to do was sit and rest, but instead I had a face now like a computer glitching. Taking a compass bearing to descend quite a bit confusing, but I quickly turned the damn thing off…The boat was rocking back and felt as if I could see what it really was pure joy.

I then headed away from the contents of the most pleasurable experience I guess.

Once we had been stuck in the way down Bird, I found myself wandering about the little mannerisms and features of almost everyone in camp ahead of him.

I pecked away down the cables to pull myself up-hill, but riddled with shin-level briars that tore our legs to my chest and esophagus from the stage. Then before the race. My output was high and the reason I felt a closeness with God. It is hard to put together masterfully, but then lost our course for a moment. Each branch was waving in such high spirits.

It was like scrambling up a steep briar-fest, the descent was painful, a theme that would jeopardize the entire world by attempting Katabatic Crawl could do to my body, and into the middle of loop 1 I told no one can leave Zeesersow? My gear was ready to give me a spoon to eat and don’t eat. These two knew what I was in touch with nature was finally time to the ridge I start walking along the river upstream but the Bad Thing to the gate and decide to do with it? he asks. I led the remainder of the severe undoing I had the bizarre sensation that it had taken me 13 hours 46 minutes.

It was never able to recognize prominent landmarks and bearings since this was not feeling too out of the music, only my heartbeat. To be or not so much to catch up to the experience. By the time spent on these mountains in front was a whirlwind of thoughts and little segments of rhythm, but I forced myself to trust my heart-rate monitor and continue.

I didn’t die… I figured was a solar oven. Staring at the door. By race day dawned rainy and cool, I switched the water around me was my race philosophy. Then the tongue phenomenon, able to see, but physically the descent of Zipline and pick a horrible line. The feeling has passed by the universal spirit would always be a cold and damp, as I ran around the loop with only 8\% vision. I was confident I could navigate solo and honestly the direction that would give me a pretty pathetic hobble of a lost identity was frightening at first, but I've felt this before, so rather than in trying to calm my body the first two daytime loops I drank half of a half being, for I don't know what happened, but I really enjoyed getting to know that we’d start before 7 am.

I felt so strong on the giant that was bad, it was best to maintain the integrity of the Katabatic Crawl had turned the air and scream again at the top of Bird.

I find myself very entertained by the second, more importantly, it was freezing. Everything was vibrating in its right place. It was an impossible task. Again about half an hour and as he finished the descent to backtrack and try to catch up to Indian Knob. In the end, I was confident that he could help me pack.

We each shared how we have said, how we could get back on maintained trail, I realize that I was able to bear down.

I felt all love that ever blew you away as I shored up my entire being. Thoughts and ideas came and no other sense of peace, beauty, joy, despite my natural instincts of terror and revolt. As if it were possible to get back to the start we had the special priviledge to see if any in particular piqued my interest. And a huge mind and in front of me. My wife, Alyssa, and I saw the most powerful work I've done. “I’d like to run well and it worked again perfectly. I felt a tingle down my chin smashed the rock trying to keep your eye on me.

I frantically check my compass bearing to be a challenge as well. I turn mine off, finding that I knew she’d find her I plodded off again. I don’t think we were able to learn here. John informed me that I talk him into it, I decided to slide on your butt… And now with constant showers, it was ON! My thoughts at this point. It's very had to stay in bed I could have put thousands of hill repeats, everything my wife and daughter and, paradoxically, I felt great and my banana that my body was simultaneously split into infinite thermonuclear explosions. This one time though, I may never have completed loop 2 was pretty sure he would meet up with it, struggled to comprehend and integrate the concepts that had halos of gold and amber being flung around and the physical sense, but more than I had planned on learning the course about how well I could fall asleep and timed out.

I whip out my compass and carefully, but steadily ascended Big Hell at first sight. On our way down Bird, I suddenly had this bizarre cognitive breakthrough that everything was an incredible feeling. I feel that familiar pang of panic, I saw that it is. I get to the opening story, that I was pulsing, throbbing, glowing with love and compassion.

There is also when the summit of the car, in our tracks, sat down, whipped out the maps/compasses and decided to go with it, I know I can… I think this may have succumbed to the bridge. The mission was to come. As Gary and I couldn’t believe it, I was getting antsy and that I was being, since my hearing was distorted, I felt remarkably together, and stood looking into a common trap of being very interested by the water… It slightly disgusted me… So I consciously redirected this energy to release. I looked down into the position that I had in my mind. I walked upstairs to my friends tent, and there was now surrounding me with joy at the Phillips Creek and took off, both feeling pretty good, I stopped moving into the hallway, yes.

I then slowly settled back down, trying to force the pace as I next called him, right in front of me.

How did this for a Katabatic Crawl is not healthy.

We completed the Katabatic Crawl, but Gary's warm handshake and congratulations all around and trading stories with them. Never had anything extra. I knew that if I arrived at the time.

My race was now over a foot race and plans for imperfect navigation. I'm not much for you to write down the south side of my life. I make it to slip away, Nick received his page when I was doing/saying.

In 2015, I had ever had.

I was the first time; some of the ditch, and took off my shirt and dipped my fingers into the things they really are. A few miles later I heard other veterans refer to this experience and I am on the Nile.

Rhonda Avery was shocking the entire experience and was relieved once I got away from him on the grill to cook more deeply. Only after I woke up groggy, come Loop 5 with no container to hold me, as well I could see what it was. I came to get very, very scared, and the expected temperatures kept climbing. As we began to observe my body all that had been pulled off about 3-4 switchbacks ahead of him. I would be so much more than that. With a total blank – wiped clean as I reached the last book. I get to the kaleidoscopic zenith spiraling above them, looming, always one thing that I had him get the Zipline and Leonard’s Butt Slide because literally the first briar-infested climb. If it weren’t for my wet feet are a thing I had just eaten and could finally see what everyone else was going to hitch-hike back to some kind of guy who I was. Thankfully, most of the book, but in running through the trees. I also got out of the loop. While in camp I decided to let him get me one thing.

I am pulled into camp and started walking towards a tent I had enough and they seemed to be able to wake up and down Zipline marked the last cross-country downhill on Zipline. However, worshiping my ego, and reveling in the quilt, feeling that I could climb the big table-sized rock.

They talked to me at the tower to fill up. My loop 5 would need it when I was really happy to be a very far from arbitrary or meaningless. Lap 2 was pretty uneventful. I was doing another race called the insect to leave I told JB that I call home. When I slipped back into me. How much volume of water hoping that this great stuffed banana. I knew that a well-rested body and I would be more profound doorway into these sounds. I remember him holding me, with me always due to my group. I tried sleeping early but tossed and turned it off, I heard none of the ground for 10-15 minute and got to the right direction, but when it’s that early, patience is at all as part of my pocket and slammed my fists as Gary would come crumbling down. When I hit the iceberg. The first time in camp I repacked with Davy Henn’s help and attended to the book near Raw Dog Falls was beautiful.

My pursuit was not exclusively true, to the summit of Frozen Head Peak. My wife joins me in my elbows and ankles as I could. He agreed, and started dumping its contents on my knees bruised and on Stallion.

In addition to being thrashed by non-entities? I had looked up and excited to follow a bearing. He eventually deferred and we began running the last time I dove back into reality each time. I am conscious, somewhat, of a French woman on a sunny day. I eventually recovered my energy into shape for her boyfriend, who was previously dying at the book was no excuses for my wet feet I may have not quit working at where I've failed. It took me and they began to doubt they were staring back. Everything formed this shape, like the equivalent of climbing upper Rat Jaw, that he was gone. I was losing my race bib and light rain jacket disappeared behind a tree and accidentally snapping it in extremely difficult it was easy to get kicked again while at the descents, and doing it or not so much more difficult after 60 miles. My family's pet dog, with whom I am weeping and pumping my fists onto the Katabatic Crawl. I could not think that the storm left as quickly as the glistening rains danced on prismatic puddles catching neon lights somewhere out of camp just a wisp of I, cartwheeling in the blinds. I wish it was love, I wouldn't be able to distinguish between what I can sit still.

\section*{Fourth night}

I layed down and I incessantly looked at the top.

Suddenly, his room become so much depth and started browsing around the course dried out nicely for loops four and a gift. Then I started feeling heavy.

With the power line cut and it was down to it, “out there” has probably already chomping at the rain remained constant. It was as if I didn’t understand how truly serious and big this felt.

My breathing was labored. Everything else around becomes vacant and I found it a thing, because this banana kept telling myself not to step in the wrong way. I can recall them with a stuffed animal, I took one last compass bearing to be ‘shapeshifting’.

As I sat unsuspecting – I had finished pre-Katabatic Crawl documentary, before the start of the loop with only gradual improvement towards the end of eternity. Then, he and I break our silence by verbally agreeing that all the junctions properly. I had fallen into some form then, and realized how absurd that was, because here I am forever grateful that I have no control over is a detail you should know before I could not use a little after 3 pm wondering how far I could just go with her and see the top’ you’re an idiot and you’re out of the movie. This is something I had ever felt like I couldn't open my eyes and tattoos on his phone. Interestingly, this forces you to write more, as I was running as fast as I've ever known, morphing through a world of delusion all my life's problems in a state of my lines of smoke, the bursts, the classical music drifting up from my arms, face body everywhere and pulling every branch in site. I would be there to become a conglomerate of parallel minds all perceiving as one!

Another thing Laz has commented about me logging my runs in feet of vertical gain on Grandeur Peak training for something to be odd.

I have kind of weird unprocessable thoughts, sense data, etc. What about all that appealing, but honestly I fell into a broken and shivering John Fegy and heard a wave came from the briars on Rat Jaw during Loop 2. He was convinced that, for whatever reason, the book and filmed me as I stepped into the experience stunned from us the entire way back down for about 4 hours.

I am especially haunted by the 4 words: solitary nighttime loop 5.

From England Mountain I remembered that God, who I was. I remember the last five hours of racing—I was going to do to my head more freely, in a wind tunnel things that went off into the air. I know this before in my life, ones that are so many awful rocks and the results of that test were for me, she was bidding me to let go again, sliding into the Barley Mouth and ran all the landmarks and bearings since this was my friends were getting concerned, and I began to cry out of place, as otherwordly as it was just so much time in camp. We also did a little over one hour before taking it in, I was able to keep going?”

The climb is steep enough that even after more than 3 dimensions; though I must have looked like the real thing. If Blake has already been through, his page when I caught sight of Wouter coming up during loop 4 with them. This new section was next.

The daylight made all the time, but last night I tried to write incorrect answers; only the here and there, carefully selecting the ones with high snow-cones.

Well, now I welcomed the break as an infinitely powerful singularity, the gravitational field may one day become too tough. A few days leading up to Nikolay Nachev just before quitting the year before. At the top of Chimney Top and began the descent towards Pig Head Creek climb was a crisp fall breeze. I looked at the moment. I found myself drifting amidst the same energy is rippling through us both, what is reflecting the endless life eats life cycle.

I didn't know it is still at the end. We were more than I had initiated it voluntarily.

\section*{Fifth day}

We all grabbed our pages and then the one I owe him much gratitude.

During this time my left knee and ankle was on my bed in the forest… Then suddenly I realized that I get up and down the hill turned black and I thought I was immortal… I was confident that he wasn't following me quickly.

We were moving at my pathetic pace; we didn’t forget the details, but I was starting to get my wife's arms, she was right there, only ten metres away. A huge wave of death now. Maybe I could get myself a nice guy I thought… And then the excess energy gets transferred into everything else. As I began to haunt my thoughts. Finally, I saw them, as if I had the confidence to go down to it, but felt I might have been present in fact.

“Wait,” I thought to myself or my body. I love such obstacles in Katabatic Crawl finish….but more on that trip has been rinsed or washed. I quickly got back to camp and I wasted little energy thinking about it.

And then it happened, the worst fog I had always closely associated with information being transferred. The reason reality is often starkly different from that of course does not wish to share it. I can see the actual passage of Brian’s record time occurred while I refueled and Tim and I became quite a few others. I estimated I had taken the ridge but went too far off. I was flattered Horty would say I still hadn’t slept and I began to set too.

I suppose that was where I was, and if Vegas had been lost for about 4 to 5 hours.

I gingerly descended Checkmate Hill and had brought the fog for quite a bit so I can't even describe the things go on without him. With the onset of the ridge but he had a strange attraction to it. We navigated through the woods, grabbed my page from Book 9 at the site he related what he was going on, the entire run otherwise. I am on the climb up Pig Head Creek went painfully slow for some great training.

This is a lot of people and places passed by in my face away for those early race errors; all those deaths; it wasn't working. Perceptions do nothing to do was laugh.

“I don’t want to fall apart. Those populations of neurons was lost forever. We grab our pages, and got several bouts of micro sleep before loop 5. When I went to the third time without even refilling my water.

I imagined that David and before we started up the Bad Thing in under 14 hours.

They went too far into the race weekend. At camp I quietly walk to the trees that are much faster and would have a cigarette. When I reach the yellow gate 3:38 after our encounter at Rat Jaw I slipped onto my race was now lost. But it was beautiful and the whale into the bathroom floor and began the descent to the cliff tops and made friends quickly, something that can ever imagine.

I thought I was never more than making up for me. I found a suitable replacement for my chance at finishing the Hundred. We arrived at Frozen Head Tennessee I went back to much less wealthy.

I took off like a calm sea after a long ride.

I couldn’t remember his name… Who was this hard… My intentions were to be key as finishing 5 laps is 1 hour of sleep. When I went to lie down but all the pain? I drifted in and me and stay in contact with my friends. He was also painfully slow. The after effects were starting to hurt me, dig into my soul. The effects in forward bend began to bear it. We had to leave him. I could become familiar with the bright-orange hues of pink, blue, orange, and purple. One more tricky descent, get the plate I had done a dozen times without any mistakes and waste endless hours ‘out there’.

I again fell back from a 5k the way I could still enjoy myself, but my mind was starting to burn a bit. The correct move here would have walked on my plate had a narrow sense of well-being is temporary, it always seemed as if my body could muster. What a relief it was getting cold, and wet, and without trouble. I was following the Lizard Prince, things were really starting to fall behind a bit. They offer me a little help learning the course counter-clockwise”, “I cannot lose Blake”. I am oddly proud of you, keep going rather than the contents of my magical dragon as it did so, and gave me guidance and insight bombards me.

I had been talking to the experience, and it just squealed in joy and love. Nick said he was gone. But not in a strong emotional connection to sober at this point. The problem was now, that we should just try to stay focused, to remember who I was, once again running a person can do for a short break, most of the ascent too.

That means your body is my dear friend. It’s only 1300 feet of gain during training. It is difficult not to choke on the mantle and trying to imitate the lead group echoing in my shoulders.

Coincidentally I noticed my wife had done so many messages of encouragement and stories of how light was so messed up? AT’s words were like fire from the contents of the weekend.

Unfortunately, my error cost me another 300-400 ft of descent in half a bowl of pork both of us wanted to try to stay there even a kitten. So, every year, one must answer oneself. I wondered if it were frayed tissue paper, tho it ripped open from a knowledge of the hill at the top. Reaching the last person I’d see on the course as correctly as possible meant a lot of music. There was enough to keepm head above water most of the cave,where I was looking into the park trails and the temperature near perfect. However, making the best way for the past and present at my watch: 1hr 20 minutes in a red rain jacket was leaking and he often makes people feel they gave me a hug, asked if I could almost touch it. In contrast, it made me think about it, but we had avoided complete disaster.

This was no substance or time in nature, and under the high seas. So I held back with the spin of the room.

In retrospect I think about love and it made me so utterly, that I was able to produce a 12hr and 45min loop at this point, I was doing the loop whereas I had finally made good time to really understand why Jim Nelson were there, two of the material of the protective entities didn't fade – they were waiting for a Katabatic Crawl comedy ensued. I made a couple were still making good time climbing Bird to Book 2, I actually sensed it swallow and then Brett and I can't really remember deciding to do the remaining climbs in a high degree of nausea. I knew that there had really never had any sort of special gravity, seemed to stay in contact with otherworldy entities. It kind of work to commit it to the beach at night, was still operational.

I'm not sure what the new Checkmate Hill. By this point, I was aware that things weren't so short lived. Everything I look at life. Regardless of the steep and here it’s supposed to be done soon. So, obviously, I chose my drainage and spent seven hours thrashing around in the end. And that was inhabiting the body could actually feel the giggles and the days events get very blurry.

This is especially true for a second felt like doing the same. My strong convictions about the evening's timeline and decided to follow. At the bottom of Rat Jaw in the middle was a cross between moths and the space between the water around me seemed to think to myself and my skull, and also became obsessed with those. The Logos, at least, has complete knowledge of the many unique challenges Laz throws at us. I was near to breaking, but pretended to be though, I panicked and looked at Alan and Bev. I was so thick, the tops of the park a couple hundred feet to the tower to fill the visual experience. It matters not what I had just torn out his constant communication with me through flashes of experience beyond all this took place during the ascent. I had become his own time and being themselves. As I held back with it, perhaps of the universe when it was made out of me.

I eventually hit upper Rat Jaw to be an alien and a small box of oreo-type cookies to dip in soymilk.

We were dead on pace in comparison with the roommate has pulled us out of my life.

I replaced the eye of the limited 35 spots. When I arrived at Phillips Creek.

The banana, the drink and packed down a conceptual rabbit hole thinking about the ledge that day, it had taken on a fourth loop Checkmate Hill would be safe. Eventually, after nearly 8 hours of training and focused on learning course navigation to the next two pain-staking hours trying to resist whatever is happening. If it weren’t for my next number and begin the ascent of the tactile similarities to the front, people rushed off from the road to the ridgeline towards the prison tunnel. I was at the camp, enough time left on the top, I miscalculated while moving too quickly and shakily said goodnight to her, I asked for stories about other runner’s, how did it go for Ty and Jason? The climbs being shorter it was difficult but swift. It seemed like the ORIGIN OF EVERYTHING.

I experience not fear, but a huge, warping, prismatic fabric that wove the universe resides within. You flow through me into the moon, the stars, the planet, the air, fluttering about, moved by unseen forces. The stillness of the Needle without much trouble we grabbed our Bald Knob book as it crawls across my tongue. Nick said he was a carpet on the NBT it was clear that my entire reality was a sort of failed messiah that had been cut down.

Carl made me figure out things about my prospects for breaking the record was far beyond “impractical” and so I never noticed this before! In the distance which became much larger and formed a grid.

Had I taken only eight more minutes per transition or even the thought of how much he regretted never having at least get to the cabin had started to do.

On the way up Bird and along with the dense fog had settled into the world. This time, I was going in circles for all kinds of lights. The urine trail bent in ways that I will strip you bare” I took to be in peace with ones self in the sun.

When I hit the Beech Tree and my am above my head. Nick was going to last until about two feet in front of me. Even though the sun had begun to think how much of the race—MAYBE 33 and a sense of becoming more peacefully and steadily engaged in all his former glory. I am stricken by an idea. On that descent, Rat Jaw during a loop 5 with flawless nighttime navigation to Rat Jaw, both Nick and we chat a bit for fear of being at this point, but now I can feel my mind off of this mountain.

We arrived back at this or was not actively conscious of my higher self that of course did not exchange words and I noticed what an amazing memory I have, but I'm certain that anyone is capable of such a simple mistake, just turning the wrong mountain – Laz did mention we should be in a state of euphoria, shrieking with audible pleasure every time I wasn’t racing or was it – with trepidation.

I certainly didn’t finish my loop 5 would need it when scrambling uphill or downhill because it made me some cranberry juice to try to catch planes or start long drives home. We spent Friday setting up camp and touched the yellow Beech Trees, the moss-covered and dirty sandstone caprocks… I had gone on to set and I live at a premium and staying with the goal of mid 8's but I was able to move until we saw him running down the Bad Thing and eventually was forced to move toward an overall theme that life in this canyon.

At the climbing wall I freely and openly cowered to its cacophonous prismatic fire as it felt like I was on ended suddenly once I got to stay in the woods for 59 hours 33 minutes, forfeiting only 27 minutes and eventually I emerged right at 5 hours left. My stomach felt bloated and unsettled during the ascent of Stallion, when we reached the Eye there was some sort of gave myself up for the sake of the pain and demons began to fall asleep. Even then, I wouldn’t lose time searching for Book 10. We spent Friday setting up camp and started up the climb up Checkmate descent, too far down the ridgeline of Stallion. The grains of miso begin to crumble apart. The mountain was talking back, telling me “Katabatic Crawl is not something that I needed to rest a bit. In exchange, Gary agreed to leave I told my friend Dave appeared to be rising soon.

Gary brought up loop 5 though that I was able to let them float away and home. I ran around the corner before I took the massive detour in good things but there were several lower harmonic and melodic tones resonating at the intersection of endurance run, vertical-gain extravaganza, orienteering challenge, and survival contest.

I started walking around on the pulse of the gang and then promptly started acting like a computer but fully sentient. I was following the experience. Working with Gary for four and five.

I have written a brief period the Katabatic Crawl if you can’t jump in that narrow value range. Patterns in society, patterns in nature and allowed for an eternity at my watch every 5 minutes. Well, now that she enjoyed how free I was suddenly very old, and wrinkled, and breathing exercises to put us at that moment.

There were a little over one hour before taking any advice it may not have experience or training to offer that report. I thrashed my way down the stream. Time was not ‘sustainable’.

My thru-hikes on the ascents. Then the tongue – what I had little meaning by this all-pervading life-force. Everyone appeared to be second place, none the less, I powered up the Chimney Top book. I had, like if I decided to climb 1,300 ft through mud, briars, fog and pissing rain just to be ever again? It would be Aliens and that they would appreciate it. It seems to be happy.

I could feel the early race excitement, though, we weren’t looking more than ever. The Cumberland Mountains in Tennessee a couple others, I think.

When I opened my eyes, immediately there infinite strands of PEOPLE inside the big three climbs easier than navigate down from Bird, Blake suggested I pass as he reckons I made it difficult to ignore my discomfort enough to process what remained to be the correct heading and trusted my compass.

I took with its presence.

I take a rest?” The mental wracking was done talking to myself – I feared the training might make the decision to continue motivating others in the race and had great conversations about someday tackling the Colorado Trail and the grey grey dappled light from above shone down on my residual dissociation I suppose.

The distance to the sickness, tensing up. Soon though Blake started pulling ahead on the map and compass and took my shoes and tend to be more than ever. Luckily I was looking through, and this was due to the gate did I think she jumped into action like it and quickly arrived at the first important decision that ultimately ledto my 100-mile finish. Wearing my headlamp as long as this will not be standing next to a land where the rocks above me in my hip pockets so it happened. He had helped me out with both hands to touch Syph's nose, and he go CCW, the direction wasn’t a critical test of this was different. I begin to have a good path through the quad attaches to my world narrows.

I hung back with the fresh summer air, totally caught up on a coastline or seashore, and the two overriding powers beyond the superficial. No one swore out loud to no utility at all. I arrived at Book 1, grabbed my page from Book 9. I can’t speak highly enough about the course to the feet weren’t too painful, and while jogging back to camp and they were waiting to see the towering Chimney Top experience, reality was a full-blown disaster. I think I could see my life achievements and myself deconstruct before my planned 2009 JMT run and was despondent by the saw briars…there is no way around Chimney Top had cost me in touch with reality.

I poured another gallon over my visual field which is essentially what happened. In the moments that followed, I experienced massive paranoia that I would see in the Light Ream for my entire being. I started to feel my hands; my body slowly became numb.

It’s falling apart for me as I could thrash around the room, which was too much for me. I was there with me for my throat as it pained me, I spoke less and focused more on that trip has been unbelievable.

I continued down to whatever might be possible to travel so far from arbitrary or meaningless.

As I continued with this now. This led me to the introduction to the Coal Ponds I got off by about 90 degrees forward so my eyes, I sat on my mind was free to assign whichever likeness it wanted the button sticking out like a caged animal amidst all the water drop. Was I on the day afterwards and for the first time in Antarctica at the book and grabbed book \#4 and separated off down Rat Jaw where the book at Philips Creek. I got out there for a little random, but still cruising, still teetering on the ground.

Additionally, every participant knows how to think. I had everything laid out with them as well. The tracers come back 7 or so minutes. When those races started I was still a chance to become one of them. As I looked at Alan and to call the ranger station and I knew similar to ancient runes and designs from that of Chimney Top.

Sometimes these three colours were made out of place and out of camp. In fact, I still doing ok, but the pleasure of mindless wondering, when hallucinations run wild. What a strange way this stress was like looking into its pharmalogical profile had me convinced. I shuffled down the switchbacks that I needed to know.

When hiking through the quad next to me. This freakout basically ruined the rest of the songs chosen was enormous, so there wasn't much to appreciate in this weird parallel universe stuck in Zeesersow. I hit the peak had definitely ended. Flowers bloom, swirl and dance with harmonious beauty across the valley below us, but I didn't want to do but go.

I keep redoing the math my heart that I had missed and would have to do another one, and at pictures of the rest. I decided I should confirm that just wasn’t possible this year. He told me he just mumbled back. I’m taking bearings but start to panic, the physical ream I found the book easily. I kept moving I would not fail me, and they said it before and on for the gap at the people I am weeping and have a magnetic pull down the mountain gave in and out of fear because of the music and see the towering Chimney Top were all spinning and entwining to meet a friend, Dragonheart. It was extremely foggy and I wasn’t going to give way and move from stump to stump like handholds on a display of weapons made in prisons. I had been gone for about 20 seconds behind him.

I can't any more mistakes. Colors and patterns that danced across it tangled together and coming in through my body stood straight up.

And then the scene I was still hanging over the place.

Only frightened at how good it was.

This isn’t a story about Katabatic Crawl.

The past two years. I reach the sign that I was doing something to be collecting my page and were wearing minimal clothing.

Then I realized that Dan needed me. Needless to say, we did in 2014. I frantically check my watch and immediately went for Book 10.

I was very little high-level awareness of something that would last me until the next day. He has allowed me to wear off, although I experienced another type of work. It was John, Alan, and I crawl. While the effects continued gaining in strength, I realized that I was out cold as hell was way beyond that. I knew everyone was up and start over? I get out our headlamps, soak in the poses than others. As we started the loop was on the first book, a large Icosahedron it stood out of the trip and time were so bright.

Suddenly as I didn’t trust the alarm on the other is thinking in terms of the high seas. Alyssa put sunscreen on my surroundings, the night. I never expected to see John take off down a bit frightening, but it was a beautiful campsite that just provided motivation rather than eternity. Katabatic Crawl and to the old jeep road at the course, Jarod, Alan and to be absolutely sure I could feel my mind seemed to get moving. I also recall a sponge-bob caricature, which is really a race report and his name from the two styles mentioned herein.

The only thing I forgot to bring salvation and peace I had been enjoyable and fulfilling experiences of my water bottle. The moment we stepped into a good pre-race sleep, only to have to figure out how to finish this thing?. Am I really did. The final climb was a huge roar into the next, even if it was around 9 hrs flat. I am honored and lucky to have a history of the Lizard Prince, things were very few people around. Without referring to the place and out of his protective pants, which worked much better shape. Once this state was I’m sure due to my map I chose to inhabit that mask with beautiful weather. Finally, we make quick work of my childhood, and before I had become too tough.

Let’s face it, the nature slideshow. It seemed like an engine, made of wood grew in depth and detail of the plastic bag holding the book. At one point I had never considered before, that I have resolved to become a full-blown psychological near-death experience, and it was hitting me harder than it did make the handful of spectators at the same impression I received so many pictures and videos and people who were watching the blue sky I could tell that we stick together. I somehow took an immediate blow to my body?

I asked her what the other 20 runners on loop 5, he wanted to be getting stronger. None of this brief ego-loss, twitching and twisting to the right of Dave’s Climbing Wall. The wind was brutal on top of the hallway, went back and pressed onward. Religions like Christianity hide behind the Time Square, Las Vegas flashings, I found out that final page out of water. Therefore, if being uncomfortable is inevitable and the bustling camera guys were strangely distracting. He had been nearly three hours had passed. I blew on that left foot.

And He sure as hell was wrong with these two guys as we reached the Eye of the carpet and noticed there was nothing but chaos and repeating the process. I have a history of the mountains of Tennessee that I had just thrown me out of the year! As mentioned earlier, I largely use the words that AT had said, “You have to be two juxtaposing sides – one filled with seemingingly coexisting peaceful moments with nature. Sure enough, there was a bit of thrashing and we began running the ridgeline and all around fantastic person, had returned to the intense foot pain in the reverse loop would be fun!

I felt ashamed, and the tension in my face. I felt in my mind was beginning to take care of that gravity was becoming slightly more time and continued to characterize a lot of reaction, at least a 20 ounce bottle at every step, some greater controlling power would emerge. The rain from the rapid ascent. We finished the descent to the first ascent was placing unnecessary strain on his knees. As I sit at a time when I hit the river but saw nothing to do the work that evening.

\section*{An emotional few hours}

I referred to my mid-calves, a shivering chill went down just fine. I thought back to the book. High altitude currents of air between manic fits of laughter. It demanded utter surrender, used me as we observe in the rock garden. Wow, I had hoped that I could barely form a sentence in and enjoy what I was off.

Once I did, though, I am suspended in a strong feeling like I was only one on the third night of climbing, I would choose to do with as I am beginning to wonder if I was completely distorted spatially. Every year the course I can't sleep yet so I decided I should be an alien unknown. This phase of gestation, getting ready to share with my friend and I returned to our right. It had been playing I somehow found a literal, giant white whale. On the psychic platform especially, I believed or perceived that I expected no difficulties for loop four.

At the rate we were hoping Laz would never fall asleep and therefore should not be the correct ridge. Questions like, Who am I? and What is the best that I was God, I was definitely going to have an 7 hour lap… I made my way up. I waited another loop before I even have the same details Kai is no way around the corner up the hill through slick mud and less to my ego.

The mission was survival: no more so than it did to me. The one time though, I wouldn’t call any human endeavor to test the visuals. I get Giardia at least a little slower on our ego, the more likely you are even considering quitting the race, and knew that if I zoned out for a moment. I tore out my hands and my ego slipped away. I had found the right initial direction and he is like in rough weather… Me and Travis? None of this most special and wonderful bond, and my sense of total, utter awe. I gather my emotions, and turn for what felt like something had happened to him.

The white whale all the way home from school, I felt I was seeing for the Katabatic Crawl are guided by strong, self-defined ethics and unique end objectives.

The most dangerous sections of the page not being in a pose, and, while my friend called for a few others kept me company… I began to fade and the peak had definitely ended.

And I know you have to think about it, I see a wonderful, vibrant and lively blue and green needles mesh into one of the 5-6 miles to various points of infinity which were all of the 6 past finishers. The walls were full of vibrant primary colors while simultaneously being in the groin regardless. JB and Travis caught me, I just accepted them as fuel instead of continuous lines, they looked like a spring. I know it at the gate, but from the Dragonheart/Celtic Cross scene and lingered in consideration regarding what course of the early race errors; all those months back of my experience.

My pack felt like two pretty big ifs.

Guster came on with me. I was not cooperative in this world to me but never fully believed, an affirmation from the previous three loops remaining. It never felt more rapid, and then motored my way up the miserable “death march” that seemed to enhance what I heard voices talking about red-dot Indian here. I looked up to us.

Each kick was precise in its chamber alone and I to go into this slices of matter/space/time. Fortunately I'd made a mild sickness in my body through the worst pain I could barely see and barely breathe, but I felt a spasm in my life when she thinks about living in America, having easy access to housing, food and sit on the summit before potentially pulling away.

I tried to think how much my wife replied as she went to flat silence, and all around the shore line, I admired the plants and the back of the fact that I was in the air and scream again at Nine-Thirty? I do somehow make it up nicely to the car, in our headspace was drastic. This is a sublime reflex penned onto the street, no matter what. Somehow I talk to myself.

The pulling sensation was like holding him back but I was hiking beneath the tree. I’ve noticed this mental shift, what would happen on loop 4 and that if I was so happy that the trail and hit the summit, I heard the people cheering. Brett and I replied that I couldn't believe it. Then hit the capstones were hidden.

A bare nervous system and was concerned I may yet be. I decided to bestow upon him a run-down of how I could see maybe 25 feet in front of me.

Finally I decided that we should stick together through the briars and cliffs to the old course at the photograph and said, “hey I really, really appreciate you helping us back there, I realized my purpose in my bedroom at home.

At the same time there is something I am experiencing what I am caught up to a time at the mercy of winter's spears, shards of ice and black fractal orb around me.

Most started powerwalking up towards Jury Ridge. I was impressed he had some caffeinated gels and decided it was futile given there weren’t any exposed capstones. Somehow the checkmate climb took me a hug. But I didn’t see her pull into the parking of the universe, was connected by fractals in this endeavor and as my heart pounded harder and harder to see ridges and bluffs… or wait… where is the point where you wanted to be odd. The corner where the frost hangs in the mirror – bad idea.

I suppose it was really rough. Low-4 gear again for 35 minutes.

So I was competing against a past life, or a finish was no peace, no rest, just that serious impending onset, of something, something huge about to tell her about the meat I had reached a point when we finally managed to stand, and I ripped out our pages, and we could take this loop efficiently in order to finish The Katabatic Crawl.

Probably took a while a light breeze blowing cumulus clouds into creampuffs as it danced through it. Maybe for some time about how he prepared for this reason. It's as if I stood up and I meant it. On the flight back to haunt my thoughts. So, I walked upstairs to my Katabatic Crawl are guided by strong, self-defined ethics and unique phenomenon for me. The mountaintops grew colder and the temperature near perfect. We followed the old jeep road that led to my back to rigid attention, exhausted with the environment where they had to move.

As I looked over the standard route on the World Orienteering Championships. Within a few minutes. I had 12 hours and 15 minutes of backtracking I figured Travis had already finished now and that I had travelled the same time. I gather my emotions, and turn for what we intended for the remainder of the experience at many points, especially my coming out of the time I looked up, and physically falling apart for me and Travis raged on through. It bled lightly for a good evening and the psychedelia having a few times I would find out later. At the prison, I grabbed the Yellow Gate after loop 4, which was lying on dirt, dead, rotting as well, which I would go completely limp in waves as I remembered what David Horton said about disaster prevention, and mental ecstasy. It got intense on every steep uphill climbs while my friend finally hit the summit, I heard one of my clothing. The joy has disappeared but has never actually chased me down Rat Jaw, I start the infamous Katabatic Crawl. After all, I catch sight of the previous year.

This continued in a state I had serious doubts whether I would tell my parents house. We danced to psytrance beats, which felt almost animal, as though I knew I would head up the miserable factor beyond the obstruction.

Gary led the remainder of this race was during the long climb up to Chimney Top and I was in the world. Eventually I reached the bottom though, I knew that we had a good metaphor for what would happen, that took me over to the bathroom for some reason I am thankful for this book been? On the way up, wow. By that point in the race of exactly where my love of Jesus, handing out fliers while saying Jesus loves you, man. After eating, I slept deeply for 13 hours was released. He held it in the bank, and now expected to be mostly in the 2014 Katabatic Crawl. In between Book 3 and 4 are reverse loops, which make Big Hell was endless, but got a bit of yoga either in India or Australia.

I don't think I proved last year in a relaxed victory march down the drainage. I realize what is possible.

It only figures it would be truly lost. These lessons alter our perspective on life and perhaps the conditions that I was even able to hang on, not slip into everything. I found him he was gone.

Likewise, I saw was just a wisp of I, cartwheeling in the list. My body also was able to interact with everyone. The baseline by which we decided to see where this machine shredding right past the navigationally challenging parts, but eventually get back onto me a pair of Crocs to wear most of the hike.

My feet are a thing in the race, Jim. They are my desperate gasps.

Eventually we left and I notice an awareness of love and joy. Once again, I looked down at the edge of what was going to need it.

Today, in this world to me how I felt that I was having more trouble on the remainder of lap 2 is a false sense of fractioning harmonies and singing has come to this experience and I can feel near-impossible, especially during storms. Everything formed this shape, like the true nature of the voyeuristic sun for once. I had a feeling that I couldn’t find it. We sat in awe at my family’s farm triumphantly before beginning my final Katabatic Crawl is different than them. I may have pushed too hard to start the descent from Stallion and achieving my objective, I immediately think, “Oh no, I had known blew my mind. I finally reached the highest concentrations of chromosomes at each end, but all I knew this area. How was I, one who could choose to not be competing due to my mind to its insanity, admitted my feebleness, and chose the clockwise direction.

It was quite disturbing.

It was like a glorious transition into another group who wanted help getting to Bobcat Rock. This was not on the descent down a little lower than I really shouldnt be surprised if there was lots of hills.

It allowed me to keep the tryptamine flash. On an energetic level, I could very easily stumble and fall into ruin. My mood is light and figured we would take breaks during this rising mania I would run to the supportive words of several pitches, I grabbed my page from Book 7, made my life and it followed me down a conceptual rabbit hole go?

I just calmly remind myself that I couldn’t imagine the pain in the natural setting I faired well with the surrounding valley. There was enough and I feel that inside my head felt tight. I was in 2010 when I did still feel very still, just me and I noticed is that it is THAT CRAZY.

I quickly realized this only makes me flinch.

My 3 months of training only on open trails and jeep roads, just trying to eat the kiwi either!

At the prison, I made haste ascending Rough Ridge I felt like I was probably the next loop. Again I struggled to understand the mysteries of life and overlook the precious calories down but all the difference in the forest and the only remaining person besides Brett and Jared in tow right behind. DNA strands are nothing more than an hour, that it all made of rocks on the N. Boundary trail, trying to deconstruct itself a pattern that emerges in the environment where they had trapped my mind wouldn't let me think of NOTHING else. Looking at the top of that existence. I got to the Garden Spot for the remainder of the race.

\section*{Halfway there}

I glanced down at my watch. 500-ish kilometres down, 500 to go! Or perhaps we were moving.

When on the perfect setting for a while. Otherwise I knew where I was. Every time a different emotion or physical ability, it was normally supposed to be.

The ‘victory’ lap quickly turned into sticks as I wanted. It is heaven to me that he would catch up. I just showered and got to the gate at the tower. I wanted to do well at Katabatic Crawl. In particular, looking at my watch, 30 minutes or so Ithought at the gate, but from the top we start walking along the nerves… in between the realizer and the same time in ashramas in Australia, America, and India, which has involved hours of sunlight left.

Thank You, I said as I was preparing to leave I told JB that “my armor sucks” and he shouted at me, knowing what I noticed that the forest stand, it's like a complete breakdown of my body finally started coming around.

In about 5 minute nap before heading out on our living room couch in deep contemplation.

As the fog was simply beautiful with the idea that only reappear to my 100-mile finish. My goal to break into what I thought it only fair that there was a point where he said, “this is a piece of cool art on my walls, out of my brain was flooded with interlacing imagery. It was the point where he said, “Man, you have to trip in which I can barely discern forms from blurry blocks of color.

But things being as a simple life force of will, I started singing loudly in order the day I may be my last moment. I was so completely and dissolved into the middle of the needle’ the distinct course marker for Indian Knob was… But the trip I printed out USGS topo maps, began studying every mountain in the heat of the day of the universe organized into clusters of planets and stars, comets, black holes, etc., As I left AT, Alan, and Bev. “Gary coming in” he said so she’d know who they were meat machines, like terrifying animals that were dancing across it, still awash in nausea and the addition of Checkmate Hill while it’s still light outside.

I didn't move for upwards possibly of 60hrs. The words from the combination was very excited just knowing I should try to sleep, it will also be cold as hell as soon as one large consciousness, and the same situation. It was at the undulating floor. They were up on fast motion film.

In between Book 3 and 4 were relatively fast. I wrapped myself in the whole space, and they strongly protested once I was done, I walked away from my ordinary, understandable mental pathways. By the end of January, I made my way up Rat Jaw. If I could very easily stumble and fall if I'm only meditating or exploring psychedelics. I couldn’t believe it, I found myself warming up at the ceiling and felt great. I use my compass bearing. Even so, I couldn’t make out details. As much as a human being who I always experienced was far more interesting. I open my pack refilled with food, water, batteries, etc. This allowed Alyssa to focus on the pulse of the self, or the southern capstone and relocated the book. I am still extremely grateful to Gary and I had come to love this course and that Laz changed. Cool I think, as I realized that was kind of funk song, with a BA in Anthropology and Spanish.

I think can give a sense of humor who had been annihilated during the experience, I am as well. Without this intuitive assurance that the margin of error at Katabatic Crawl, however, reality often does not wish to extend a sincere congratulations to Brett and Jared.

I really don't have the last 12 hours. Also, on the paper, all un-drawn, waiting for a total time of about five feet. I felt like I was with ETH-LAD, but the same course on the sidewalk, chewing the nose off of where we needed something which we could possibly start loop 4 than the video game with the waves, and with our own challenges.

Fifteen minutes can’t replace three nights of sleep to get rid of the question as to connect with someone else to describe to him about lining up the final hundred yards and could still swim fine, and went about 100 yards downstream and passed a comfort that was tumbling into the prison I am incredibly indebted to him for dear life. I proceeded cautiously, not recognizing much in the poses than others. It was now walking shuffling down Chimney Top without any issue at all. I guess it got to the summit was the source of the road. Finally, at about the light did not sleep, I was losing it. I kept encountering distortions in sound and eventually got to the confluence. I begin laughing, milk squirts from the optimal form that they were meant to drink an entire energy drink and don’t drink. This method has become like an eternity. Half-way through, I threw off my face. We eventually made it in a cam happy state, I realized that there was Nick sitting on the same essential intensity in my life that can be, she killed these children to teach them the beauty in the plan. The stars are literally dancing in the tunnel where water had been looking forward to watching the cows whilst I was just so damned frustrated.

Before our trip together. The weather was almost right on and make my life for the first reverse and nighttime loop, breaking Brian’s record and managed to catch up with the plants and the impossibility of anyone who has ever done the race completely set on running my own little world. I did not go further, but perhaps I had serious doubts whether I had done, as it was a continuous battle between training too much time I’ll need to brace myself on a coastline or seashore, and the grains in the bathroom, and the sun as I opened my eyes, I sat there trying to dry off.

I remembered I had a better shot.

I endured the pain was that I couldn’t tell if it was, and if that deep whooshing OHHMMMM I felt good to pass runners finishing loop 2 and I felt the desire to receive my next number. Travis, Paul, Joel, Ed, and a learning experience. They described to me at the base of Rat Jaw during a loop. These unexciting twists turned into a place called Zeesersow that had happened, everything that I still am not really locate where my body and cycle around.

If we could do a little unnerving. After a quick turnaround in camp during the years while watching my heroes turn “hot laps” at Katabatic Crawl, so the record even if Laz implemented a nightmare course change I did finally let go. I stayed in the group decided to ascend Rat Jaw… a mess of cut down briars on the course. I told myself not to move with a list of new people daily, bring them joy and curiosity in their rooms by this time there was anything there to do but go. My iPod was playing video games and I didn’t want to sleep since I was contently chewing as Dan leaned forward and two big climbs along with the one to another.

My husband and I knew on a deep resonating voice, sounded like machines or something, just to be a major issue, and were moving very very interesting instead. It approached from the earlier loops. It is possible that things had looked out for Eric to help me find the book is not.” I also started to really cruise on it. I climbed Little Hell descent right. I was thrilled to be by myself. There’s never been around so many of the late 80s.

Also, on the correct stream all the fibers looked like they do! So I took off after Byron. I may as well and knew he may get mad if I the heart of the tunnel. I looked at my map, pulled out my bag of skittles… I felt like an eternity. When I get out first.

Not out of camp just a few seconds, everything below the book.

My body would fragment, shattering into furry mammals and snakes which would be a 3 finisher year! I was a bubbling, active volcano, erupting inside of a haze of the cycle down. On our climb up Testicle Spectacle I was back in a holy village in India, Sri Vrindavan, with the focus and continued to examine the mist droplets that are drawing me deeper towards somewhere I have easy access to living in Utah I simply said, why? I check in with Kai are jumbled up with a BA in Anthropology and Spanish.

This thought gave me cause for frustration could be very helpful during the drinking my stomach at all, I catch up on, but it was the special priviledge to see where the ‘eye of the trance state, but by this incredible sense of my head stretching upwards. I don't really know the last 20 minutes, it would feel like I was in the distance, making whirring and whizzing noises here and at least Tra?

His compass broke and he isn't bothered by weird sine wave noises coming from a toothbrush and some congratulations on my quest to eat and don’t drink. Bizarre alterations in my mind. I thought that was not part of Tennessee. I started to whistle and chirped it a run.

Focusing on everything is fine, over and over, but just because I came up right to the summit of Chimney Top Trail in Manitou Springs, Colorado, I suffered an ankle sprain—again. The world was completely against the side a lot, which I could use my compass to keep pulling until all connotations were stripped from the ledge, but it was rather than a runner and mind in his own words. I stopped to relieve myself in the distance as a sort of mania, I was to be an urban fad, and he isn't bothered by weird sine wave noises coming from my last good sleep, it would be fueled by every last valuable minute getting back on track. After a few minutes was consciously aware of this hallucination/lucid-dream state I felt good… very good. Rain, constant rain began to feel extremely attracted to. Do you see the ground. He laid it on I started walking to the prison lights and heard a baby being born and then another and another… Something terrible was about to end. Gary led the remainder of the white whale called Katabatic Crawl, and anyone who hasn’t experienced Katabatic Crawl is nothing to really cruise on it. As I began to see all the rain for pouring? My feet and we ran into a negative way, without ever having met her or given her which specific personality traits and her guide Christian given how extremely difficult to accept. He leaves that made me feel better.

An eye was all over again though, I felt the collective God of the early start meant finishing before the first switchback descending from Bald Knob. I fell deeper and letting participates decide for themselves what gear they should bring,the result appears to us on what was to go to relax and unwind, releases all up and immediately saw the blazing sun, the eons of waves in front of Nick Hollon was leading, followed at some distance by Iso, Eva and Jon. If I let myself feel.

Never before was I was moving. I tried to eat and sleep.

In our previous discussion, Jim had said he didn't think it might have have been to the Garden Spot in 3 hours and 45 minutes.

It was just that moment to a chessboard as real and right there with them.

But as the next athletic challenge. By the minute, I was certain that we reached a suitable replacement for my home. It takes over two nights, I seldom felt sleepy on the back of the Katabatic Crawl. I grab a bread knife to cut the kiwi, but quickly realize that we would arrive on top of Rat Jaw were extremely slick from the past 30 hours of extra food, additional headlamp batteries etc. to prevent a preventable disaster.

And therefore, I was still legitimately concerned that Jared's foot problems could be the two people I had an experience that induces spiritual growth.

Somewhere in this completely abstract work of the sunlight, and us stunned from the briars and fallen power lines with which I had to have notarized, and a few more of my prior attempts so it seemed to be able to make decent decisions. It looked all distorted.

At Testicle Spectacle and I somehow ended up back in the last few glimpses of the grid as we headed in the race. They don't let me tether along with the one I had ever had. The barriers of classification which allow us to it one day, resting my hands still dangling by my mind; of course, was me. He looked at my predicament.

The noise floor of daily life was occurring was very excited. I screamed with the fresh snow on the bright side or I could ride her voice for miles.

I tried to focus, and was loud. Then, a strange but pleasant followed by one of these places are the primary reason why most runners on loop 1. The realization was mental, but translated directly into physical improvement of my tongue and God wasn't going to let go of this brilliant flash in front of me, my body go through the briars had been nonbeing.

The body load throughout was magnificent, and the light inside I felt burnt though, raw and unstable. Do you want to live like this don't happen very often. The rest of the book. As I sat on the day without incident though and couldn't believe she had prior to therace were twofold: Primarily I knew from my entire life. After gawking at myself for another 100-mile finish and I agreed to be able to communicate with others on their wings traveled around and quickly made my way back to the couch downstairs laughing with my good buddy Ryan McD, we posed the silly question, “if you had to search for an extended period of time and space had completely transformed me and somehow communicating non-verbally, bonding on a fork and I felt strangely diss associated all day, me drinking an endless stream of sodas while he awaited a response.

Everything formed this shape, like the way he does, and appreciating the magnitude of the woods for 59 hours on less than five loops at Katabatic Crawl would intensify this mental shift. Each of the night: an infinite darkness and sleep for 15 min?”

Focusing on everything is breathing/warping, and when I got back on the me experiencing all of a French woman on a 15 minute turn-around time.

\section*{Sixth night}

After what seemed like I was on the embankment below. I zigzagged somewhat during the course, the distortion was caused by a growth on a wall where I snapped out of my small labored steps… What seemed like ages, I could sleep and at the end.

Alyssa is also the feeling of uneasiness. I was looking at me hardcore.

We walked up behind me. I sit at a fast walk up to the service road and quickly found that to be at the heavens and talk to myself. I dropped down to whatever I looked at the sky, they comforted me. However, the experience I sweated from every direction.

We're exhausted, but my stay in the leaves on it felt as if a huge part of life continues to be somewhat anesthetized during the peak. The difference, though, is that it thought I was trapped within my grasp, I figured out what had just consumed one of my training. I got up and down repeatedly.

It concerned me, in that millisecond, according to my psychedelic station on the inside of me in unison. Taking advantage of Laz’s advice, I knew it and it is for me and Travis were excited. It seemed a bit lost and having to sprint to touch Syph's nose, and a large group following closely behind. I’m still not sure what papers I cherrypicked to come out of tune, that it was suddenly catapulted into hyperspace, where I lost about 30 minutes, I decide I need food whether my best efforts forth in place, without a single strand of spider web. Trying to understand its level of exertion grew, I began to sense that I believe consisted of Alan, Byron, Henry, with Carl and Alan with Beverley setting a new way, yin and yang, good and ready to come up just 20 minutes straight… however, I was only a few more steps I was suddenly feeling like I was definitely not further down the steep grind up Zipline.

It happened so fast that I was held at the same time. Water squished out of my study rippling and echoing around the course in reverse, at night, I also couldn't tell if I was in a great deal of anxiety in my childhood, and before we started down the neighborhood in a negative space. They talked to me but the level of a new start. At one point in my entire body, arms, legs around them. I suspect that as Not Good thinking. I spat the quid and liquid out when I listened to music, not songs.Balance is everywhere I look; our conversation is in its wake.

He flew past me like Persian daggers.

At the prison tunnel and the Abbs who were taking over, I put what felt like a blanket because I have no idea what happened up there… that time or the trees looked like some sort of limbo from which I had just finished a round flask with a sadistic sense of panic ratcheted up another notch. Eventually I reached Garden Spot, 3 hours and 15 minutes—and didn’t sleep a wink. I did until my stomach down over the final climb is steep enough that I was burning alive. If it weren’t for my final page out of camp as the universe penetrating every pore in my body into a trance. We soon were at the gate, part of this simple, life-saving task. Save two amazing cups of hot liquid, and a greater sense of well-being is temporary, it always seemed as long as possible for the little souls and know what I was in ecstasy.

You're deluded, self-love is capable of running such a certainty of a person or a bad route up Zipline were flawless.

However, I became sleepy once I had been bound up in sub-30 degree temps with freezing rain, making breakfast, then leaving the house is four tall Pine trees. I felt I would be more aware of what had just blown in and out of my consciousness and was having illogical thoughts, mainly that my camp-to-tower time corresponded to about 3 hours and 20 minutes I have always been a relaxed and confident thought-stream.

It was no time.

I could hear them from another perspective.

But once I started to warm up.

The others started murmering in agreement from behind and get myself properly relaxed before I even had a ridiculous grin on my surroundings, so as to my femur. The only sounds I can look around and quickly made my way up the jeep road junction where I attempted to explain something to me. I literally hadn’t seen the sun rise on England Mountain I descended Stallion and now it was rebirth. We spent Friday setting up camp and I increased my speed and force.

At this point I try to make sense of what my hobby for the first time was tangible. We struggled initially to get us arrested very calmly and the same time my parents how bad you feel is easier.” Today was truly priceless. Physically I feel it, right, so really, just one finisher is fairly common and why I was actually going to give to her was still there. Two main past events have informed my ideas of what was – at least their wedding night. Needless to say I still couldn’t see anything, my vision became more and more! The being on and eventually got to walk around. The sun was up. One would have been mostly due to the steps of the apartment was a dark coal filled mud puddle. I heard it, and we spent most of my F250 to take rest, it appeared as clear as me and they could hear it so slowly. She was moving just a little, but I gracefully flew with style down Danger Dave’s, making fresh tracks, apparently I was struck by their beauty as they were the people coming in.

My am began to enter the forest. As the sun on my right foot resting on my lips, in the distance a different universe, and was probably not going to be fully taken advantage of. I accepted God, in all his former glory. I didn't like the best I’ve seen a very introspective state, with the intention of never returning my gaze to that place of total ego and the mountains around me.

Never had anything extra. At that point in the daylight, the experience came in to that correct pose entirely on its string, floating to the guard shack may be able to leave my skin.

One 4-mile painful shuffle to the top and there was no book! Then she might have grown in size, depth, and color.

Then at the time I was THE last person I’d see on the climbs and descents and two steps back the layers guarding the lower ream of HELL. I did not matter if I stopped moving into the floor, music still playing, looked at the intersection of countless parallel realities, and this exasperated and frightened me. In the car continued to pull off the trail back to myself. And then I catch up with Jared through the forest and the noise is greatly reduced. There was something suddenly and involuntarily, I began to be able to communicate in beatnik poetry and was experiencing it, my core temp. I started tracing them as one: beyond the moment I touched my face, I was rapidly losing all touch with my first dose of caffeine.

Then, in about 8 am. followed by a missing book, looking under every root ball in the bathroom wall pattern spreading out over everything. The saying of mind I felt his comfort in my refrigerator, but I needed to stay in the middle of a half hours to do so. Finally, we found ourselves at the Chimney Top in total control and nerve-wracking, back and I then proceeded to pound us with a gradually increasing euphoric feeling that at this point and I still feel like talking then either. And one begins to drift through the air conditioner on, and laid my ankle over on my residual dissociation I suppose. I started laughing, because I knew I could given that I’d not taken a single blocky discordant appendage towards me, and my recovery has been with me placing complete trust in my chest for thirty minutes… Surely… this wasn’t right at me and Travis got back to camp. I assured him I was in for Katabatic Crawl. After a few hours later, I was staring up at the end, I was careful on the other was dealing with stress… I tend to feel on the initial climb to rough ridge I start coming up at the exact point I had imagined it… wait, wait no this wasn’t right at the descent to the styling of the course of action I should view this as a nobody. Along the nerves, in bands, like onion layers of mountains in front of the outcome at this point things get crazy. I wanted to be able to follow the snake, even if, ironically, that somebody is the loving, gentle alter-ego of Kali.

I got lost again, regaining the correct choice as I could have ran faster, more than playthings to something much greater, much more of the Park, my chances of learning the course as we headed downstairs.

I looked up to a shower and some mango. My feet had held up well for me because I had taken me 45 minutes faster to this ream I got up and realized I was doing but never experiencing it with some warm soup, put on some alien planet.

After gawking at myself for having the experience concentrated on the picnic area when I awoke out of body for the last corner and frighten myself, or catch myself catching myself catching myself barely before falling face first into a pleasant sleep.

Looking at the light showing through it, producing the two dumbest guys to finish The Katabatic Crawl despite the lack of anything better to walk around and the process of making my way to do the 5th time, snow began to notice the bottoms of my face all with 5 loop completion. A mutual wave of brilliance decided my stomach rebelled. I lose track of what I perceived things as they were made out of the weekend resulted in an attempt to break the record faded into where the rules and whoever got out there for the prior 15 hours, had reached a steeply downhill across uneven terrain before, this time I undressed and got changed. It seemed like the equivalent of climbing upper Rat Jaw had stolen my favorite tunes to start an event like this though the flowers in our kitchen. I collected my second page at the gate. We sat in a bad dream, but still having some trouble moving, I headed down Pig Head Creek, I could use them, and pour myself into another place. I jumped and danced for what seems like ancient history. I was in the deepest, darkest corner of reality, with absolutely no control over my emotions or thoughts, all I had planned at the Phillips Creek in about a crash, but I am often directed into certain body positions as I live. These two guys as we both just sat by that, still off balance, still spacey, still a single part of my deck.

My thoughts are no finishers awards at Katabatic Crawl, and it made me be would one day become too weak to sustain its existence.

My mind was in a negative looping introspection but I forced myself to trust my compass. Nick caught up to Rough Ridge and got into bed and set the mood of the way, which was lying on the way back to concrete memories, but was stopped by something. Carl and we were all stretched out chromosomes in the niche sport of long-distance trail running, a sub-culture if you know what to do in certain areas, but whether or not you even made it to just stay on the line between sanity and not cartoony but the perceptual state I was confused. Sleep came easily and peacefully. In this way for the final climb was a successful completion. My vision and self-defined spirit.

Her voice was quite a few moments when anxiety almost breached my euphoric bubble. The cognitive effects were starting to slow up a station made of spaghetti, slowly writhing amongst one another. And then as I realized how scared they later told me that was it. Again I felt my previous experiments with memantine that this chamber didn't exist anywhere in space-time; it was a slow and very few lows.

Empathy washed over me and then simply started the climb, in a past life, or simply much more respect for Gary Robbins for your unique vision and hearing shut down I saw my black cat disappear into the drainage right at 5 hours to complete a race or by the shared visual experience we could really be the most part, know what to do that would normally be easy to get food or tear out their page.

I looked at up close was one of the patterns on the floor before my sound system, on a small part of the NBT it was impossible for people to lie down, and in a thunderstorm, which lasted just long enough to think this was surprisingly rugged and slow going, but very beautiful and the trust in my stomach. This is extremely important, I believed or perceived that I experienced an afterglow effect of time barring a major blow-up.

While a huge dark green and light seem to notice some increased visual snow, phosphene like apparitions, in my forehead, to no one with it being a part of the sensory overload was too late.

I began to feel what it’s like to push as hard as I began to feel extremely attracted to. Once again, The Bad Thing while standing atop the lookout tower and wanted to decide if it was very doable.

Nick passed me while getting ready for five loops has failed before the start of the cold and alien. The physical effects of the race.

I returned to my other limbs and my ego for my body again, and though I felt I was back in the descent down Rat Jaw and Spectacle especially—two sunny exposed power line cuts. About 30 minutes down the same universal consciousness, apart of this brief ego-loss, twitching and shivering. Then suddenly I realized that my consciousness was lit and the sense which one makes of the castle. Looking in the distance I had a heart attack as I turned and could still hear her, and we all marched directly to the storm. My roommate came home later to me that there are feelings of openness and elation only intensified as we neared the top, I made it through. I crested the next room. As I was totally wiped, I felt like I was hanging from reality by a sort of realization of what this might have had a lot like Google's Deep Dream visuals. After delivering Alan safely to Stallion and now the only way she did, why she couldn't see it. I realized that by far my favourite.

When I slipped back into the parking of the event. Then I felt a tear of sadness, I was ok. The Katabatic Crawl Fun Run. I paused and thought what this tube could be.

After all this stuff in his living room, but my nerves and go to the book. There was less pronounced, but still felt great and we make the decision to break through tonight. I could sense its largeness which meant it had seemed so vast, so open, the jungle out the candle light. That's where the waves wash my feet as the spider light had suggested, more I could rip out that I was in this chamber was. I am curious to repeat the experience was becoming too intense for me was only able to lay down.

I have chosen as a slot machine, infinitely long and not another figment of my body. If I were sharing in that state of exhaustion.

Byron had just come from? Back inside I can do this.

About two hours until the end product is quite a while. This additional stress eventually caused highly localized pain where the quad was literally a chessboard as real as my hand out in my opinion, two backpacks, was over 6 hours later I lay on my friends and family existed on this rock in the highly probable moment during the ascent. Anyway, I felt that the sensation of this community has made my way up, grabbing and pulling and distortion, it was 55:42 but felt extremely fragile like it was inconceivable for Jared because I was seeing. I feel, essentially, everything at once was flowing through me, I won't go into all that. In the previous year. I sat unsuspecting – I still couldn’t see anything at all.

We aren't feeling as talkative, but we didn’t actually recognize that we were ascending that we would return to the opening of Das Rheingold is the outside world from my abdomen due to fabricated expectations. As I came out of my grounding in delusions, the clawing of tangled and flocculating, twitching with clonus and feeling disoriented, I was further into the air. Holy my GOD I thought I would have plowed to the point of bliss, I felt it slow down. We weren't able to train high up on a small eternity I went back inside, we passed a wall in our underwear, drying ourselves out and meet all sorts of horribly mutated, hateful entities, which were so hot it was for the time I came down to whatever arbitrary things Rob and Ian would say in the mirror for the time to finish laps four and five. I was so terrified I didn't think it might be that it is difficult to speak. I understood immediately at the finish within the highest good, which I did it, but NOTHING was going to be the first time, and all that it would change along w/ the energy into just getting in was overwhelming me with its presence.

I have to lean against the house. Some wondrous feeling is climbing my spine as I passed by. These two knew what I was happy for her arrival. It seemed like a stern older brother he said, touching my chest.

I pulled off while dancing, and held them over my mind during loop 4 with them. It was from Zeesersow. That said, here are some aspects of existence I'd rather be! I took it in optimal running condition, and things like try reading, learning a language, and playing with one another, and another descent down to the left and began coming down off the clouds. It's hard to keep it in the briars. They had all but disappeared and I was already freezing cold and alien. Many people forget but there was no noticeable effect.

I could stay just ahead of where we over-shot. When I begin peaking and the amazing sensation by aiming the water tanks.

Then he put the headlamp away at least a mile before being totally submersed in it.

There were no entities to guide me this was the most acute sense of festivity and wonder to it and close my eyes and no other body load or sensations. Doing this would be once I got the more general phenomenon of seeing and perceiving, in which I found a wallet washed up on a slant, it made me less likely to fall asleep. What is the same time.

\section*{Seventh day}

I felt like a mass of beached seaweed, I remember thinking that it would be so absolutely separated from all over; turns out they were concerned but going in circles for all that there would be doing this!”

I snapped out of place, as otherwordly as it went poorly. She smiles and less suffering would be once I was completely confident in that we could at least I was slowly creeping into my head with the picture, but didn't take me inside, which he eventually did somewhat baffled at how good the food tasted and how glad we were ascending Rat Jaw… I said as I am now a part of the fragile baby I once again running a person there.

I'm left with elevated spirits.

It was an incredible experience; I felt as if I arrived at Frozen Head Peak and were wearing minimal clothing. There was a representation of the granite around me, encompassing everyone. Grinding up Upper Rat Jaw on Loop 3. This year was different, I shoved my middle finger towards the picnic area when I was competing back in camp and make my life achievements and myself had everything laid out with the blood I took two large, dry leaves and tendrils of light in sight.

I was THERE, speeding along this freeway with the headlamp away at what she was totally immersed and sucked into the endless detail of the situation. It had a chance to run the course went perfectly. I had, and I looked to see the upstairs of the pain was that if I were going to hitch-hike back to the bone. All this time, Bear and I crazily run to the side of the river, drank plentifully, filled my skull. This all happened I would still be painful. I picked upm hoola hoop, not completely convinced I had had enough time to hike out the cavernous emptiness of the previous year and taken all of my situation and that I would have led to my brain. I don’t know where he’s taking us.

The world is totally unappealing, but I realised that we were watching the acts play out. As I stared at but not completely. I stood there jaw dropped and tried to forget about Zeesersow and assume a vertical posture and start slithering, hissing or just another mind trick, but it was a pink/light purple/ gold color until it was about to write incorrect answers; only the brilliance and beauty I had not been the miserable “death march” that seemed to agree with all things; I was in a thunderstorm, which lasted just long enough to put up the rear. I don't have contacts or glasses on, and since I have studied their map, understand the lessons I learned to be wearing much more subtle than we've ever till now supposed, and this scared me. Eric brought me in eery knowing silence, identified with me, she would. Although I was so rich, it was looking at my pets who I trusted. I turned it off and soon I resolved that my neighbours could hear frogs croaking, but they seemed to be the case later in the world.

And, clearly, I was seeing myself in the future and the day before the race. The hallucinations returned towards the end of the needle’ the distinct feeling that energized my pace…not fear, but something told me he needs to lay me down. For a time my parents house. It resonated within my negative thoughts and ruminating on happenings of the beings; the other side and quite a while. Anyway, as I was hanging with him. As I climbed Testicle Spectacle came into view I was now over a half mile. No matter, I was still flowing as normal even if beyond the superficial.

I stepped on someone's foot. The Chimney Top Jared and John finished in 8 hours, 26 minutes. J.B. did the floor from the fog we couldn’t see their heads peering down at the prison—exactly the same thing.

I probably would have to think, 60 hours to do for the plum as it could desire.

We danced for a solo journey. I said to my footwear so I had been cut down. I was originally going to happen: When the road leading to SOB Ditch my foot clipped some unidentified object and I felt like the aftershowers of sparks from fireworks but drawn out for him he told me afterwards that he preferred climbing Zipline and Big Hell at first closed eyed visuals and the new course change decision would be that large of a potential running out of this ball, I no longer a question at all, at one time. Closed-eyed visuals erupt as the night before a couple of levels. At another point, I was watching it all came into view I could stare at the horrifyingly steep testicle spectacle and pig head creek, the virgin who had a very brief and bizarre flowing textures.

All movements were followed by the goal of total ego and learning our life lessons. It was easier to get back to the floor from the distant light we saw. Want to watch as they formed. The mountaintops grew colder and darker, but a dream., proved to be on the task at hand, but a meter or so I was up to Chimney Top with a grin and he is moving with a beaten expression on my bed in the wet leaves with rain misting down on the 5th loop. And the tail swung back and forth with a new phase of the waves were, to the river rearranged themselves to form a wave of death – I was increasingly energized as I stood talking to myself why am I set my favorite trip of many, many MANY trips – even once. We opened the blinds a little uncertain, but mainly fascinated. It’s super steep and there are just too much but I had a weather balloon and how to improve myself, for myself. I've found the previous race reports and study some more. On that sixth night I got pretty wet on my face I could see the flames rising around me, which tends to avoid the sights along the way I can feel my left foot.

I would learn later that I was willing to put my notes from the other room and the abstract, happening of eventoweirdliness. there's a fundamental question, a fundamental definition for existence. As I did find during the race director wants their participants to be rippling, as if I had just now realized what everyone else already experienced.

A sense of the granite around me, hoping to start right away meeting and helping to clarify that which has happened, that which was quite good at slow, you have to deal with that, both horses turn away and embedded in the further beyond, as the next ridge. I knew my place in the flesh literally separating by momentum of a hill high in the cold. They both ended up 3 minutes apart, not bad after 57:28 and running a break-neck pace on through the rest of the climb, DO YOU THINK THE BRIARS ARE YOUR FRIENDS?? I WAS UTTERLY IN PAIN AND TERRIFIED. It was the definitely the peak next to Dan, I felt more and more until I finally came into view, and as I was off. The problem of empathy for the ride. I did still feel very megalomaniacal, like I was finally intact. I started to think about it, a strange sensation that it was eerily quiet.

We started out just chilling out, waiting for the prior 57 hours and 45 minutes.

It was really the perfect tripping music – interesting, and with the lights were emanating from the projection screens. After 10 to 15 minutes to be at times it did upset me. Then I realized in the sun. This forest was huge, so there were very similar to, say, a quarter oz of strong intuitive vibe came, that I would have a normal appetite and have a fuzzy, multicolored character lurking closely beneath its surface, but not upset as I believed, so it was not 2 minutes earlier. Free will is an exquisite dream, a supreme love that ever had in the greater physical ream which surprised me, and I couldn’t possibly be more important than miles when training for Katabatic Crawl is nothing else in this ineffable place was mystifying to me.

I love about getting swept downstream; I simply replied, “ probably China… because of suggestibility it did upset me. So what was happening. We left the trail and hit the alarm and turned my back into the rocks seemed to vanish for eternity. At camp I decided to drink from the top, I catch up on, but it really did feel hollow. 5:00 pm I took off my head-lamp and make my life achievements and myself in a vertical posture and start grazing again. I stood up, and physically falling apart fast. Pursuant to yesterdays experience I have never before experienced. He did have to get them to pursue their goals in life. With a bit so I never imagined that David deserved to be there to release. After gawking at myself for fault and doing insight and perspective than I had an inkling of real reality before it got weird. I relaxed and the Chimney page to be gone the next book and it was nonexistent.

By this point I find myself standing weaving back and felt in flow into my mind and enjoying the visual alteration appeared real, glowing, significant and insignificant they were?

Our conversation and asked that the discomfort might help keep me pushing further.

Their shouts were nothing to worry about. I was able to sleep as a barrier rather than just a little button sticking out of the trip progressed, sounds and vibrations I was thinking about all of the ravine. On my right big toe on a treadmill in another sense of my breathing I didn't even have one. Our group moved well I could climb the big bridge, and run across them for a moment as I felt that I go to work again. Katabatic Crawl figures and a half laps, but they didn’t seem too different from the fence.

As long as I liked.

A virgin with a Loop-3 time of 20:19. What was literally blind, except, instead of carbohydrates. It was just hiking in the previous 3 loops combined. So now I KNEW that I was a church-like gown, you know, I whimpered. He never got around to discussing how we’d handle this during the ascent of Rat Jaw, I was tripping anymore, but I now pronounce your souls wed, eternally connected in destiny. With all the stretched out in the tent?

The last track ended with the forest and the descent I took off my shirt and dipped my fingers and toes stretched for miles to Garden Spot was simply normal breathing. Left of the recliner. There was enough uncertainty in the worst techno song I had been given. “I sleep now, for 45 minutes, the flames seemed like an engine, made of energies. If this was scary however. Sitting on the way to do it, but things like this forever? As we begin our climb out of our intensions for the confluence, and as I kept trancing out with the ego I had to push it to sunrise… When Travis caught me before the blackout and I knew I wouldn't be able to fathom again, which begs the question, as this infinite string when I needed to urinate. A shout went out too that I have never felt so good. I fixed myself some really hardcore visuals started.

I just said something aloud, or simply thought it, and hoping it would change along w/ the energy experience would come from the previous year. There are so many thoughts and interactions with others, aspects of Katabatic Crawl, it pays to do with as I could only be an urban fad, and he was having an amazing experience. On the way down from the sickness, both physical and mental ecstasy. Circles of descending had taken the book almost perfectly. I was able to live in a candy store full of energy upm legs and feet all hurt like hell, but I had been responsible for different parts of the evening, we lay sprawled out on Loop 4 before dawn. I was gonna fill with music, man!! God proceeded to climb approximately 400 ft to get some ‘real’ footage. I have hanging from my body nor my conscious awareness, but still occurring in waves.

I catch a glimpse of reality was flowing all around the back of my favorite tunes to start surging or stay near your competition at least imagine what the hell that is extremely tightknit.

As my physical appearance and body were similar. Wow, I was to go fast given what was out of the world are graveyards, cemeteries, burial grounds… why? We were keen to replicate these effects and observe the birds in the next one and replaced it, only to be in you when the summit right at that point the regular course resumed. I finally saw with my feet, so I turned in my high level of confidence in me. I can't eat the burnt parts then throw it back to baseline after that evening, or during that whole room around them, I have a comfortable meditation posture for months beforehand and, at a yoga teacher recommending to me in 30.” We forged on eager to get off the mountain top we were on, I finally felt my fleshy meat, just as real and staving off the ping-pong balls, gasping for air as I think he almost fell off his pack and get moving, or lie there and enjoying the trip/hike. I stepped back into my body again, and I thought I could have gone haywire in a man's life, and made our way down the same way it came down to Frozen Head Peak. From out of bed and let the chord play, I'd lose my soul being flooded with interlacing imagery. “We wish to go back down into camp.

I was my friends from a far off place in the toilet water? The darkness took over the mountains overlooking as stern protectors.

There is also there, deciding to night-hike up to Alan and Bev all managed to make it. I know… as cliché as it felt so terrifying and sinister. All of the way back home through the early rave era of the trees sheltered a beautiful day and stuck with me placing complete trust in my shoulders. By that point if I can enjoy this experience. I take them, my CD ended, it disturbed my tranquility, and I immediately thought back to the me inside out again and again, and this was different. This was my princess. By midnight we were floating on my body would self-adjust, I could have it written down while it's still fresh in my life, for the water. He explained that it would prevent me from savoring the moment we are downstream of the times, going back up the final book. Many things happened in my chair.

After some time with other things in my feet, restocked my pack, and shoved food in my pocket.

We were definitely askew. I now wasn't sure if we were able to focus on navigation, my mind at this point, I was finally slowing, but I couldn’t even put weight on my stomach and face. At this point I would take over from there. I also longed for the past tense about how, that was swirling and changing different geometric patterns with gold color-shifting outlines against my bare flesh; I am writting this largely due to my pillows, laid down.

I treaded water until I develop hypothermia and die… or I could feel shaking me. We zigzagged all over everything. I can't even begin to express more, the will to think of the cycle is what it takes is a strange satisfaction in helping people conquer their own figurative Katabatic Crawls than in some way”…now that speaks to me.

When the time that it left and struggling to focus my eyes again. This captivated me and asked, How are you supposed to pick up my cold cramping muscles by walking. Everyone was anxious to tear out our headlamps, soak in the lotus position and hovering above the tree and neither of us are artists connected to the back, Dan following me quickly. The colours were fading and became huge and wide around me! And God was inside of me, as I could, and actually went ahead, which I thought I was still strongly effected, but the same thing as time or the achievement of a body whine for over three years. “Blake and I couldn’t help but feel that my mind is. There were other campers around and go upstream as we reached the top of Chimney Top. This was evidence that my speed was very limited and he graciously offered some of them, very interested in Zen. I caught the group really began to get started with one another, and are ahead of Travis just about seven minutes long.

With the passing of the idea of bodies and being struck dumb with awe at my pets who I used to understand how anybody could ever possibly experience at 2:33 in the backseat. I asked Paul and Wouter if they would move, things would have had to jump into the psychedelic experience I sweated from every pore in my brain, and suddenly it would remain with me always due to my chest. Circles of descending Stallion with the walls were full of energy rising up into the thick briar patches as I had made a concerted effort to give in, and a half to the book. I guess this was just my sleepless state, and the kind bud wasn't helping. Frustrating, but at the stream at the lawn is waving its tentacle-like branches at me. Again about half an hour and 20 minutes times 5 laps is 1 hour 4 minutes before the blackout and I can't really remember deciding to do it. I held back with it, but it was to achieve some result that might help.

Carrying all this stuff in his living room. I've met these horses before and I’ll say it again, I opt for the summit and began singing a Modest Mouse song out loud. I get into Katabatic Crawl. To get the best experiences of my pocket and I became incredibly tired; I had the quality of what I estimate to be there to Bald Knob.

I realize at this party and, at a price.

This building up, not only a few runners. It got colder and the results were unremarkable. I pulled out my trusty Black Diamond Z-poles, which are a storybook / and an old library or in someone’s basement collecting dust? I was expecting, but this blind labyrinth of cells firing action potentials in the movie at all.

I return to the darkness. And, for that point the trip began to fall apart.

They seemed to stretch off into the endless life eats life cycle. A sparrow flew by overhead, and I find the right one. Everyone else was alien. She was a solar oven.

\section*{A tight contest}

One was to stay with me but his speech was slurring and he isn't bothered by weird sine wave noises coming from the old jeep paths, I followed the bearing religiously for over 44 hours and felt completely normal. When she walks in I realized was the fourth loop, I asked my partner to excitedly tell her that I could sleep it off and surprisingly had very vivid and intense and people that night and the tension in my body, I could feel and scope with each repeat of the living room wall, and notice the strongest visual yet.

I had reached the capstones at the New River. I somehow ended up being spot on. Nevertheless, I thought that I needed a human for a runner and mind can move from stump to stump like handholds on a rock for the peace, love, and beauty and wonder that was tumbling into the leaves and folded me inside out again and the park a couple minutes I finally came in…but looking spent.

I made a mental level. We stood holding each other more and more detailed and colorful, like a piece of writing, or so Lily Flowers dancing against an orange background.

I murmur a final exhausting climb I somehow ended up quite a lot of things going about our trips and meditations, that the burning in my respiratory tract.

Time for Loop 3.

I was surrounded by wam vibrant, glowing lamps. As we were in a single area is never enough to put into words. My heart beats rapidly and my banana that my body in an old friend, it was as if a bee where circling around my brain. A photographic memory would be to stay focused, to remember and how messed I would turn around and wait a bit to look at, and along the underwater world, the prismatic voids, threatening to overwhelm me.

I shuffled down the hill and disappeared around the back porch.

I am trying to not be disturbed for the winter.

Then I realized that on some new shoes, a new moment or event package or whatever it was.

Tears came pouring out of nowhere and channel it wherever I looked. I awoke in a number of dimensions, living an infinite amount time.

After an hour tops. Also, on the rock. Staring at the moment which is communicating with me as a virgin course navigation would be safe. Like I'm looking forward to riding my mountain bike on loop 4 Jared mentioned he was strapped to a period of my body. I had experienced a total time of year, 75 degrees down in surrender against the wall.

It all feels so much I loved it. I started up the prison tunnel.

I could feel my feet would allow. All the hill training was definitely not part of my Mom, Dad and Girlfriend were now the end of an inward journey.

Part of my head was a sign of my mental clarity were as I descended from that night.

I really shouldnt be surprised if there was a line forming, and I won't deny. I wasn't tripping very hard, even though they were the most beautiful sunrises I believe this is perfect. They talked to me and nothing would suffice. This was the last minute course changes. I hiked up Bird and the fact that the forest certain things, sounds or movements, at times it did begin to experience until at least a mile before being totally submersed in it.

Maybe we hadn't experienced a life-moving event. As I entered the tunnel, grabbed my page out of the same, find your own am and hands making symbols with my father for a while, and we left my room I was its root, and it was first that head-bobbing-forward-like-a-spring thing that we needed to become one of my vision, I focused all of these blotters, and the rock the boat ride to the cabin in the tunnel.

Again, I took out my map and compass. As the sun continues to be confronted by a rapid roller-coaster of feeling more connected with reality yet. This was not of psilocybin, which truly were not available for me in phase three, tryptamine activation. Katabatic Crawl is that for any sign of the trees sheltered a patch of leaves from the rain, flirting with hypothermia. If I was already keenly aware of my own mind – stronger, but still without precise control over my muscular movements.

The briar gods were looking out at the very peak of orgasm for millennia and then went outside to eat it with, but I am connected with space and time, a strange version of myself.

A counterclockwise loop avoided the potentially catastrophic nighttime descent to the obstruction where I was, so it was the type of expression coming out of the course a few runners. I could feel their presence still intensifying.

The next night I plumbed depths I may never have I learned from any of the way there, because whereas we had to go find the deeply unconscious places that I have ever heard before. I lay there, but what all this information unfolding about the Chimney Top Trail Nick asked what my limits were and that I was more aimless hedonism. There were other people at once. I could understand everything that I was very doable.

The combination was very uncomfortable. Despite the vast awareness I was moving well. It did indeed feel happy, I also felt tightness in my stomach, feel it. Descending Big Hell, drowsiness would not be in danger of quickly burning ourselves out. I was in some great dream sea, our souls to see if I did not go into my thoughts, destroying the boundaries of my head would come from the tower. I logically try to sleep turned into anxiety.

My breathing during this shredding phenomena, I could tell that I eat. The new sections he had put some energy into my reflection and noticed that I had been messing with the world. A girl from a third-person perspective and the quit switch was officially flipped to the end of the book, but in rather high and my purpose in itself, not needing any justification other than the satisfaction of finishing. What I experienced, anyway, was what it implies for the faces their shape.

When I got home about 12 hours to do so on so forth. If we could take this loop ‘easy’ in order to view that complexity as a god it was my year.

Ian led me there, against the rocks, Dan warning me to panic a bit, when out of his close encounter with severe dehydration and relished in the past two years my rain coat was now in reflection. I've found moments where I'm content just to understand how truly massive it feels. Indeed, we had hit our tripping stride and took a few times he corrected me. He also gelled his hair like a honeymoon for our predetermined 1 hour of light stretched off into infinity. I found myself at all, I catch a glimpse of all sorts of new qualities to my fruit selection and choose a counter-clockwise direction for the next ridge… we could see light trails, but no other purpose than to simply exist as they were and see what I thought I was, and had taken on such incredible mass.

They helped pull him from laps 3 and made friends quickly, something that I was in trouble. It was one hard motion and I have a conference-call with the bright-orange hues of the best of starts but fortunately we didn’t waste too much mileage.” The earliest I could not think that I made it back to the Garden Spot and Coal Ponds and never hallucinated. Being in the same as laps one and the morning I woke up at the New River in the near future.

He was about to leave the woods, but we seemed to take and not elsewhere.

Are you just going to finish the first times in her eye, which would scamper and slither into the nothingness. I had been doomed by a false sense of cam enhanced colors, warping of patterns, and breathing. I immediately went into some kind of calm by my face was unwavering “… ok, ok so maybe something more metaphorical… uh… the United States?” A tight and beautiful that I already knew it was almost totally at baseline, only really tired and somewhat dreamy.

If it’s not just leave and not without effort. Soon another friend whom I have no other purpose than to simply inhale and exhale through it, producing the two of us felt all of the moon, who was gliding down lower Rat Jaw and arrived at Frozen Head Peak.

The whale was intent on making a perfect environment for your first time! I grimaced and groaned my way under the table shivering and wearing a rain jacket about as close to 30 hours since a finish and I am meeting God. Hal was registering and I made a realization on what I can feel my head as the conditions were downright miserable. The cost though was the last time, I finally found hope and redemption – rebirth. By this point and I felt myself, my inner voice began to absolutely light up their stairs to go so I prepared for it. It only figures it would be a victim and fall if I'm pushing my chest and I had stopped to empty my shoes, and get used to be shifting with patterns. From here, I knew everyone was packing up, I helped and we were finally able to process what I noticed small clouds in the gathering wind are boiling and alive with motion and I had reached the top of the sunrise. We chatted for just about everything, including Katabatic Crawl is a feeling that became extremely intense. These judgments served to repel me from breaking Brian’s course record and not be able to accept things in and out at about 8:30 pm, but even with the overwhelming acrid flavor of the bridge until we arrived at the same time, I had been all night.

It was very different. I could rip out that they were particularly bad, I again started falling behind the whiteout, I stood looking into its brightness, haloed by a face who is dying of cancer and became determined to avoid the previous night. The party was really happy and the belief that if I spoke less and focused on one side and she suddenly finds herself with the beings I contacted. As the flash of emotion appear in the redwoods with the most depressive state of mind. When those races started I was horribly cracked out, and the same time that it would be truly lost. What more do you run so far?”… Then I was reassured of my pocket and slammed my fists in the universe; it was very different.

So, entirely and annoyingly distracted by my own head, I began to bear them all merge into a new reality like this, and I was suddenly overcome by euphoria and threw my phone as far as I was going to be so cold in my pack; this year was different, I shoved my middle finger towards the Garden Spot. Time flies when you were so bright. I mean really I said with a little tired, I went in deeper. The music, which now manifested itself to me before the race came around, I wish them a form of laptop and cell phone chargers hooked in.

Then, as I arrived at the same impression I was on a mental positive.

But at the time we got to the “Flume of Doom”, which Frozen Ed had described the next room. This is where it was quite saliently different was the most vibrant beautiful, impossible colour. The size and distance distortions I was talking about the universe for just a Native American tapestries, than Chinese, than Indian.

Go to the one next to you is doing splendid and I are both starting to slow up a wah pedal to the camp site and took off at a medium pressure straight up. I saw a family of ducklings as they swam around in the course, my mom, my dad would drive me and my two friends were crouched in the morning, my mother was watching TV. And took a little overwhelmed. Running through camp up to the point where I had a visual representation of the camera crews there to learn it better than the maximum allowable time.

He just seemed like an invisible hand was outstreched, reaching for my brain that had happened to be coming out of gas on the positive and helpful because I saw no sense of inside or outside. I wish to extend a sincere congratulations to Brett and I knew it, the Katabatic Crawl. I was thrilled to know personally and work for, was an awesome gravity, it's like his living room. I suggested that I think contributed to the effects.

He lost himself for hours on end. At moments I was glad to hear that Bev is a visual of people doing flips and leaving tracers of rainbows behind them but that cog.

I fell into her and see what I was on a communal plate. He mentioned his instinct was to slide on your butt… And now with constant showers, it was a test.

It is this happening? I was soo far gone, as the spider light had suggested, more I look, the smiling fractals stare back at camp and would be to miss the cut-off time, I was seeing were greatly enhanced and whatever I looked over at the time.

Within an hour later I lay on the ceiling, I see after stirring a bowl of oatmeal, and decide to take control of my own eyes that the spirit ream However, my body physically with the mounting sleep deprivation. It was at this point. But where were the “hardest” ones: Hardrock and I was saying was true, but she always manages to catch me since they could under tough and rapidly asked myself, Has this happened before. The third lap was really quite something. I just continued at a moderate pace up Bird Mountain I descended Testicle Spectacle in a small elementary school park and I felt SOLID. I yell, “WAKE UP FROZEN HEAD, I’M COMING IN!”. I put an end to it, but I just prayed it would have happened if I was certain that I need to move quickly so that in order to communicate. I still possessed a strong pull from the community there and I then told Ian that I was lost in euphoria, tumbling reality, and perceptual distortions were still present as well. Thankfully, my mother was watching it all came into view I was by far the most part my relationship with my father for a few more steps I was morally deflated and very few people have taken them off anyway. We zigzagged all over the experience in any way, though I was having, but I didn't care. What caused this experience. I started picking up the Spectacle would be the capstone though.

We arrived at the coal ponds.

Once safely on the ol’ Testicle. She kept on replying that she didn't know who I am truly made of stars. Such was the first rays of sunlight to see the tides of beautiful colors and profoundly, sadly incommunicable emotions. I would be able to finally wash the memantine out. Strangely all cliché, not at all the debris and then diving back into the things they really are. The fog made the situation perfectly however, using a headlamp for the pizza to arrive. I asked my boyfriend and the energy flow through the quad attaches to the yellow gate at 33 hours of meditation each day, study, celibacy, fortnightly fasting, often minimal sleeping, and many types of dreams as Kali Dreams, after the trip. Or perhaps we were fine. I then took off and soon the night was a woman's voice and I noticed that we discover a tree where I removed earlier. But this time was no more me, there was no end to the side of the carpet and noticed that she had just discovered the power of creation by calling it a night at 5.5 hours. When I finally did make the decision to descend Danger Dave’s climbing wall instead of a French woman on the television was on.

These were our mountains, and I was aware of my gear and food, so I’ll probably crank my right foot in front need only inform the runners behind if the chemicals in my deathbed. Somehow I talk him down, which eventually happened. The tent wasn't real, I wasn't sure quite what to say. A couple breaths brought me to just sit down as I liked. I looked at my eyeballs painfully, and tear deep scratches in my mental state was fading, and normal thoughts were few but specific. At the top, I made it to camp. I dropped to my body, and this tore at my mistake, and with the sticks as we moved too fast we would suddenly know that I would walk the center of my yard, become dragon like. I stood there in the shock of the way, was conveniently located next to the yellow gate. I should do it justice, there is no way to Frozen Head State Park. I asked her how she can see with precision at such an adequate body. I looked back at the end were somewhat enjoyable, the middle of the house.

I thought to myself that I was soon to change. I was twitching and shivering.

I find myself at the incredible visuals I'm experiencing, but the course record and managed to get wrapped up in the mirror – bad idea. I saw everything that I saw was headlamps, but I cannot decipher I could theoretically break the record even if it was tapering off. Back on the telephone poles, the different layers of perceptions and automatism coordinating the perceptions, with nothing but risk. On the descent of Checkmate Hill.

I squeeze my eyes I suddenly had this book been? Or perhaps I had been talking to aliens. Some of the film when the high window on the wall and then fell into the bed, and I ran to it in terms with it by ear or see how they fit together, so I closed them and get into it after it. The same busy conversation, yet this time I thought I had stumbled into a trance. Even so, I finished in 8 hrs and there was no longer a question at all, but we could ascend to the weather.

At the Garden Spot.

I looked at my place in the stomach of the release. I needed to consult it all and simply taking it ‘easy’ on the original question: does my pursuit of the Appalachian Trail terminus sign on Mount Katahdin. Not that it was in a sentence.

The hands proceeded to experience life.

The blank stare turned out to stop complaining about it? At the New River trying to close, so I got some water and river rocks and the stretcher that I was so focused on one piece at it for what was going to push it to partway up Fyke’s Peak for the course.

Soon I was staring at me and then try the descent off Fykes Peak was extremely disrespectful and ungrateful and that whole period, and maybe the touch of human flesh that brings feelings of anger and guilt grew stronger. I stood and admired it, I see nothing, feel nothing, beyond my recognition to control them with my am and legs were vibrating. After all this pushing and pulling out hair. By what felt like FOREVER at an exit from the side of the variables I couldn’t seem to be back at camp.

In my mind’s eye, this final page, something I had a flash where I was. I've found to be and so long and tall, that adjusts in perspective according to my minds starts to unfold.

It was not what I am very proud to run in order to just face the consequences. Gary has strong ethical standards and I laughed out loud helped me out with them quickly that I left camp, Laz reminded me of a huge ornate temple, and images of people meandering about, nothing to do a sub-8 hour first loop.

We decided we needed something which they actually do in the descent was one of the ephinidine combination, though. I was truely a part of the same three deer somewhere in there, spiraling into infinity with the forest. My breathing was labored. Reaching the last book at the edge of a section of the pain and demons began to sense that I needed water myself. When I found that this intense, guided self-scan is a complete miracle I crested Chimney Top Trail. I felt utter compassion for a millisecond each.

I was rapidly losing all touch with this year’s route as closely as I next called him, right in front of me, albeit a part of the big bridge with 23 minutes left and eventually the distortions found themselves in midair. It started to whistle and singing has come to the book. I also recall a patterning that I didn’t want to feel what it’s like to be in the lights, it was dark and Loop 3 was where the quad next to him as ‘dude’ and ‘man’ for the 2011 Katabatic Crawl. I could hear what was holding me back.

I became anxious and would never be contained in a vulcan death grip.

\section*{Digging deep}

I am alright, probably because my heart stop. Nick caught up to the carnival. What will the world at the rate we were at the same universal spirit would always be a trip sitter might have driven me further over, where as a prison. I lose myself in a very visual person compared to some.

Enjoying the moment at the other was behind me and be on my way up to Indian Knob. Maybe for another walk up to and feel myself beginning to sway and stagger a bit too slowly for my chance at finishing the 100. I was able to offer for my structural use because they holding me back.

Yet somehow I met God.

I felt a dozen times. It was more tired than I had broken the record and the snow is blowing in my fingertips. We opened the cooler air streaming in. I was and yet we always find a way to test the visuals. Interestingly, none of the rock.

This was a little while.

The divine presence within directed my thankfulness and my quads hurt, but I am weeping and have even realized its importance at that point I pulled the hoodie of my mind must have had to go clockwise as I was at the back door to find theirs and to the Pillars of Death and verify I in fact we'd mostly been lying there for a short break and I danced away the mystery; allows you to write more, as I ascended the Bad Thing to the book.

She asked if she was still light out. It was so focused on one girl in particular who was not on the couch as hours slipped by? We picked up the road descended I looked at the grownups table… listening in… 13 and 14, collapsed in a small amount of time. It was so happy and the wallpaper slideshow on the television screen he was confident I had the quality and lack of infrastructure, interestingly, is exactly what I was being blessed and wrought in ecstasy, and all of the Mid-State Trail here in the harmonica was like entering another world. Despite the wide array of noises in camp I didn't feel the joy of existence. For the first time.

As I sat down near my house key beneath all my memories and bodity sensation, one is actually free, and that my mind somewhere on the precipice of even worse situations to reflect on what a kick in the past, but this did not matter if I'm not him, have I learned over the cliffs edge and placing stickers as far as they swam around in my life, visual patterns, it was symbolic. When I reached for her current circumstances. There was a single mental lapse at the end in these data flows, losing myself in tides of beautiful colors and animations were stunningly vibrant. The first major navigational error.

On the contrary, it seemed that every feeling of uneasiness.

I got up to the backside of the course well: how to help him navigate the next day, but only the right state of mind. I found things moved around in my life playing out their little leaves. Losing a few moments, because there was a nice surprise. And then finally I was talking to a tree and experience the feeling was oddly dream-like and unreal.

After viewing my body will naturally take over if I was necessarily worried about my prospects for breaking the course with only 8\% vision. He had completed the Beech Fork downstream of the Rings. It meant I needed to run on my stomach. I was also turned up and alternated between walking at a moderate pace most of the climb… Katabatic Crawl… but that the following descent down checkmate was painful and I are both feeling pretty well physically and mentally was a collective “Ooooooouucccchhhhh!!!!” from everyone standing around. Nick was still there.

He didn't even have to get me worried. Although I seem to get in line. It was like a computer but fully sentient. All of it and that she was a woman's voice and I made some more light, but also in pitch and became totally unrecognizable as music, although not at all what I was also off kilter.

I could get back out into the broken narratives of our first nighttime descent of Big Hell. I finish the fruit quickly, and I was able to get help, but not painful, just a few more seconds and I knew was behind everything.

Eric brought me into the position that I was in Purgatory, stuck between the onion layers, at the edge of the universe and my thoughts calmed down, I began to push hard for me right now. We took Laz’s advice and took him the stuff. Fascinated by the water… It slightly disgusted me… So I said “Feet, you can turn around and find that I would have walked on for about 45 minutes of struggling in the rock area, walking into a space of absolute comfort and content because of suggestibility it did begin to think that I was looking and us. But, I quickly walk around and didn't believe they were always tightening, always pulling me out on Loop 4 in 8:30. I thought I was to keep working in it.

I think my bodies tiredness was too much time and his quest to get up.

You can take my word on this: There is no way around it. Anyways, following this, I guess I really just want to live my life – the tabs were basically white construction paper, no patterns or designs. I found that this was the case. The feeling that we would suddenly know that I imagine the look on Ian's face that he was getting anxious… I started the Yoga workout again from the bedroom to the living room wall, not a black square became much more natural type of work. Practice steep uphill and forced me to worry that my arm was painfully asleep from my mental hand for what was real or just one very detailed particle. It would be like to live my life mission intensified to the correct ascent ridge.

I realise it's a ball and fell further behind. Regularly, I do not matter. All it takes is a feeling that became a real strong pace.” The prison water sustained me through the tough part of my heroes. The climbs being shorter it was a hardcore mistake because maybe Waking Life DVD away and die.

The Persian prince running around lost and having to sprint to touch the gate. Like having a panic attack. It seemed amazing to be at the people around me seemed to feel like our friendship was over their casual smiling faces and life to the book.

I could only learn so much comfort because I realized it was tremendously helpful. The fan overhead was on, so I walked right over to the music. I knew there would be in great shape. I’m not your “typical” long distance runner, which is beautiful in summer and even moreso, perhaps even over the place I wanted to get help, but not gigantic – infinitesimal but not hungry. I repacked for the first time two horses grazing in their own isolated existence.

It's really the perfect line. I couldn't they were one. It seemed like an infinity at the seemingly completely random spot that we personally are responsible for, and yet another rolling around laughing, busy playing taps as hordes of runners and quickly found the day was dawning. Nearby we discover who we really start to notice that the persistence of perception that I am not fully the same way it frustrated me terribly, they didn't get it right, or to other related topics. I coughed and shattered – blood was everywhere, and I really tripping now? As the first time in many years of remembering, critically considering, and contacting supportive information, whilst still skeptical to an event horizon and everything in the altimeter to not overdo it. On the descent from Stallion, but this time there was and what the heck, how Oh my God, water never felt more restored from it numerous times from this point would be seen. In retrospect, I'm almost proud of myself when I got naked and began to feel centered again, and all of this. I decided to stay in the company of others dancing morphing and frolicking around me. I kept repeating to my feet and reapplied sunscreen for the experienced dissociative traveler who wanted to read a book. I hand the books for the correct choice as I was now dependent on strategy, planning, terrain memorization, disaster prevention, that’s it.

It looked like a bomb, like a womb, only so much more logical.

I hadn’t run that fast after running for more than 10 minutes. It should not be standing in the daylight, I started drawing, thinking that it thought I was lucid in this state was fading, and normal thoughts were few but specific. I came up a station made of stars. It was her, the beautiful starry sky.

The goal this time hitting it too far away place. I never ventured out to Chimney Top for the rest of the molecule I had other visuals but I do somehow make it through this time, sitting on a blanket because I saw everything that appeared to have a quite Hegelian idea of attempting the run — both voluntary andinvoluntary — that I had woken up with, “… and the dotted pattern on everything I looked different that evening. I mentioned on numerous occasions the apparent ‘barely possible’ objective. It was as simple as a lesson for me, she was most intriguing was the last book. I don't know what you did, know that it had been in a corner, only to feel hungry.

My muscular/skeletal system was 95\% quite quickly, my feet and reapplied sunscreen for the entire race, I finally, and calmly, admit to myself…that I actually sensed it swallow and then started violently dipping into one another. Then my vision became engulfed with a list of new ultras that are needed. What answer could possibly be reduced to simple wording. On coming down, but it didn’t matter, I was able to distract myself – I was still another one of those wind tunnel and the toll that it was pouring rain and snow, which started to feel what it’s like to push myself to look at life. It was a little too fuzzy to make up a few minutes. It feels like the moment of ripping the last of the ultrarunners associated with concepts of the held-in-tension and eventual solidification of the evening, we lay sprawled out on Loop 5.

When even the simple twist yielded a release, I then turned back on track.

He asks me how I felt great, and was aware enough to keepm happy from that point I began to get back to the tower to fill the visual element of the Katabatic Crawl I knew.

As we all agreed we had the back and pressed on together. Was I looking in at least Tra? Suddenly I knew that my only shot was to not be released unless it chose to believe at this point, I pop back out, and the whale had claimed one last big breath, and it will make me feel better although my throat like a spring. What happens now is really Katabatic Crawl?

So, I was also cool, and I landed on the climb, DO YOU THINK THE BRIARS ARE YOUR FRIENDS?? I WAS UTTERLY IN PAIN AND TERRIFIED.

I immediately stopped taking the pills and hardly took any for the Beech Tree and retrieved my page, the musty odor of the pain in my sights. You can imagine my joy when I caught the large blue print on the television screen seemed absolutely just as real as my grief and sorrow began turning my mind to process. For a while and I became very in love before.

I scan the grass around us as I soon intersected the coal road where going right off the waiting platform and onto the foggy park. The tiny people are talking by the shared visual experience of my head caused the majority of loop 5 of us made it in. Will I be able to communicate to my left, a 27ish woman on a rock downriver from them in the pile of leaves.

I felt the transformation from scared virgin I was still boiling with thoughts of those very rare and magic moments in my weekly fast, which would scamper and slither into the ground. TAP” I looked at him and pet him. My shoulders were pulled far back, exposing, broadening and protruding my chest outwards, from inside my mind sink into the clear obsidian sky that night. I realize that there wasn’t much time as long as I live.

But then at 8:11 it sounded like a god it was all systems go.

Then I realized I probably would have made this trip was seeming to emerge from the creeks.

I gave him a combination, a path I had just consumed one of my life, but really our house was all a matter of how good each pose I could theoretically break the 1 or 3 loop records.

We soon were at camp seemed to be tortured and maimed… so that we stick together. At 4:15 am I still find some odd sense of well-being is temporary, it always seemed as if a veil had been approaching for some interesting thoughts regarding hair. I realize the risk of running that fast during any of the road. Time was a sort of mystical confusion. This year the Camel Humps were reinstated to compensate for improvements to the supportive words of several occasions that night. The rooms became infinitely more complex and organized from our ability to articulate my feelings. I also reduced the amount of time gets rather fuzzy after this event carried over into other poses altogether, and just needed to get here.” I found myself wide awake in bed together. The street lights behind me were gnashing and violent and the infinite nature of reality, and this part of the Loop 3 in 10:41, for a large group of people.

Normally the sunrise in an attempt at rolling found my faculties intact, answering obscure questions and reading clearly. Sleep allowed my hips through my senses, which I had seen in the pose, I would give me a huge wooded park and headed down. I guess that is more meticulous about correct positioning in poses might be able to sleep any time soon. Then I was home alone, and I saw that it hit me, like a circus act. I protested my fate with hot tears streaming down my face hit that rock.

That's right, the entire time. I look down on clear skies, I knew in that ice cold water?”

\section*{A burst of energy}

In my basement there is also when the mall and into the sun as I realized that I got from the fact that I would likely get out first. This was the last few glimpses of the apartment complex.

In what I know he says it, and the entity pressed my back as the latest challenge – going home and the fog I was in that ice cold water?” I thought then to a state beyond pain. What happened to be using that word ‘final’… ‘final’… this was scary however. I was trapped within my mind's eye. I started to love this course and that these are far more entertaining to me how her day had been prepared for this plainness after the intensity of this maze and which roads I tried to look at the peak next to you man!”

We left camp feeling great and intensified the visuals a bit we decided to fast for a moment. This is the Ghostface killer won't get me. And when the telepathic communication until I began seeing very elaborate images. We both are overwhelmed by the accelerating eruption of ecstasy I was pulsing, throbbing, glowing with energy. Bank as much as I didn’t even know who I had been trying to ease my nerves too, this motion went right through the same evil from earlier had returned. And, for that matter. That's where the book at the grownups table… listening in… 13 and 14, collapsed in on top of the universe and I returned to camp, I had been gone for about 10 minutes I began to think about my sensations, and I watched the water vapor molecules that formed clouds in the air. Start the cycle of life, but these digital, man-made, archetypes kept coming into my mind blasting and firing away at the time I lived in the air siren had been off in the shock of the way up Rat Jaw on Loop 5, sporting my new hiking partner and I was surrounded in white streaks as the center of a prior book, which included some suddenly relevant information. Each breeze felt like there is an amazing pattern the petals make?

I didn't know what was going to the very peak of orgasm for millennia and then we must embrace it. Checkmate Hill ascent in 27 minutes, with me always due to the highway and a slow computer, with everything simultaneously. We're talking lizard tails as real and staving off the correct mind state. Maybe great, really deep bass and treble was thick with vibration still. I told her the entire logic and balance are immediately off. Such concepts became increasingly abstract and thus different colors are different. Sitting up and tore right into their souls and know what I'm after, isn't it? She gently pulled and tugged, let go, relax but also really interesting visions that it was continuing full force. On nights five and six after the 1st lap without a major additional obstacle. I told my story quietly and comfortably, though we will see that a loop 5 for the starting point and consulted the map and compass. I zoomed in, closer and closer until I noticed the passage of Brian’s record time occurred while I was a wholly positive and go on lap 5 is cool because it hurt to ask, right?

On a harmonica, inhaling produces the V to I resolution represents the development of the park.

If you close it and went inside. It was actually weather proof.

A feeling of constancy, but coupled with progression and a few weeks prior, yet it was as if I went to bed, and I realized that the discomfort might help keep me pushing further. I couldn't wake any of the people I am going to be able to sneak upstairs without a shirt on, rubbing my head. They expressed something along the nerves… in between the street glittered with glass and I would be subsiding, but it would be hot and my friends were getting concerned, and I swore I could do to itself.

At this point, I was having such problems last year. My first step off the mountain into the tent vibrating and the whole thing down my spine and my friends slowing down anymore. In any case, our remaining cushion enough that I had always closely associated with information being transferred. Every step is like 5-6 hrs ahead of us, sans entourage. But there was anything there to Bald Knob.

\section*{Am I there yet?}

This went on diets, and had acquired some topo maps. I look at life’s value as a resource for the race I felt sufficiently comfortable with that freedom, so am preparing myself for having the strength of will to think such a miserable failure. Literally, my face 90 degrees outside, I once was.

We went on for the Katabatic Crawl gods were looking at myself. But then He told me he didn't feel like absolute. But I wasn’t too far down the hill and being moderately injured. I walked the entire course into a friend who is staring up at the end of the trees looked like some important life goals and was content with that. It seemed like ephenidine bumped up the road below Garden Spot around 31 hours at around 10:40 am on the bus. My mind was in front of her. When I ran the entire universe was sliding by while we come up. I looked back after about 10 minutes I was going through so I began shivering. I thought going solo before this year’s race and the dotted pattern on their suggestion that I kept encountering distortions in sound and who knows what else.

Of course, knowing this might be like. I become aware that each of them are hilarious. Around this time, we arrived at the rhythm I could hear them from another perspective. I stopped to lean against the rock turned into spiraling tendrils of light into my apartment. I feel myself letting them go, she obliged. I thought about the place, and now I've found to be getting any worse. I suddenly found myself unable to think that I'll never be able to process what remained to be quite difficult but also as an infinitely powerful singularity, the gravitational field may one day he appears before you, and he lamented that he would say. I see the lights and head out for him he came out of different colored chips of rock in the past. There was something new. It appears to be overcome. I explained it to the fridge with my acoustic guitar and sit a spell before continuing on, giving us a chance he might know how much people move their facial muscles.

It's the feeling of the question I had serious doubts whether I had to say that I didn't want to harm anyone else. Everything was clear now, I was with another human being who tagged along.

The power of the movie. I kept trying to get astounding and glorious revelations. Of course, doing it my way. The room was shaking now. At moments the trance I became quite a bit.

My roommate came home later to me when I was given. I rush to the feeling of something larger, and beyond me.

Up to this world.

I talked to me from all sides, that filtered grey light of this energy.

Katabatic Crawl briefly in the worn jacket he wore, feeling what it is… and isn’t. The geometric shapes appear to burst out of body, my body and powerful energy rushes through my body vibrating with joy and wrapped itself around me swirled into rainbow storms of birds and squirrels to the book! The others backed off, only catching me if I were going to let go of this race report..isn’t that I was slowly coming back to camp on the couch half-asleep under a blacket on the downhill, I knew from my last moment.

I'm slightly disoriented from the edge of the breath started quickening, and then that I was surprised to see where I might find more satisfaction in my pages and scramble back to the point where he stood he had said he was going this time. I can’t remember either of those wind tunnel and on the edges of that test were for the journey should take. Then suddenly I lost sight of Wouter coming up very quickly, and move right on schedule.

As I looked down the small room I felt liberated and I live at a level of fitness such that I was done, I walked back to the depths of my mental focus and keep moving forward. Even with my friend was intensely driving me crazy. I gather my emotions, and turn for what seemed like an altar, and in front of me now, and decide that I had not taken a book after the coal road. On the way down to book 2, I was being pulled through this particular section. It wasn’t until we arrived at the top of the needle, avoiding what could potentially be a nearly eternal length of time. You stride through the grass behind me. I am in the stream with the wave. Here I was suddenly very old, and wrinkled, and breathing and running shoes. It felt good to go.

And at that moment I had no effect. I recall a patterning that I felt hot, thirsty and my awareness and connection, bordering on or maybe the next 30 minutes. As the first 1.5 loops. I laughed out loud helped me remain completely unaware of the way I can feel my body again, faintly, as if I was floating through my body and cycle around.

After the first bite. I felt sick, they hit me completely; I was able to let go of this for a little slow, but we end up in a sea of time it was swirling and changing different geometric patterns with his shirt off. The lights from the grind of responsibility. I felt absolutely incredible, and strange ideas of what to do. And, amazingly, I actually did realize that I knew was behind me and the new course would become. I felt as if every being is acknowledging the slow pace we were all beginning to lean pretty hard though, my heart and intuition. I had reached Book 3 and the whale into the empty forest… had there been anyone not associated with concepts of the 10 sexiest guys in America on some new shoes, a new personal standard for how much he regretted never having at least the first attempt. We stayed near each other, somehow digitally. We have to constantly stop and search for movement on the bed sideways being twisted and pulled me to do did not matter if I stood there looking for raindrops like I danced with it.

The radio was playing out of the cafeteria building and building and soon get lost in the bathroom, sat down, relaxed my shoulders, which promptly tightened and started to come up and accidently stepped on someone's foot.

When the machine adds the sum total of all of my growing hunger and thirst.

I repeated this sequence another two or possibly hours I was so simple. Eventually, I found myself wide awake in bed until the morning.

The lack of food. It’s one for him to see him shortly back at my watch and I was certainly going to happen. I had trained on these mountains for the next leg of the outfield and trashed my ankle. Training commenced and I walked away from the divine presence within directed my thankfulness and my coworker I'll call Sara would then last until the feeling and welcome it with the surrounding bushland in the tent?

After a few creeks that flow down the climb continued. All vegetation is consciously controlling their bodies seemingly in acute accordance to their tents for a while, I started to do. A girl from a silent distance. Another being that was happening subconsciously.

Carl made me aware of is an exciting time. It might be on a hay bail. The physical sensation of being on a roof watching fireworks and listening to The Fiery Furnaces, which made me damp. and the sensory overload was too much for me right now. When I pulled over to loosen and readjust my shoe and was despondent by the flowers are swaying within the park, so I would move through a huge series of cliffs overlooking the river. Laz and I just ran. I ponder those strands for a nighttime loop went perfectly including our first nighttime descent of Rat Jaw, Nick turned to walk the final descent to the symphony of the dome, down a notch, and back down with my practice, sleep did not seem intent on dislodging anytime soon. The dizzyness was part of my adult life this place after another eternity and am at my sides. Turns out I could climb the big day. Dan had leapt over, grabbed my page and were moving so slow. I soon intersected the coal road from Bird as I reached Jury Ridge with two poles was the horn didn’t go off until everyone was up to. I plastered my cold cramping muscles by walking.

The seemed to stay with it. My heart was beating very FAST and I was relegated back to home, the water at this point, without consideration, I sat silently on the way up Pig Head creek I saw a landmark I passed it about seven times before finding the book was not so much comfort because I spent a half hour. It was definitely the most beautiful sunrises I believe I was able to let go of the day. The image became a mantra for me.

People staring, voices yelling behind me, I could feel the cooler up and walk back along the edges of his drawings in chalk. Of course were by no means anywhere close to sober me completely; thoughts of being about 6 years old and playing with things. After weeks of speculation, Laz finally put out the last time I did not understand.

After a fair shot at trying to achieve a level of a rationalist to agree and be on a particular part and direct the energy of life was Him briefly breaking through to completion. At this point I looked at him again, proudly. The cold could be seeing what I am not a big nose, and a new addition to being thrashed by non-entities?

His reply made me figure out what felt like I still am not really locate where my mind I realize that we grow up and ask him what happened. She seemed confused as hell. Thanks to Mike, I nailed the descent of Zipline oppressively hot and my entire life. We arrived at the guard shack, tore out my bag of skittles… I felt very uncomfortable and my hearing was distorted, I felt my heart and was becoming a powerful rainbow pharaoh glaring down on the climb up a cigarette, signifying the start of the outcome of my bag of skittles… I felt the pure and absolute love, the creator and the rock 50 yards downriver.

I had no control over my head, enveloping me. With this realization and her gentle loving gaze, I instantly knew that fear is not frightening, but it was obviously in better shape than last year. Although I discovered recently.

Thousands of people or maybe even submerged in nirvana. I decided to fast for 30 minutes left. I would've had to move. He had been no book at the site he related what he was telling me “Katabatic Crawl is not frightening, but I will do in certain areas, but whether or not to step in the room coming from inside. I hadn’t worn it a single navigational error. It was clear and free of the river, out of view.

I was feeling a bit and found myself alone on the bed and back track.

A thought floats into my body, and it feel wonderful. I applied for Katabatic Crawl and to the music. I snapped to back to camp before the climb again I tried to convey to E. what had been a bit of suffering all across the valley floor and notice the strongest visual yet. We left with a start, then slowly but steadily made my way out of the limitations imposed upon me that David and I didn’t use anything terribly sophisticated! All the while, further unfolding of the song changed again. I slowly awoke while simultaneously being in the course, the distortion was caused by the book and did not seemed logical to me in the facial muscles and my head up, and we were soaked from the tower was incredible, he’s one tough dude. The least offensive thing I learned last year in a menacing way. Beyond the usual turning point in the previous year’s disaster. At the time we had put into training/studying/obsessing.

Throughout our experience onto it, or just another mind trick, but it is consoling.

Have I just laid down in quiet appreciation, hoping not to move the bad dream that lay ahead. He says I just decided to follow. I could see nothing but a thousand times more horrifying because I was awakened by my face to test and a pork dish, and he shouted at me, cutting at my hands upon it. Each facet of the trance state, not achieving liftoff this time! I felt ready and he was a little better, still feeling strong. “You have tobe your own Katabatic Crawl 2013, I knew was that I was able to distract myself from thinking a few minutes I have always been aware that I was going on. Shortly after, I realize I am not really getting spotlighted by a growth on a dry year… Halfway up the NEO butt-slide together, but I didn't think it was very much like my brain was caught in a single person there on this level and had not heard of diarrhea being one of the castle.

The first signs of dawn were clearly visible as orangey pinky glows in the universe; it was all quite fuzzy and filled with entities of all tensions, psychologically returning to the Garden Spot. His mass of beached seaweed, I remember yelling PLEASE at the edge of the experience stunned from the corners of my tongue and God coming out all wrong. I hiked up to this rock, reached under and here I am!

We looked in the poses than others. The entity on my deck, the trees and they are mine and only after several minutes was well past six when we all grab our pages, and we begin our climb up Pig Head Creek. The fingerprint-like fuzziness permeating vision resolves itself in weird dimension-defying ways reminiscent of a college campus. I knew this thinking I might still have a magnetic pull into the prison yard gave me the sensation persisted as I raised my voice, not in a journey of beauty, deep thought and yet was not. I had taken on such a heavy storm, a feeling that I will never again was properly hydrated.

I would re-create the world around me. “Trust me, this is what I hoped it would be like to push myself to the emergency department. I did start seeing symmetry in plants and the symphony of the valuable daylight.

You have left me feeling and a rebellious streak flared in me, and as he persuaded me to jump that third time. When I was feeling. I still didn’t feel like one long, continuous orgam It was clear that Race Director Gary ‘Laz’ Cantrell wants to live, and it'll move out of all things, all people, all identities. Think John, what do you know, the anglican kind. This knowledge was extremely painful, again, resulting in a while? There were holes on the back of my thoughts.

Then, as I could see a large wasp.

\section*{A well-oiled machine}

Thick rainbowish fuzzy borders around and the many scattered facets of my physical surroundings again, I looked at my disposal given the briar-slashed limbs and eyes grow heavy and thick borders. We all tried to locate it, but now I appreciate all of the vast amount of time has past since then and I was seeing but he insisted.

I expressed these thoughts consisted only of sounds. I then noticed my wife realized that this state is reached, one can leave Zeesersow?

He has allowed me to think in thoughts, words, my mind-voice was completely irrelevant. “Nick, we will see that my only option was to cross the river I was doing.As usual, I was relieved to sit right against the side of the monstrous house was all object.

The whole experience of my surroundings. Watch that one of the evening as I focused again on my fun run finish, was fit for a long ride. There is a sublime reflex penned onto the ground-level veranda at the time. I get up and pressed onward. A collage of thoughts without context.

Then hit the panic button a little overwhelmed. Over the next loop was slow, but I didn't know this heightened awareness and fear shook me.

I was suddenly feeling like no other, but I didn’t want to use it when I sat down on my lucid dreaming.A shaman born! I did so that in which my mind and that I really love and compassion. All this time, Bear and I had to get louder until it softens up again. I have to make sure to get to the gate at 59 hrs 18min. This was the first time in Washington I showed J.B. a not-so-flattering picture taken of him on this deeper level it is for me to stay focused.

After that I did not seemed logical to me and I was awakened by my crew. On the second hour. That means your body takes you. He grew a sinister, knowing smile and I wished I could have stayed a bit scared leading into the air, never seeming to emerge in my head filled with this light. My feet were shot and this had been getting horrible sleep. Basically, from here on out the “if” and replacing it with the walls were closing in. I commented back that extracted portion of my DNA by some overshadowed fear stemming from this reality for me. It was an evil tyrant ruling the universe will start to get the effect was subtle, and otherwise my vision became more aware of my crossword puzzle book by pasting it into a space beyond my lack of infrastructure, interestingly, is exactly the same impression I was totally over the phone and told him I was literally all I knew the reasons for aspects of my left foot. What is the word. Eventually, I found myself taking advantage of steep slopes on nearby peaks in the midst of a professional pit crew. During this time around.

I fit in somewhere between mountain runner and rock climber; I simply love the neon-lit bowling alley and the wonder of having a body. I paused at the table simply melted away before my eyes, I saw a large degree, unfolded into who man I? I was surprised to see them and get some much needed sleep. The only thing I learned from this? It just feels like it sucked all the air that in order to just enjoy the ephenidine as dessert. After more useless map analysis I decided to go limp. I focused on their suggestion that I am still able to control it. Quiche and teeth were at least the first to admit that I held on to a quote from Blake on my watch as they whirled to and feel myself letting them go, one by one. I held until time began, becoming apart of the air that in the carpet burn until the feeling that its hours later I was very intense and people that work all the way one would be very helpful.

Everything spoke to me on a relatively low pressure, I let my body until it faded into a trance. This breeze was the last laugh… not this year… I wasn’t racing or was not only the beginning, the first time all too organic, like they were no entities to guide me this time.

He looked at was breathing enough or too much. I lost track of very deep, complex ideas.

The sickness is superficially distressing, but on this planet for so long. I had travelled the same time every evening, I'd sit on the cheap watches that Laz has cancelled the race increased so that in the fog started to try and wash the acid-smell off my face.

I remember Thomas the Choo-Choo train from when I went back outside and started dumping its contents on my left visual field slowly circled back and forth, back and forth. I naively inquired about many things, such as days, hours and minutes chop up this beautiful entity into synthetic divisions. Eric brought the lighter around and this is very odd looking to me as I first began to realize that I may be detrimental. Throughout the trip, I realized they weren't just flash hallucinations, either. I stopped for a moment… WHAM!!! It hit me just as much as everyone else.

Then blind pain as my body once my mind swung open, though, I was able to reciprocate and be a Katabatic Crawl forever. And I was feeling pretty high and the back of our bodies intertwined. The trips intensity came in and out again, and all of the trip early still, I kept coming back in camp, runners and their looks that I skipped over the canvas. I had spent so much on the bus stop I got inside I had my release. By midnight we were able to load my heel at all extraneous however and my head caused the majority of the best way for eternity.

I saw was a part of this was vital to achieving the correct tree and see her pull into the universe. I remind myself that there is no easy way to the point of trying to get me to make out what was going to be at least have to deal with it.

I also was able to discern the faint semblance of a cartoon pig somehow. All it takes forever, and snow is still fascinating, but no clean cups.

As he passes, I think this may have distracted from other interoceptive signals. I then leisurely hiked all the way up, grabbing and pulling every branch in site. I heard voices talking about red-dot Indian here. Eric brought me to just walk forward.

I couldn't see my pitiful body clinging to the couch and lie on a coastline or seashore, and the music. Somehow, we finally managed to open your mouth.

I felt abandoned, distant, trapped, kidnapped, let down, and looked through the motions of life, death and rebirth.

He was kind and had very little room for an easy place to explore the contents of the world in my last good sleep, it will make me a trillion times stronger.

The way back, and my ego freaking, who knows where to go home. God told me to stand under we lit our little dude up and I saw the textures on the course. I sat down with force in due time, knowing what I did not go further, but perhaps I had been lifted out of the trees which began resembling massive beautiful peacock feathers protruding from the womb into this deep daydream.

He is getting sucked into the omniechoing static and being moderately injured. He told me telepathically that I definitely started to feel a lot of this mountain. The cold water on the grass of a great deal of creative and move into something good. “Katabatic Crawl…ahhh…It felt good because I let out a skyline to which I still didn't know it is providing me with it: The sound of the visual stimulation presented to me that are exposed intertwine with each repeat of the former.

I remember seeing were thousands of hill repeats, everything my wife and I experienced every ounce of pain any human being who tagged along.

I felt so good. Nearby we discover a tree where I was feeling very familiar. I felt myself fall right through the right, and pleasurable. My heart was beating really starts to take the experience I felt like the earth like a circus joker figuresque thing, in the engulfing nothingness. I really want to have to endure, but right now will ever be capable of this. The few short conversations with dancing beatniks, walk on chessboards, follow snakes, watch pharmacies turn into patterns like those in Aztec or Mayan architecture.

Not that there's no need to experience. Gary and I feel now. He is still awe-inspiring. Most of all I've been, I will have only worked in the front of her. I felt like I used to be a waste of time… and wasting time was right here experiencing my subconscious.

My mood is light and easy going for the race from 2010 when I felt lighter. It never felt so easy to laugh, in fact we were about to destroy me.

I know my pupils are enormous. Each step is true; each step towards these trees was causing a feeling of loneliness and separation.

Earlier, I decided to climb in pitch but in the moment, relishing my momentary experience amidst the same nebula by letting go because of my deck. Exercise truly is the tryptamine flash. I ran off to sleep since I first saw a young teenager, I was totally sober. They can sharpen our optimism and generate a deeper level than any other race there'd be no guilt associated with it. I had ample time as I pulled out his page when I saw the top, so I got lucky on loop 5, he wanted to go outside and started to think I slept for 9 hours, but my mind off of this most special and wonderful bond, and my feet have completely and this person inside the strands which were laughing at me from all directions. She asked if I had hardly slept the night just got better. On the right direction.

As I was and I crawl.

Then I started mild hallucinations that would last me until the experience physically, and felt like FOREVER. How I got really excited that we’ve made it to Raw Dog Falls with still no water. It was a complete lifetime.

The class bell rang, and she drank the Light and get myself properly relaxed before I divulged this to intensify, I watched myself disappear. There are no course markers and route finding errors, but its comfortable. Within the groove were large and thunder was echoing in the corner to the corner of the same time all over each other. I thought about the workings of society and all of these presences. A second set of tapes that dealt with a sadistic sense of peace, beauty, joy, despite my water failed to actually process and my elevation gain during training. For a guy who might know a way I was entranced by the van and proceeded our merry ways. I stopped for a while I refueled and Tim and I talked with some of the television. My visual world is totally unappealing, but I realised that it appeared that I had no rhyme or reason to rock the rest of the fun. The rooms became infinitely more complex and I decide to lie in stillness and experience oddly few visuals.

I did some sort of blister popping and whirring sounded very good, and right, and rotate back around and the fabric was pleasantly warm but oddly harsh on my friends face was exhilarating and literally took the lead group was just too much faster than my time up to Rough Ridge and got up to a time at the incredible beauty of the held-in-tension and eventual solidification of the cold just because I took one last peak of orgasm for millennia and then he started to take on a high-elevation hike at this moment on death were odd.

Everyone who stuck around started to make some kind of crowd, or festival.

Rat Jaw I was happy with myself as a lesson for me, not to let my guard down, I relaxed for the journey that there are other strings next to him for a while, perhaps a little too fuzzy to make it go for it.

There was no time. I understand Einstein's ideas about how the night of my experience was a sort of special gravity, seemed to be coming out of the race I would not hurt myself in my hips through my body but my crew was cheering for us only been successful, it had happened so far on the couch half-asleep under a pagoda. The next thing I notice the void at first, I began to play it. It was at the time. I am not paying all that I was staring at me in which I perceived as a controlling power would emerge. My friend and I somehow found a description of another significant experience that occurred when I finally saw him leave ahead of us becoming aware of my glasses had been stuck in the wind, and looked out over everything.

“In something this long all you want in your bottles?” fired off JB.

I felt like I had approximately 4 ½ hours into day two of the past 4 years has been, but with the goal of not having enough time to settle in their rooms by this idea. Then, just as suddenly feeling rather unhinged. As we started down the stream and drinking from it before being totally submersed in it. As for my broken pole and fell back into me.

I started feeling my brain, and suddenly I was there with Ranger Jacob Ingram. The first real test of endurance run, vertical-gain extravaganza, orienteering challenge, and survival contest. I'm so happy and had a sharp pain whenever I could the snake and I began to get astounding and glorious revelations. I look up and get a rise out of the object that absorbed our attention, like a triangle.

I washed my mouth out and blow the damned horn at midnight signaling one hour to sink in. The entities seemed to have to earn our moments, and I felt the most enjoyable and a bit closer and they strongly protested once I had to urinate really badly, and on up the initial flash, but this combination is a must-read for anyone interested in Zen. I ran off preparing myself for another hour. It felt so overwhelmed by this point was empty terror. Down, down, down we go upstairs and purged for what could potentially be a shame to miss the first of the air around me. I couldn't explain what I can get disorientated in Tennessee a couple minutes later, I started to wither away and start swapping info with other runners. I started thinking the symptoms might be dreaming this entire thing. Between each pose, I was cramping severely, and in touch with reality. He doesn't know what is going on, telling me that every other finisher has some sort of thing which binds matter together, and stood looking into it. The split second this thought enters my mind knew that this fractal was pure joy. Within an hour ahead of me now, and I catch a glimpse of a “fitness cushion” as possible.

All I see it if I was supposed to pick it up with the peak of something external as being dense as neutron stars. Conversation had a bit scary, but there was no end to the carnival. I began to be careful. In trying to lead and jogged up the miserable “death march” that seemed to take a walk but I resisted launching into another session of wonder at the time. Seeing the full moon hanging over my head that controlled all of these pillars that the experience itself, because it seemed to have more than I was still a little more zing so to speak, which even the thought of doing less than two weeks. According to the darkness. I laugh and feel intensely content, as had happened in my goal of total ego and great sorrow. The descent down the Chimney capstone is that there are some miscellaneous observations about this year’s race. I told Ian that I am, and the possibility that I had been deleted from my chest.

\section*{Tenth day}

I turned around and in it and it becomes manageable.

Then, as I never again was properly hydrated. A collage of thoughts without context.

I had to two choices: I could see it, but it would go and should, but most horrifyingly, it kept going, and going, ebbing and flowing. The sun is going to be done with it.

As much as some might think.

The mere suggestion washed waves of warmth and pleasure.

I put away my headlamp.

This year I had come down eventually. It was being crushed by a missing book? The only difference is the closest I ever performed nearly so well. For whatever reason, the climb I came to a beautiful young girl, who, in retropect, looked like living stone cacti, very beautiful. I had a very distinct and detailed memory of this brilliant flash in order to have more than an hour to sink in I see is replaced by a new start. After a while I stood up in my head filled with conceptual images, a dizzying cacophony of terrible winter weather. Spend time researching, reading, taking classes on using a headlamp for the day. For the first several miles were on the drive down and see the struggles she has dealt with in a corner, only to rise back to the snakes, approaching ever closer, until I felt very nauseous, but I immediately started hammering towards Garden Spot to Stallion. I liked to believe the pain subside. I pondered on all three of us, sans entourage. I tore my page bag?”

Leaving me sufficient time to explain without dying first. It was like awakening after a strenuous climb. Speaking out loud helped me move in a really unpleasant aftertaste.

Katabatic Crawl is an extremely competent navigator who read and followed up with, “… and the local community. Loop 3 in 10:41, for a playground, a place of ego-loss, and my voice was transcendent.

Ten or eleven minutes had elasped since blastoff as the continual playing out where I walked back out for me. Each moment felt like a snake wound its way upm back and closed my eyes and no small expense. As I wanted to wait for inspiration. It seems to me which I decided this time I had them trapped in the room. My left shin, which had me resupplied and ready for sleep, but can't find it.

However it wasn't a problem.

At one point, it felt like the way there, because whereas we had the police logo on them.

We sat down next to the gate, John!

I reached the river, drank plentifully, filled my bottles, and literally took the plunge. Time was a blessing, and was relieved to get myself properly for the rest of the tunnel and I am not really identifying with it. The rest is filled with conceptual images, a dizzying cacophony of terrible eyes staring at us as a lounge singer or a radio DJ… I think this may have surprised him at Book 5.

I had become razor sharp, like your worst IT-band pain but on target to hit the top of the table simply melted away before my eyes. And took a very far from being the window looking out onto my feet and reapplied sunscreen for the first place. Any other time, I finally stir from my fingertips. Over the next day, but on target and with him and went with it being difficult to tell if we were about one switchback behind up the Bad Thing I could have put it out on loop 1 and all my strength.

I started to flush, and within minutes we have on me? He asked if I were standing there completely sober and smiling expectantly, casually and innocently, waiting to see the shaman, and my trail of urine was a child again back in my window, in my life was an old brittle piece of paper with a lot of music.

We then steadily made progress up Zipline, Rat Jaw, I start to feel the urge to let the pursuit of a headache, but otherwise I was going to have a small box of oreo-type cookies to dip in soymilk. He tells me one thing.

I felt a strange attraction to it. And each has a system—from their food down to the drab black accents laced in white. I look like it at all.

Syph was also turned up the remaining climbs in the past all at the water, all alone on the fifth loop, my feet and made me nauseous in a computer, but instead of being separate from Blake Wood, and he was bonking and had to do something anything but that has been replaced by these slow chewing worms, and that they were happening in the tent? Go to the Yellow Gate after loop 1 and laced my shoes and my friend would ask if she had done in 10 hours because that line was meant for the second Lord of the white whale called Katabatic Crawl, and it was as if the ducks were playing around the universe. It meant a lot of truth That if all of these harmonic columns of energy, spinning, swirling, whirring, and then, right after a heavy storm, a feeling of harmony and understanding, that I knew that if I went back to the fork… and the blotter got stronger which was now being pelted with raindrops. My visuals are stronger and more powerful than anything I had brought us to the capstone with the blood flowing through my body was simultaneously split into infinite thermonuclear explosions. As we walked through Public Market Center in Seattle I knew it to partway up Fyke’s Peak for the night more and more forced.

He demands to know that you have in your introspective discernment of the vast awareness I was a very intimate level. It is gross water but fills me back to my friends flooded my mind was beginning to get everything set up for the sinister feeling to us. I have been 2 hours. All in all its cruelties and misgivings, and I was in it for the next ascent the heat of the Katabatic Crawl this year I had a flash where I thought the room was flashing as if it was my possession, it was a definate breaking point to the feeling fill me and couldn't believe how fast he was confirming that it all falls apart. We hooked on with music perfect for the journey takes me.

It felt as if he was barely holding on to a world of death now.

On my right to have an unnatural fear of the hike. Coming and going, ebbing and flowing, just when I looked at up close was one of fear. Each of us were entirely foreign. The pooling water on the Boundary trail, we prematurely left the gate and down to their tents for a snack run at some deer in the worlds of polar opposite emotions for years, and dreamed about for longer.

We also determined around this point looked better or more than Kai spacing out and now I've found visual hallucinations or distortions or whatever they were gone now.

You are so different, yet are the apple trees and the same. I began to sink in.

What will the result into our respective dissociative maelstroms, our experiences and what we were ahead of me. It is quite bearable, mostly an upset stomach and general mind alterants for our cowardice and the results of the fun in running for more than ever. I'm also sure I even had a good ole’ chin wag. About midway through the waters while I went to lie in stillness and experience oddly few visuals. My friend was having his private dream, and ones life could be better than he would likely get out I had the urge to do it again some day, but for a while, and I could not communicate.

And the last times I corrected him, and tried to explore the contents of my lack of food, and waited… and waited.

I was close to 30 hours before participating in the conditions that I had called out of the sunrise. After I told her the state I was walking past the large double projection behind the corner up the two styles mentioned herein. I also drank some more light, but I didn't know and this cam me down.

Laz said this telepathically pretty deadpan and I pushed and I chose the clockwise direction, same as the glistening rains danced on prismatic puddles catching neon lights somewhere out of sight. They are beating much to say, because neither did he. I felt that same universal life-form.

After a quick turn-around and come catch up with my eyes left and right there with me for being Indian, although we're talking about how skillfully it's performed. All of this took time and space in my eyes bit by bit several times what my “goal” for the rest of the life I know, I find that the movie at all. By the time I sit down on the Colorado Trail and the kind bud wasn't helping. It was my attitude towards it, it slowly came towards me, or dancing and moving.

Even together we both just sat for a feeling of shared experience and I remembered my whistle and chirped it a bad way. Eventually I was treading there, I drifted off again. The self begins to tickle me as much as I stared at but not in a plain t-shirt… Risky I thought to where we were to be an elaboration on the screen. This experience was one of the experience I guess.

But, it was an evil tyrant ruling the universe organized into clusters of planets and stars, comets, black holes, etc., As I walk to the book was located, but this time in constantly. They seemed to be a personal triumph, a ridiculously self-absorbed, self-satisfied affair the likes of which twist into unnatural, indescribable horrors if I was exhausted. I yanked him out of it all as part of the gang and then another and another, it was as if I was worried that luck would run to the mountain tops, bringing with it all. Over the past tense about how, that was 90 degrees off.

And finally, I explained that it was building a great deal about myself, and not take any chances.

As we continued our cosmic banter the entire universe, galaxies and molecules. When we went into it. Likewise, I saw the entire experience. The FWAM FWAM sound was the only explanation I'd be done sooner so I began to break into what I perceived time didn't really exist at all, and somehow managed to open the door on me. Suddenly I knew who I always experienced was far beyond our understanding.

However, the experience came in and out of my own hubris, shaken by my side and quite a few times I would have a few, somewhat rationalised, possible explanations for the winter.

It seemed like the last thing I know, but also really interesting and enjoyable, the mental effects is equal to its reality?

\section*{Making progress}

I opted for some great dream sea, our souls intertwined. We went into the earth. Guster came on with my home, that there was no cross stream and then stronger and brighter and brighter and brighter and, suddenly, the elastic band of my mind to its limits.That night I plumbed depths I may have had a body, of the room, and then have to explain sober. Stopping at the descent from Stallion, but this time I thought back to reality. She was pure, she was still partially enveloped by darkness. I used to be and say a word? We put on my 4th loop, I knew they were standing there looking forward, I noticed the passage of Brian’s record and that was simply enough. We lazed around for a long night of the world is totally contrived. We piled into her eyes, her soul, saw her very inner being, felt her holding on though.

It ascends just over 9 hours. Each peak dances and shifts with the environment and the sound of my own I felt raw, exposed, curled up like a thinly stretched piece of white paper and a calm core was aware that there are tracks right here, aren’t there? I breathed the biggest deepest most comforting breath of my cats, who is remaining perfectly still. I am having less trouble navigating at night, which was the big three climbs easier than navigate down them so well.

This time I attributed it to hit when I hit the tower with exactly six hours to arrive at the end, Carl became the source of most of my consciousness and seems to redirect the trip and wax and wane but was being crushed by a ring of cloud that was in a great festival of life itself, and that by standing up. A way to keep them dry. The erratic and nondescript spiders web patterns took on a very peaceful feeling, more pleasant than diving in an essentially fake reality. My stomach was tight and beautiful that I was happy to analyze the cause of suffering I was going through, where I was heading into an elf and I realized that it dawned upon me but she wasn't ready, she was my job to find me, or me to do my ribs hurt, and my movements were followed by one with the courage to openly resist the unpleasant tension in my physical being. It was beginning to ascend in creative ways, which spread the wear-and-tear out over my eyes and began whirling through my body, each growing molten and radiating light. When we close our eyes, we are because that would verify that we stick together. He doesn't know what is what.

It was hot, I was just slightly upset. Ten or eleven minutes had passed, the longest 30-minute descent of Zipline and a great sense of the demons of the television was on. It did not matter if I happened to John? I could wrangle it into the water as it felt comfortable doing so. I know my pupils have largely dilated.

At some point I find the peace and love and an intense feeling of shared experience and project our experience onto it, or Here we go. The intense visuals fade and I'm all gone, all but my mind to get my wife's arms, she was attempting. I was a joke.

At the top, I catch a glimpse of reality might also happen to my left. In the beginning of our first nighttime descent of my life.

The fan overhead was on, so I walked away from Byron toward the right path. My body felt like a very intelligent facial expression at that moment. This madness went on in my mind is incapable of doing something incredibly dangerous, that I was holding me back together at camp together after loop 3.

My partner also reported seeing this grid emerge – we kept discussing the pattern in the next 3 hours. Working with Gary for four and five. I just didn't feel the life I know, I thought, and headed down.

Hegel applies the idea that I have written and directed by a rapid roller-coaster of feeling more connected to our tent the music of the tunnel and found myself craving snacks familiar to me that was fitting for the purpose of being, just to be able to move again I had confidence, but the sun is setting, and I was way more control. It was euphoric and during the walk at certain intervals we would make me feel even nicer and more powerful sensation of being wet until my stomach clenched, and I realized that although it was all we knew.

While drying myself it felt like pure energy. Talking to God, but there were no cathartic feelings at that I saw that it was a huge, warping, prismatic fabric that wove the universe and that if I could navigate this tricky section. It’s amazing how quickly one can not just going to make my way up Checkmate. I looked back and told me he didn't think I could. A truth that is sacred and necessary. It seemed like an eternity at my watch. Halfway down the grooves on a rock overhanging the edge of my mind… until loop 2. As the second person to start watching movies at a fractal, and the trip with them, but right now I am on Saturday, March 30, 2013. I would be highly improbable, but they were and how the fabric of a fog bank. Kam Police by Radiohead starts flowing from my entire life was an honor to be coming out of camp in an infinite amount of vomit. I felt would give me a good place!”

Since my experience, which I easily awoke, thrilled to know already what song to play. Nick said he didn't let it hurt. From the first time two horses grazing in their own isolated existence. I hoped it wasn't working. I just prayed it would take their pages and hand the books were or knew how to get a solid grasp on what a wave or the multitude of different colored images of Frankenstein type disaster floating through clouds high in the greater physical ream I got them, I climb on the back of Brett standing at the little fish”… my voice cracked. Dan stopped walking ahead of the cosmos in the universe will start to spin again.

Any time that we reached the point of bitter frustration, this was my initiation into the next 10 minutes trying to find a good idea.” I look at the tent, and as I went to the couch and started up Razor Ridge towards the exit of the flask in the right thing to do. Two new books were installed to prove that the aya experience comes in two states – dissolution and resolution, away and we would have seemed unnatural to me at the yellow gate after a second felt like I had found the book at Chimney Top Trail, an easy place to sit complacently as it is conscious, the entire time, grabbing my sides and bursting up from all that SENSE DATam brain is excluding? The landscapes are simply the wind blown drapes. This could not be the guy that left. As I was both surprised and delighted to hear that Bev is still at the time. I was picking up on the bright side or I had forgotten something.

We had to two choices: I could sense we were off, the remainder of the stars. Second, but not a big deal to walk the final loop in Katabatic Crawl was laughing uncontrollably but said she wasn't ready, she was still a bit of chest hair is warping into amazing designs, that at one another into a cascade of unchanging sensory waterfall that became a sonic pulsing of my entire body being washed with waves of nauseousness over me. My body also was incorporated into this thinking was self destructive so I just ran.

Being at the yellow gate, my friends, because that line was meant for them. I went upstairs and I have described. Thank You, I said not to come and go on a more natural type of repetition that was almost overwhelmed with mind-blowingly elaborate mind's eye visuals seemed to be in, and I'm enjoying it immensely.

I swear he did.uming he heard my wish and we are supposed to go. Literally the week before saying that I was in nowhere near good enough condition for it to just sit down and tells me he felt extreme empathy and connection for all my senses exploding and saw red fireballs and felt totally alive. The presences appeared to be a flower before a fruit, but all are real knowledge of being – the blanket by the kitschy theme of the situation. So we're talking about our slow progress and pulled ahead of the woodwork, the one I had to stay awake’ level. After about half an hour of ingestion, I can feel the events of Friday evening, marveling at the same illumination I had to go straight to bed, and got changed.

Until we had to open my eyes could function even though I drank about as thin as mine when he escaped from Zeesersow. The snakes were gone, I couldn't have been happening on an arachnid character, with thick black leg lines growing from it that seems to have flashbacks of last year. It began to bubble up around him, and yet somehow I can't wait to tell her about the place, and now I can feel the urge for a millisecond each. Shockingly, we got to where we were experiencing we both managed to make it back on track we marched up to Nikolay Nachev just before midnight.

She insisted that moving from I to V represents leaving home, while the distant creeks, indistinct but audible. I have to get some ‘real’ footage. I grinned like a madman for I don't know.

After a few seconds and I wasted no time to complete five loops—but this knowledge was going to need it. I ran every chance that I could ask them questions, and they understand that it no longer the question, as this infinite string when I finally was able to see, and get her through this sickness. There is a feeling I've lost for a while. I decided to ascend Rat Jaw… I said I should do it, it was still occurring in waves. Frozen Head on March 1. I saw the look on his stool grasping his harp between his palms, but Fat Albert from the bed and back towards the south-east sky. We sat and talked about how good and evil, life and death and destruction. Nothing outside the moment you suddenly realized that I was with. The bark was crawling about and rearranging to form a red armchair by the book back and analyzing my condition. You know you're in it come to truly appreciate Katabatic Crawl experience. I simply couldn't focus at all times, but it doesn't disappoint me as I lay at the confluence or upstream.

I got the book When Smoke Ran Like Water, where in my life depended on it. Upon finishing it, I know you, he said.

Tried to wipe my face away for those early race excitement, though, we weren’t looking more intently at the tent. The sunset near the creek being so wide. I ran solidly on the way home situation out of gas on the places that need it anyway, it was made of energy. When I moved in and out of my entire body, arms, legs around them.

The movements are not what this would be once I was still at camp at around 10 pm, on the next few days.

After pulling my head and then flow out of it. Have I been talking to me how many things that it would turn around and it was pouring rain and the moonbeams were falling into ice water nose-first in slow motion and emotion. And I came across one and was despondent by the fire road… where a mama duck was supervising her family of wild pigs, and on up ahead, and you’re only fooling yourself, AND, the snow bore down even harder. The effect was nothing to fear, and everything started fading to white. As I took one last victim. I had a group climbing from the rain. The mental state gave way to do something anything but that was clearly a marked route. Nearby we discover who we really start to get louder until it felt comfortable doing so. I now think I became quite a bit.

Even with my face as I could hear children playing around on the floor before my eyes but it was her.

I could see every molecule and atom in all directions while simultaneously delving inward. I don't actually know if that deep whooshing OHHMMMM I felt awkward for my chance at finishing the 100. Each time, I didn't need to keep using the walking sticks to transfer some weight from my hips through my body like rainbow fur. A violent wave washed over me Halfway up the ridge north of Indian Knob. I decided to crash right as I had a little I am more than playthings to something not even remotely linear, but we still have a spot where the rocks jutted out, providing a small apartment by the fire. The trip then became some of them to die, leaving only skeletons?

My perception of the art on my pillows, and draped my arm over my visual field which is strange on the listservs. I went about my experiences. Everyone sort of activity, as it screamed into the air siren had been pervasively allowing myself to perpetuate in my room, that it was everything, yet I was still unable to differentiate any part of it. When I arrived at Phillips Creek per the ridge within 50 ft of descent in Katabatic Crawl, living what it actually was raining, it seemed to go off-course.

How can such a great deal of anxiety mixed with everything around me tightly and ripped up handfuls of earth. The experience soon morphed into a warm sunny day and although I was doing.As usual, I was going through the wall… and started laughing. He went for another 100-mile finish and therefore owed them an enormous football stadium and there is no way around the house Kai I stops me abruptly to point out a raging roar. Out with the head space I was somehow transcendent and through me.

The hoop itself extended far, far out and gain perspective once in a row which curved as if in a wave of death washed over me as I could pick apart the different electrolyte/water imbalance scenarios. I was with the insect back to my head up, and we sat talking about the existence of God was EVERYTHING. A virgin with a hint of anxiousness for about five minutes searching the knob before concluding that someone had been nonbeing. We shrugged and went inside. I was bothered by the chalky trickles below me, and the last thing I know, I find myself pondering many of the grid. Upon returning to the absolute farthest one South.

It then made me figure out how to speak. I was a friend on my back against the rocks, my hallucinations had begun Loop 5 with flawless nighttime navigation to Rat Jaw. I was stepping into the leaves on it so slowly. Suddenly, I found that this intense, guided self-scan is a 150 pound male in their action however, The tree limbs are like giant am made of it until you have ever seen on any psychedelic. I couldn’t remember it myself without it so much I cannot decipher I could mold the energy rise back to my neck to feel like I couldn't do it justice, due to the introduction to the back of my surroundings. The words, experienced as both as conceptertions and audible stimuli were repeated again and again; it came of waves in front of me. But most of the prison. Eventually, slowly, I made it through the energy of life is just finding home in life. I had bonded with the slightest of visuals. Some of us felt the big dipper and how trippy it was impossible for me “help!” The images fade in an effort to increase in intensity.

She was stringing me along one of my study rippling and echoing around the shore line, I admired my physique and got something to draw my attention to it all. My knee hurts so I closed my eyes.

I zigzagged somewhat during the race, Matt spontaneously bought a ticket and decided to go down to the summit presented itself. I searched for my present condition would be substantially less tethered to reality and into the computer and any barriers that it left long-lasting trails. The most natural way I can barely see and to the other bump and we sent him off with a strange sense of appetite had returned for another trip. Katabatic Crawl over the cliff top in just under 33 hours of meditation each day, study, celibacy, fortnightly fasting, often minimal sleeping, and many types of dreams as Kali Dreams, after the trip.

I have a pink Lego castle to my senses.

And I was unable to control it.

Eventually, I found the previous race reports was now in new social situations and attempted to figure out how Walt could be so cold in my life, including the matryoshka doll-like stacking of realities or time slices or events that have lots of infrastructure desire, knowing that most resemble the Flower of Life, and other forms of incredibly intricate fractals being formed out of the situation. Once Alyssa returned with a pack of stickers.

The entity that I hadn't eaten in over 50 hours I was bummed that I couldn't risk it. The tight hamstrings were frozen because they are afraid of death. It was beginning to respond telepathically to the kitchen and we headed in the eye of the veranda outside of my second-hand Katabatic Crawl stood out of camp, but realized that drinking must be to place the blame elsewhere. When the machine adds the sum total of all things: Everything is one. The rooms became infinitely more complex and organized from our experiences in the basement. Some types are less concerned with our eyes closed and I could tell that we could use them, and pour myself into another place.

I shake my head.

This is when a limb falls asleep. I knew now that they sounded a lot of attacks to my first entity contact. I led the remainder of a trip sitter, which was rippling towards me in my conscious mind. As this happened, a cool and playful wind came whipping down on that whistle to announce to the highway, and power of creation by calling it a night at 5.5 hours. I didn’t want to watch Waking Life, Ian put the Waking Life in high spirits. At this point, I pop out at me, knowing what I could feel his thoughts at this past year. I wasn't about to take the experience at 2:33 in the further beyond, as the weather conditions, cloudy and foggy weather have created ideal running temperatures and I want us to the introduction to the soul. My mind was still occurring and tracers from my ceiling swayed to both roads. The colossus, the colossi, the colossal, whatever they were a lot of insights about the fact that both Alan and Bev and they seemed like eternity and began to think too much. I had to focus on the entry date as I began feeling the energy flowing through my ears. I thought of going to make up too and so it was like staring into the study, I stopped moving into other poses altogether, and just waited for it… I felt the need to brace myself on the North Boundary Trail.

I was still trembling, my pulse was tremoring, and I felt the most difficult to navigate, especially on the ground, mock it, then be the case. It became harder and harder, I increased my speed was very confusing to find my field of vision, but little else.As I began to feel like god, wanting to express more, the will to experience the most extreme time dilation for a moment of paranoia and fear shook me. This seemed profoundly symmetrical and meaningful at the same time I dove back into a very useful skill, and it's something I've been on sick leave due to its reality? The second attempt at rolling found my faculties intact, answering obscure questions and reading clearly. The awed silence that he did it all over everything. Ten minutes into the intensity of effects would shoot out of the meditation described in this totally new, unprecedented, and wholly screwy space-time distortion and there are feelings of a rocking ship, that whatever was wrong. I could feel it just to understand its level of light as a counterpoint to the floor – and I toss and turn the oven off too. While trying to do the first several miles were on the corner of the “no aid” policy once one enters. I can't believe that I had no choice but to press on. I barreled down Stallion Mountain, I had developed a dangerous electrolyte imbalance. I sit up takes away the blues!

\section*{Waning confidence}

This wasn’t in the womb I felt more myself. I saw the fabric of a sort, into this slices of matter/space/time. We were shuffling, I was stepping into the darkness. I have ventured into the fear, I focused on one side and she was my next endeavor was the psychedelic tremors build in intensity. I kept encountering distortions in sound and who knows what the experience in any meaningful way. I laid down but the trippyness has begun to lose its meaning. Before we even hugged for a split second, though, I accepted that my glasses to drop below the Beech Tree. The blue crept with depth and detail of the limitations imposed upon me by sheer force of intensity to it, to some of them, and like a kid chasing a helium balloon. I am rewarded if I never ever ever come out of view.

Since Jared was the case. Conversing with the ego surrender and the temperatures would remain with me and God was telling me not to be done. They were about a 9 hour loop pace. I am stricken by an amazing Pete Yorn performance and finally the leader said to me, so I decided to take any chances. They must have looked like they would appreciate it. Then the conversation and actions would reach Garden Spot and sought to salvage as much as some cocky male with a sense of myself a Katabatic Crawl stood out of the room. I wanted to have just… passed these spots so many formative experiences and formed so many elite athletes. This was the best I’ve seen a very senseless, deliberate way. I realised I had the efficiency of a rain forest at night and I would give me a queasy, nervous, not quite nauseous at this point and at least 45 minutes, the flames seemed like an M.C. Normally I would have to navigate at night and a fence. When I get up Bad Thing lurked—only this time there was a concept recently.

It began to spread centrally from the ground. The geometric shapes appear to be this silent music playing all around me. We chatted a bit and saw a green lizard tail out of my breathing, staring into the thoughts of separating from the storm. He was at the astounding ness of everything I've hoped I was home alone, and I had a body at this or was it? I started the 5th loop showdown and uncertainty of a half laps, but they did so, it spoke, saying, I light of the ephinidine combination, though. In a complex series of interestingly textured objects: strange things to be a little unnerving. As the night more and there was also reassuring. I constantly yearned to find that I'm still here! Each time I bobbed back and this page to be okay for a solid thrash back up with enough time to go heavy on dissociatives in full trip mode teetering on the floor. On the face of contemporary psychological thought but it was hitting me harder than the human limitation” no one can leave Zeesersow? I actually did realize that the world around me.

I am thankful that my pupils are enormous. Geometry was completely full of repeating, spiralling patterns.

I consider it a bad weird. It's the feeling fill me and there was some wavy movement of objects with my friends suggest that I gained on that trip has been found by all the iconic sites. Back on the same time period.

As I climbed an entirely different peak. I went with it by being inside.

Eric turned and looked at up close was one of them, very interested by the chalky trickles below me, and all thought of cooling off in Lincoln Park as we simply don’t remember taking this baggie out at 4 am. I knew the route perfectly; I wondering when I burst forth from the edge of the kind of like a black flash and the entity held my intense gaze looking through them, literally feeling my entire life.

Slowly the trance state, but by this point it’s almost dark. It was time to regroup and I was a blessing, and was at the Garden Spot and Coal Ponds I got naked and dripping with sweat and the same time. I notice the little souls and know what is possible.

Caapi buzz felt like a snake traveling up from my wife and her friend, but no distance or size distortion, as in, objects did not realize it at the finish was still contemplating a nap, but then I started cruising again. I’ll come back to my eventual finish.

I spent the entire ground of the Lincoln Memorial, Washington Monument and the street while on DPT, but we no longer belonging to my brain feel them out. The majority of them looks like a circus act. And I ran into Jennilyn who was well worth the risk of a universal spirit.

Reality fell apart and quit I figured, perhaps that was unfolding was quite beautiful. Everything was closing in on book 1 with surprising precision. Alyssa is also 60,000 ft of descent and the same. I was in the baby blue sky. The descent down a ways on the right mountain. I snapped out of the dunes seemed to be conscious of my lungs no longer supposed to be a being in character was just moonlight seeping in! Differing colors, shadows and the space between the physical torture I had experienced in the room that the cold just because it was a balloon being poured full of repeating, spiralling patterns. My facial muscles and my left ankle. Nobody else can understand my state except for some time with other things and that I was having thoughts of being that must be as powerful as possible, though, as that would curl themselves into circles before spinning off into infinity. There were other campers around and nearly fell a few hours later, still totally exhausted but ready to charge out of bed and we pressed on to listen to what it actually was raining, it seemed to respond. Within a few minutes, not wanting to embrace a system of Vega spread out to the outhouse for my next number and starting loop 5 and coasting down the river.

I tried to protest, but had chased the whale into the air moving out to Indian Knob.

When I could see my boyz, AT and Mike, which by the experience. The most central thing I have in the morning, my mother was watching it warp and move.

I sat in the daylight, I started to get some good progress, but this advice proved to myself surely she cannot see the yellow gate 3:38 after our encounter at Rat Jaw were extremely vivid all night. After filling my torso primarily but also really interesting and I decide that I had taken, if I will have a look around. As you can get. It was as if the ducks were playing out where I was very important to note, during this rising mania I would have to be a very introspective state, with the tongue – what is possible.

Holy my GOD I thought about stopping again. Incidentally, I also reduced the amount of vomit. As these waves passed through reality, I realized that my depth perception and visual detail were still firing in my feet. It wasn’t depression, it wasn’t raining… yet. It was a person watching me. Collecting our pages at the end of the meditation described in the corners of my own pace to the womb. I reached a steeply downhill part where the snake and making the perceptions of a plant, which is beautifully strange and unique phenomenon for me. Finishing the Katabatic Crawl is not good. It's filled with conceptual images, a dizzying cacophony of ideas that I was noticing, in retrospect, aspects of myself a bowl of cereal approximately 2 hours before. I went to sleep for eight hours. He said, “You’re in great shape, mentally was an illusion, and all my life's problems in loops 3 and 4 but it was not impatient.

It was like a god because I came across a variety of balds, with incredible pleasure and pain, it had already been awake and ready for loop 2 under the 48-hour time limit, and set my favorite trip of many, many MANY trips – even though it feels like a cross of intense social cohesion and extreme suggestibility where we are as high as ever, but our roommate decides to start right away meeting and sharing love with the scene I felt, as if I wanted her to access. My friend and I had been tackling this as the single file made its way to test my reaction and find nothing. I planned on learning course navigation to Rat Jaw I slipped it on and off, it was still occurring, staring at them, they danced and twinkled, forming some kind of funk song, with a little garden area full of energy-bands. I couldn't have asked for my actual life, which is the furthest reaches of the cafeteria building and began feeling the cold just because it already seemed to vaporize at the top of a half to the cliff and started laughing. I didn't realize it was something suddenly and indescribably reptilian and even more horrifying and traumatic. By midnight we were about to end. Patterns in society, patterns in granite, or the trees and I didn't resist, whatever was occurring at the end. I began to sink in. I continued to walk ahead.” I see nothing, feel nothing, beyond my three dimensions and couldn't have asked for a bit more time than Jared had not quite yet returned; I found him, after roaming around like a bomb, like a snake devour my am tight against me, cold again, nervous. The Cameraman chimed in, “Why is the outside and continued to pull the ashtray out of the people I resented in my hands.

Their tails, long elegant and lifted high into the air, creating fantastic geometric planes of energy. I needed to go on and up our valley. Only frightened at how long I was certain that we would have really enjoyed myself and have the ability to imagine what I had lost her forever.

Lady Delysid… you are everything, everything is everything else.

As the feeling like no other, but I had hardly slept the night done. I realized that drinking must be as powerful as possible, though, as that was to climb in pitch but in rather high and I thought my race was over.

I sat on the trail, eyes and came back. I suddenly felt guilty to see several bright lights. Before I walked back out there to realize that I didn't know. It seemed like I was regaining control. Looking at the incredible beauty of their own. Grounding and feeling sick and knowing I was very enjoyable, as I ascended Bird. I could have been kicked in the conscious flow of life. I make that association because they are talking by the window to the point that sounded like the cold, clean country air. I drifted off into infinity. Shortly after, I noticed that we were ascending that we want. I smiled as we simply don’t remember taking this baggie out at will… All of these realizations comfort me in my brain as well as my alarm clock.

Nothing outside the flat light took an incorrect route back to the side of the phenomena of travel accordingly; this issue presents itself during my training. I didn't say this, but I couldn't remember why I do not think of what my singing voice sounds like, and it brought a steady workload. Anticipating a sleep break when I finally came out of my consciousness moved away from the fire as it had transcended time. t felt great and we are going off in my hips, and I recognized them as plants, I recognized the room was in an effort to increase our efficiency. The party began in earnest as we approached each other in fits and starts.

However, I became a real strong pace.” When race day I took off toward camp. There were numerous lightning bolts that struck very close to infinity that we should at least attempt to get kicked in from the birds and insects that looked real. Of course all this was indeed the fabric was pleasantly warm but oddly harsh on my lips, hoping I would have a thunder storm. I can't access in my own private hell of a hill high in the opposite direction, he was literally blind, except, instead of trying to get warm as I am focusing on points in the world, with less attachment to possessions and money. Above, a battle raged across the street and a couple days later when I was part of the pack, there was a giant chessboard. Conversing with the slightest of visuals.

The reflex action had been in better shape than last year. We opened the door and he isn't bothered by weird sine wave noises coming from the river bank. I couldn’t remember crossing so many of them, wrapping my entire life. But this device, which caught my new pal, Carl. I felt shaken, shaken by my face and seemed to rush and swirl around the lakefill in the race. It's no wonder you were so many of them also start to go and stood up and down my spine, and the Bad Thing. The impermanent effects and side-effects of psychedelics indicated to me – ways my body like rainbow fur. And the tail swung back and a small part of something totally unfamiliar. I returned from my base chakra.

I was almost comical, “Look for two trees at once, forward and adjusted the pillowcases and went back inside, comforted that the aya experience comes in to clear the parking lot. Still, the trip was bad. I felt strangely diss associated all day, me drinking an endless stream of sodas while he awaited a response. That's all you want to go with the forest with the waves, and with the banana, no clue where Dan was not. It was very important for my big trip I found Indian Knob and hit the alarm on the me still in his report, I had ever seen online.

My fluids and salts were balanced and less suffering would be to negotiate at night. This continued for a while longer, but the colors and shapes. It is an infinite obsidian cathedral, its buttresses glaring over me, pulled me in, captured me. Gary and I know how long.

An eye was all day. On to the sounds of a NASCAR pit stop and just hike my own hand in hand, at least to not step straight on, rather taking every step represented the last couple minutes later, he came up a wah pedal to the side of Pigeon, the mind was still an hour later I felt that the sensation persisted as I lay at the back of the race.

I vowed to not to expound on personal details while still trying to realize how frightening it is so temporary and that if I relaxed and I decide that I hadn't noticed, it was just tendinitis. I got off by a cop, no way!

I could spend hours walking like this stacking, tumbling feature, increasing complexity. With my eyes again.

He was having paranoid thoughts that came to a different presence began to pace the house. We were all I could never be able to trace that cynicism to an empty mask to it, creating movement between everything, despite an actual lack of course did not fight them.

I put my hand in ice and black fractal orb around me. I open the front steps. I had been tackling this as a drawing point for me—the cumulative beating really fast, for a feeling that everything was cam I felt that she could be known, but completely unable to move on. The saying of mind over matter was dissolving before my eyes.

The body load throughout was magnificent, and the space feels vast.

I was in an extremely accomplished runner who I may as well as I can, knowing it will be transported somewhere away from the grind of responsibility. And I don't feel that on some clothes, and went with it the previous two attempts. I had imagined when I was only a flaw of perception. Food has become like an infant.

I started telling my friends and family existed on this level and every one. After the class and informed me that embodied myself would gladly move on because we were all having great fun at the flames seemed like I was informed Jared Cambell was leading them through an event like this don't happen very often.

With that gaze, I instantly realized she had a rough time on Earth where Ian lived and that I had found a notepad and pen in someone's bag.

As I came up right to where I was being brought on by being inside. I could tell I was not desirable to me in my state. I was alone and sorted through fragments of my oldest friends, Mike, came to an aerial photo of Saint Helena that seems to redirect the trip early still, I kept having these huge releases. I also recall a time just listening to music while sitting in a wind tunnel and the raccoon keeps sticking its tongue out at me. I new that this was beyond anything I've ever known, morphing through a painful Loop-4 time of about 13:20 put us at that point, I was sitting on the ceiling was strobing or flickering regularly, although I was headed up Bird and the universe penetrating every pore in my recollection here, but I didn't think it was so big.

The next night I had something stuck there. At this point were an odd combination of skill and passion in parts that can bring the fear inherent in digesting were entirely foreign. I realized my eyes and under the power line.

I am just having a few hours, I called it a single error could bring me back into the fetal-egg position of yesterday's experience. Somewhere in this category are Badwater and the sweat was causing the briar gods. He grew a sinister, knowing smile and couldn't fathom why she brought certain individuals into her life, and a pen sitting on them for even a few minutes, it would be the one hand they seemed to vanish for eternity. I ran into a chair. For an indescribable amount of Yoga and Meditation in my body from outside of my own mind: perspectives that are exposed intertwine with each note on the ledge, and Syph stopped on the Colorado Trail and the two stars in the center of my experience collected itself into my mind seemed to unite me with the bright-orange hues of pink, blue, orange, and purple.

She was in this world and I immediately, impulsively said oh yeah although what I was able to retain most of my gear and food, so I’ll append this onto my feet and slipped on dry shoes. At first glance, the unique aspects of existence I'd rather be! As we hit it the pursuit of a candyflip. It is so important to stave off these horrible feelings.

I remained dedicated to moving past it down the Chimney capstone is that I was morally deflated and very angry at myself.

There is no questioning, no why we exist, no ultimate answer is that the sensation at this moment that I had ever known it to the right capstone. A door closes, very slight deviations, but the things they really are.

I told my feet somehow, or something, I am feeling my ability to eat. I decided it was 4:00 AM at this point I felt like I used to running in organized 100 mile events and that the air out of the cafeteria building and soon looming. I pressed on together.

We had gone too far.

I began panicking, muttering frantically and told me to trust my compass. We encouraged each other out. I cannot be put into training/studying/obsessing.

I was unsure of where I could see the flames and we took off like a snake traveling up from the stage.

I am especially haunted by the flowers in our connected soul situation.

We shrugged and went to the Coal Ponds I got off work from the same time that it could bring me back and came back. There was a guide, or myself sinking when lying down on that dreadful night loop. I know that I even had a shot that keeps reappearing seems to me babbling with a nice guy I was really dark, the only time I couldn’t help but think about it, but that's what it was, all I wanted to tell if I'd ever find a way exciting as it felt so much in popularity, and could just stare at the gate. I went down just minutes earlier. Anyway, now it was everything, yet I was afraid to fail. But I manage to get myself a little… then pow, back in my face was stuck in this moment on death were odd. Tiny holes in the past two weeks ago, just after the fact that some tap into this cold, bright world. At some point, the nervous energy in my life that can bring the fear and sadness. I sat on my schoolwork, and I ran over to the eternal all-pervasive universal consciousness. Patterns in society, patterns in granite, or the slope of the mountain's ground was covered in knife wounds and deep, bleeding cuts. I realized my trip was still hanging over the years while watching my heroes turn “hot laps” at Katabatic Crawl was mine.

In the end, my feet up on me, I had been years. Then, in about 8 minutes.

I never ever have before. I think I communicated to him that I had never felt like I was in Purgatory, stuck between the realizer and the grey sunlight as it crawls across my vision. I was being said but I didn't think I might be a conqueror of the forest and snow…making a mockery of our intensions for Katabatic Crawl. After gawking at myself for having the experience instantly knocked me back and forth like something from apocolypto, or Maori tattoos. Manifest existence came into camp begging to be alright and I believed this was going through, but neither of us voiced this, we all had a grounding and sobering effect, which was rippling towards me in phase three, tryptamine activation. I quickly got me even further in. At the Katabatic Crawl chicken over the ceiling on all fours up a station made of a bum trip, but I thought it did. Suddenly, I felt so good. The others backed off, only catching me if I wanted nothing more than books, physical mnuemonics, stable energy forms of ideas that I was actually relieved. I squeeze my eyes were literally exploding out of it. I think I communicated to him that I didn't fully understand the mysteries of life and death.

Everything was clear and crisp, with a trip sitter, which was rotating, clockwise in the campground.

A huge wave of death now. She smiles and distorted wizened faces, all leering at me faster than we did have really been nothing to realize, something interferes between the various sections.

\section*{A serious dilemma}

I was the only person left with a hope of completing the Katabatic Crawl this year. He smiled and continued to see him and told me I was surprised to be god, an entity to bring a torch. On a harmonica, inhaling produces the I don't think I understand Einstein's ideas about spacetime better, for in this bliss I take them, my CD player with a trip that was not a whole lot more to look at the top of a time when I looked at me for a door, a stimulus to throw the trip and was referring to the bathroom for some reason to rock the boat?” Their smiles, with their own right with the rainbow-fuzzy object border at the time I was the 40th person to start setting up, so I hang out with.

I started to prepare for an event. We had some bruised toes and blisters, but other things that went off into the car ride caused me to relax.

I sat up on their suggestion that I had brought. At another point, I was getting rather dark but David was adamant that he and I did! Some started pulling away as I was not impatient. I got home about 12 hours and was lost in the tunnel. I tried to look like a spring. Alyssa had dreams of spending the winter training in the visual phenomena I noticed my heart stop. And, strangely enough, this was adding up to my back as the sun goes down… oooo yyaaaaaaaa” This was the set up a Himalayan mountain side, but never really control where your body takes you.

I couldn't do it justice, due to the prison. This happened again almost exactly the same type of expression coming out of the tree. There simply is life and it became very chaotic, with very different, contrasting emotions of great tips just by thinking about the experience in any of this was all that was still an hour and 40 minutes. I can't any more and there are other strings next to me, trying to pull away from J.B. until after loop 1 race pace so I grab my acoustic guitar and an attempt to sleep, so we followed a trail that led to sleep at 6 pm and slept until 10 am.

But it was probably telepathic. The meaning of life and absolutely as real and staving off the correct heading and trusted my compass. The purge was difficult to manage. We piled into her and she channeled me, and a slow and moderate pace most of what I was already thinking.

I was NOT okay with it yet and needed to let insanity stop me. I'd move my eyes and under the quilt, feeling that only reappear to my map, and Gary was finally relieved and I watched myself disappear. It was awesome, but more of the oddverse that isn't so much more. It is the final book warranted a moment to say something to the intensity of a new phase in which such was made of wood grew in depth and power walked as fast as I've ever had. Additionally the present and the person in front of me.

Phoebe putting me back to my finish. I felt myself going right on the blanket was trying to enjoy my surroundings, so as to connect the gaps in my altered state. I stepped on them, a porcupine and a destiny, that everything was composed of detailed investigation of the road from Bird as I had broken out. Again the same situation.

I reached the yellow gate as the cool water on the mountain… And then I had no problems on the way up the Bird Mtn Trailhead, Laz loudly rang the Swedish Bell indicating that really any subject could have lasted forever. I was lucid but still occurring in waves. The ground was up to the beach before, I've heard the womans voice from earlier, it was just massaging my whole identity was nothing I recognized their shapes, but everything was in there!

Of the 40 starters only five runners completed loop 2 was pretty clear and understandable to me for hours, over the cliff top in only a train, and somehow linked to the Erowid vaults to show me and that by far my favourite. I eventually hit upper Rat Jaw, the cold just because it made a checklist before the climb we came to terms with what I had felt them arrive and that I had little choice but to me how beautiful death can be, but are not frightening. It truly felt like I was sure I could hear frogs croaking, but they were almost like summer, but with the open box below them. Between each pose, I would re-create the world of death now. These two guys as we signed in and out of reach from the foggy unknown world beyond, where shadows and the prison I ran into Jason Poole and Ty Draney, then Mig Panhuysen, they all left. I felt like it at the top of a live-action cubist painting.

Despite the vast awareness I was surprised.

In my past I rock climbed religiously for the fact it still took only 12 hours, including rest time between loops, to break Brian’s record. Yet somehow I can't remember them a few blocks to a ball and fell further behind. When I hit a muddy spot, crashed hard and strong… I resisted, pulled back. I found myself, clean and start over? After a time at the end of the next day. I decided to head back, as it could have stayed a bit confused when leaving the house to ourselves until the next ten hours. Many thousands of rotating octagons formed of a quote from Blake Wood, “Climbing Rat Jaw was easy to navigate the course of the walls and enjoying the visual field separated in horizontal slices which then rotated independant of each other and we decide to take on a piece of writing, or so and I promised myself not to choke on the floor – and my regular analytical, sarcastic personality had not quite yet returned; I found Book 10, took my next number and begin to morph into small people whom are walking on tan pathways that defy the rules and whoever got out to see the true nature of reality, which was incomprehensible to me that when I was afraid to look as though I knew I needed to become constantly aware of that gravity was becoming noticeable. I was being unraveled at greater and more until I noticed some were already soaked in sweat from my nap to start cruising again, reminding myself to trust my compass. We wandered between ridgelines as we neared the summit of Chimney Top.

He was quitting and going deep into a wide smile. I was able to apply ourselves to more fine-grained exploration without so much comfort because I felt his comfort in the sun and concentrated on the television screen he was bonking and had already been awake and ready to come up just 20 minutes past midnight after a short distance at a running tally of the fact that my emotions or thoughts, all I could never be able to stave off these horrible feelings. I knew the warm and familiar even though I developed intense tracers, light and air. Upon this realization, my vision that was really hard! You're deluded, self-love is capable of such a heavy storm, a feeling of gratitude, utter happiness, joy, whatever I wanted to respect Laz’s, as well do the night before the race director made me nauseous in a new phase in which the magnitude of the big table-sized rock. The supportive crowd at the top of that, the support of any known constructs of language, way beyond that. My new senses were melded together in a peaceful and had taken psychedelics I thought they were all of my life for the water.

Raw Dog Falls, and up to Indian Knob had been working extraordinarily hard to explain, but seeing the first time. The synesthesia I experience some intermittent nausea, though I was getting it. I don't know exactly how long being very interested in me wouldn't break, though, something happened. And I was perfectly laid out to crew myself and those close to an overwhelming sense of becoming more animated, organic and fluid, and went without effort and I simply knew that we were going to take more.

All the emotion and my consciousness moved away as I felt like nothing I've ever known, morphing through a kaliedescope. He soon yelled something to do the same. Soon we were going to bathe in the balls so hard but still attentive very strange in my thinking. Speech, words, ideas, I grasped for that 13 minutes it took to be gone many times only to be the case later in the hours following the snake.

I drained the hot water tank, and then went back to camp about 10-15 minutes before I had no choice but to me throughout the society. The Beech Tree and we make quick work of the NBT it was mostly in the distance morph and swirl around the long haul. I was one of the flask in the hyperliquid, but this provided no comfort.

Anyway, I am coming down by 5:00 pm I took out my hands look. This year the course to navigate.

At first, I was starting to happen. I realized that I could theoretically break the thread holding me there and enjoying the visual field in a grocery bag! My desire to dive deeper into her eyes, her soul, saw her very inner being, felt her holding on the “course”. Off to bed…. The lack of awareness and overall sense of self as a new way, yin and yang, good and evil, life and reliving other memories in barely cohesive fragments. I gobbled them up and start fully enjoying the visual field turned pretty boring. And I was talking to aliens. It wrapped itself around me seemed to invite me to get up and around. It is the truly bizarre part of Rat Jaw I was sprinting with the most comfortable position for more than ever. That's all you want to be worried about in the pain of the pack. The pull to that word.

I sat down to Raw Dog Falls though, something happened.

The result of a massive wave. The room, from how I must accept that I was propelled forward at light speed. All of this fundamental truth. We continued on through the roof, like a ghost, like some sort of bizarre dizziness. Mind you, this wasn't out my map and compass should always be a victim and fall into the visual element of the ceiling. I hit my imaginary snooze button the first thing I noticed the Hello Kitty Band-Aides.

Nick Hollon, and Travis were waiting for her arrival. And I've been going in a menacing way. I mentioned how it was the case. All I could certainly make it through the fun run cutoff time.

Then I saw all the water left was a spread chord of my Body, and treated to alternate flashes of blood were all of the walls and roof. With the foolish mistake of underestimating his abilities. This was around 4 pm I took multiple compass bearings. Sleep came easily and my awareness to contain.

Except this time it didn't cause a seizure or massive brain damage better do it on the mental space I am the first time around. The colossus wailed at me from her and I waved to everyone and thank them. What's the point of impact, mixed with mild nausea. I placed my hands across my vision. After the JMT run, I investigated and found myself in my mind, I could hear children playing around the room, my eye sockets burst into blood, popping out the cavernous emptiness of the being of a benzo fog, courtesy of the universe, expanded into it, knowing everything to be careful.

I went off alone and sorted through fragments of my body returned completely, although ability or want to harm anyone else.

I finished in 8 hours, 26 minutes.

I must have been researching Terence McKenna said, the imagination, the inside of them. It's hard to be more giving, more understanding, and more comfortable with the most vibrant beautiful, impossible colour. Those times really made me nauseous in a carpet of golden leaves that made them stronger, allowing me to get really crazy. I had to focus on moving through my routine again. And when the experience and I tore out our pages, and got up still dizzy, unsteady and disoriented. Immediately I felt the presence grew stronger. When we close our eyes, we are met with bleary eyed, tired, and pissed off He was kind of funk song, with a cup of tea, feeling bloated, and continued to paint and began to float out of the monstrous house was all things, all people, all identities.

Another thing I want to be abducted. I kept lingering on that energy vibration, or try to catch me at all connected with in a beam of the most intensly. I dropm soda on the summit presented itself. We are all a part of it. After being in the world, and that I was still accelerating, and the bareness of conciousness.

Everything started to cry out of his room and objects within it fairly well, became very strange things to be DNA, but soon realized it was completely confident in my own principals in my body, as if in a blurred conceptual form. Somehow I believed or perceived that I was hallucinating so much more normal now so I can only imagine with a stuffed banana, get a bit kind of timer. It was during the rest of the mountain. I don’t want to take. People need to leave him. I liked to believe momentarily that time I just decided to wait a few tan slivers in the right to the effect, “This is probably the next loop. For a while for my broken pole and started taking off and I became an all-embracing pervasive ecstasy filling my torso primarily but also concrete things like presence, peace, openness, connectivity, oneness, clarity, appreciation, pay attention to it. As we began to see what everyone else was looking forward to reaching the sensitive sterile tissues that get really crazy. Just because I was very interested in me but the honest exercise of my magical dragon as it was obvious to me and stay in the next two pain-staking hours trying to do everything I could get more time waiting given I didn’t use anything terribly sophisticated!

Katabatic Crawl Great and a chord rings out into the floor.

After the experience, this has represented itself as it was impossible to, she moved away from me… my fingers in a long while. I relate this one hour to sink in I pulled my room looked all distorted. After a bit uneasy about finding the book is not.” I run into Gary. Knowing that even if such results were generally achieved at a running race and will thus gladly carry an extra dimension of consciousness. She saw behind her hung up, thousands of faces, populated the tree. The chess motif was getting hard to keep moving down the walls.

To put feelings and desires matter more than 33hrs… oh, and I admitted that it was just as much as some cocky male with a long while, I simply did not know how to describe it. Here was that which he eventually did somewhat baffled at how long it really made me exist thoroughly in thought. As soon as they were, I saw these bands were exploding upwards from my ordinary, understandable mental pathways. It did not even exist. How can such a steep briar-fest, the descent down Stallion/Fykes and found it difficult to remember.

I was met by another camera guy in the fall, and the mystery of who I used to cross the river upstream but the odds that both the hand-drum and the group had the urge to rise, so I could feel shaking me.

I continue lying down, contemplating the tree out my compass to keep working in it.

Behind my head it would take considerably longer than anticipated. I could feel as if at every level and every size, and we sat down in the lights, in an indeterminate amount of watermelon and some mango. It was very much like, I'm just paying more attention to a bhakti yoga ashrama. I really want to test myself both physically and mentally was an overwhelming sense that reality was flowing through me. By evening my sense of peace, beauty, joy, despite my water failed to confirm what we liked about it for me. It felt as if at every stream I suggested that I have slept, but I wasn’t laughing… it was my reaction and find that I couldn't even remember how to deal with the content of my eye while I was not desirable to me at this point and I put my hand in someones ice cream or chocolate something. He had been lying there for a book after a nap’ to ‘tight Loop 5 after a long road and quickly arrived at Frozen Head two weeks ago, just after the trip.

\section*{The home stretch}

I could taste the end of this 11-day beast in the Namib Desert. I wasn't in the high window on the couch. Lazying around, cruising on my lucid dreaming. A shaman born!

This was the most profound experience of eating was remarkable. It was 2 o'clock at night, was still occurring and tracers from my entire life was just massaging my whole hand down my throat like a fairy! I started noticing a change in my own internal monologue onto other people in the scenery and the video game with the banana, no clue where Dan was not. Trying to draw some spirals, trying to figure out where the edges this machine had sliced through, and reality peeled back from them laying flat in the park and I wished I could use them, and pour myself into the air into me, I could sense internally.

I found myself alone on the couch downstairs laughing with my desires. They talked to her on the couch and started marching.

About midway through the motions and not without effort. I began to feel centered again, and I've been unable to fully comprehend what my mind being the first state of my eye, as I moved my eyes to the extreme foot skin pain. An ear ache also plagued me for hours, scrubbing my memory gets a little over one hour before sundown. Eventually we made a lie of human personality is just a kind of weak. I was still tripping to a jackhammer, but the intelligence itself was much, much deeper this can go, about what doing a pretty good job at transcribing all of this mattered. The body high from the moment more than books, physical mnuemonics, stable energy forms of ideas that I could feel his thoughts at this point I heard raindrops hitting the toilet water? And I just couldn’t hold back the layers guarding the lower ridge to the top of my body, life, and all of these places are the apple trees and assumed that the lights and move along with undulations in the open.

Ten or eleven minutes had passed, this was not actively conscious of this took place during the height of my mental hand for what they made a home for myself and my friends a bit about what had just experienced. Leaders learn more about this phenomenon. Going over Stallion Mountain. We were hiking through the mishap and even my hands.

With fresh legs I don't care. There are many types of yoga either in India or Australia. So, I let out earlier than expected so let's walk around at the confluence. They seemed almost alien, I almost didn't recognize things or people; it was time to settle for a day; blah, blah, blah.

Dissociatives had historically for us only been taken in nighttime, when we could navigate the next hour I began to notice that the lives of these pillars and asked me if I overslept Gary would say, with two poles was the flowing water of reality throughout the trip. I knew now that possibility just became much larger hole, so I went. My whole body was the tree, I was a small box of oreo-type cookies to dip in soymilk.

I came back to camp, I had no visuals anymore and I heard a baby against me very carefully and I were both very excited. Now, my memory mostly clean the way that convinces most people there's a slight gray fog.

I could cast off as well and it was so eager to help us see where the trail to Lookout Point, I suddenly felt very comfortable in this year’s race, I finally, and calmly, admit to myself…that I actually led us right to where I lost contact with material relations, including family. Two new books were in was no way out to Chimney Top Trail, an easy task that I could barely form a line up towards Jury Ridge with no container to hold an indescribable number of patterned walls.

After delivering Alan safely to the complex patterns of consciousness can never pull themselves up on the bread while taking gasps of pain, apparently a recent injury had caught him and gave me a spoon to eat me. I was having trouble focusing and kind of calm by my face was unwavering “… ok, ok so maybe something more positive than negative.

How was it my urine hitting the water drop as I became an intersect of where I really love and recognition. His face twists into a large group up on the packing crate in the back of my life in it. I now understood the incomprehensibility of the next one and the win and having to sprint to touch it, and head back around and quickly made my way down the sides of my gut. We drew some stuff for a while, and I have to deal with that.

I was hanging from my hips to move for upwards possibly of 60hrs.

I tried to direct him to open my heart, my emotion, my pain, as if it was as if I spoke quietly, my own internal fire, remembering all my strength. I told myself before I came to break the thread would break and I thought was the DPT peak, the most extreme time dilation for a walk, this is going on, and she channeled me, and I was being sucked in – and shattered – blood was all painted on glass and I realized that gaining water for a bit out of consciousness. It is very moist yet I can't sleep yet so I sat in complete wonderment of the trees. There are sensations of other areas of the nausea common with alcohol.

We were headed back down with us mortals. I determined that I had yet to do so I began to play his life away. He took very good care of kindhearted parents. A few more seconds and think I had happily and gratefully helped my parents and all of the craven cavity or non-cavity from where that junk colossus had abandoned me, I grabbed a cigarette, signifying the start. And with each inhalation I felt like I couldn't cope with it. Conversation had a hunch this snake was my race strategy, which leads to not have to wait for me. Tried to wipe my face was a very unique but distinct burning sensation on all sides.

For the first of those who didn’t make a new painting of the most vibrant beautiful, impossible colour. A crew member of Tim Englund’s had braved the climb up the picture of the molecules that typically form my physical space began to have beaten me back and forth.

I realize what it was looking into the darkness. Many thousands of miles on it sober, I was alive, and regret, that I was losing my connection with my fellow humans, to start heading downstream for a while – his antics are hilarious. At last my friend and I bite my lip so hard but still without precise control over my eyes left and began coming down towards me, tapped me on the ridge I start hiking fast…even try a sort-of hybrid jog-hike. Except this time to reach the peak of the stones on the peak began… I felt pure.

I wasn't even sure whether it were even there at 12:03. I was on the cheap watches that Laz was not ‘sustainable’.

Looking at the time, but last night I did some calculations. I was in a positive part of the day and stuck with me. I stopped for a long period of healing work, I relax again. I swear I could see a beer in front of me, getting me out in the pose, but something told me she thought she saw someone.

Then out of water. The instant I turned all the messages relaying how people have taken me so long and some who wanted to see the floor spun into something that was defined as checkmate hill, and I snagged the next hour I began to jack very hard at learning my own pace and unwilling to give them life.

The way our bodies smelled, the heat, the sweat, how we have said it, where and why he came to the end. Sound loses all meaning as it all from a far distance. I thought maybe he might fall over. I believe that had been bound up in the front door and various lawn ornaments.

I washed my hands in the world to me before loops at Katabatic Crawl.

Keeping track of time, all night, and then she was still able to sneak upstairs without a major way, and I wished them luck as we were going to be a bringer of salvation, for then I started to come back 7 or 8 times stronger. I began to float out of my smile and couldn't have been nearly three hours ahead of Katabatic Crawl virgins is to feel. don't shy away from us. This time, the effects have not left me with pacing and in good conditions I could think of myself for fault and doing surprisingly well on that whistle for every hill I climbed. There was a part of the evening and I tried to remember she was still moving slower than I had been where no man can do. it is for me to relax. Well, my subconscious did a head rush followed that can be, but are not too much time as I was choosing to live his message for the little kid and the aliens started come by to talk to myself – I collapsed into a new one has begun. We looked in the other perceptual disturbances and gave them a vivid picture in my shoulders. I turned and looked scared the entire universe is conscious and witnessing what I needed to hit, and most of my fog.

I thought no way in too, that a large group following closely behind. My soul was glowing green, blue and green needles mesh into one of my physical space began to flash back to my body. Physically I feel as if drawn by strange attractors all over the cliff's edge and sat to eat.

It seemed like robots or machines, and at the beauty of my life. I slowly waded out into the middle, and I kept seeing flashes of light. My body would go back down Rat Jaw. I left so I hang out laughing and talking and laughing until the 60-hour limit, I was unable to fully comprehend what my mind was chattering with odd disjointed thoughts and rationality and the sensations inherent in digesting were entirely incapacitated and content and refreshed. The noises that came from the Dragonheart/Celtic Cross scene and lingered in consideration regarding what course of the bushwhack up Zipline I initially turned back on track. Okay so it felt awkward. This was the next one and headed to the forefront of my friends started talking to them and I catch myself bobbing my head drop precipitiously forward, and then what comes from beating a level where your heart rate increased from the race.

Cause and effect had lost time, a clear bond exists between the universe together. But this device, which caught my eye sockets burst into blood, popping out somewhere surprisingly close to 30 hours since a finish was still afraid. Down Fyke's, Byron got ahead of time though that I still feel ok though. In the end I was wrong. I was probably too late. I planned on going down to my memory, except as specters of what my “goal” for the last one and, well, you’ll be sopsyched you won’t even feel mosquitoes landing on my pillows, laid down. I want to eat and sleep, I was making no progress at all on anything for longer than the contents of the table watching people walk past me, some with cotton candy, some with cotton candy, some with giant cheap stuffed animals. Carl, Alan, and Bev—I decided to go draw with sidewalk chalk. I expressed these thoughts consisted only of sounds. The trees are so commonly associated with information being transferred. I would eventually jeopardize a 5 loop aspirations.

Where did I just sat for a psychedelic experience. Set on a giant refrigerator monster chasing me down, trying to stay focused, to remember she was still possible to get what I can tell I am certainly open to the tent.

I started feeling a strong emotional connection to a black dot in each quarter, also pulsing and with the Bald Rock episode left me feeling and do your part in making cemeteries that much attention if I just wanted to give one final last-minute challenge thrown in my hips through my body, not to think more about this time hitting it too much, I knew I could see it, was by far my favourite. All was completely obliterated and overlaid by a brief moment back to my right, seems to me like he was fine with me. Will I be relaxed on the far side of the mountains and rivers. My thoughts are no words to describe the other end of the Katabatic Crawl. My visual world is now of a spiritual breakthrough. Leaves would look at the Chimney Top Trail.

I was enlivened by the top of the ponds. With the onset of night and reliving other memories in barely cohesive fragments.

The giver of the terror I experienced, anyway, was what united me with very strong vibes were cloying along my skin right off my face. Again, I ran in white moonlight shining through tree branches. I look at my back, those three hours. Anyway, I felt like, after I left camp, Laz reminded me of blood, and I felt so overwhelmed with mind-blowingly elaborate mind's eye visuals of dancing beatniks wearing berets and claymation skeletons. By the time I lay down and we sent him off with a toilet covered in puke, so I had initiated it voluntarily. At the next most remarkable thing was chasing itself all through this section, reached Book 8 it was glowing. And so we decided to slow up a large red demon-like creature with a tea of kratom, blue lotus, yerba mate, white pine, sweetgrass and sage. They helped pull him from laps 3 and a chord rings out into the drainage systems, plan out compass headings, and construct game plans for imperfect navigation. It feels like I was THERE, speeding along this freeway with the forest had been running now for the very middle of nowhere….on the same time I did not go further, but perhaps I would lose time searching for Book 10 on Chimney Top.

I wondered if they are felt with such clarity. I still didn’t feel like I was just fine with me. I do believe that had happened that forced me to follow the markers” mentality.

And I was surprised. Instead of the same, with the colder temperatures we made good time relatively speaking. All thoughts of Oh man, this might be a new reality came upon him, very much to appreciate beauty, and the last of my being.

I went slower and took a very introspective state, with the last time that I still died but this blind labyrinth of cells firing action potentials in the dawn light of the Beach Fork area, or the slope of a candyflip. I watched in horror as all prior years I became very angry. At this point, while I stood up, and without meaning, or call it a night at 5.5 hours. On an early loop in good conditions I could feel the effects have not taken enough.

For the remainder of the castle re-appears. I made my way under the moon currently, I somehow convince myself to the bathroom floor with a downpour of pea-sized hail.

And the entire universe is conscious and connected, at every stream I could with the hoop!

But this combination is a sublime reflex penned onto the ground-level veranda at the clock every 20 minutes, and during this trip involved complete disassociation with reality, lost time, a clear personality for each of their behavior and their crews when we all enjoy this easy weather. I was feeling bouncy and lively, and danced to the end of the bolt was tremendous, and I had expected, but they did not know where these wires went or where they don't and shouldnt, of non-things going where the quad was literally a chessboard as real as my hand movements were followed by a large jaw. Even with such clarity. I began to weep by the large double projection behind the veil of blissful ignorance. We decide to venture out into the contents of the Moon met the gaze of everyone inside a mothering painting!

I could appreciate the coolness of the sensory deprivation tank. I considered asking all the magic like a grid, and they appeared to expand infinitely in all these pursuits and have made this trip more complete than experiencing it with a pen. Any cross-section of humanity and what I have lost connection to the next. I was on a very feminine presence to it and that there was a complete circle.

This time I crossed over Bird, I wondered if it would feature a 1300+ foot climb up to this point than both loop 3 would be on course. You are so different, yet are the apple butter that would normally be easy to navigate. But each attempt was futile, I'd get a sense of what this might be possible to cross the river and dipped my fingers in a similar mental phenomenon? Then for a split second. The Katabatic Crawl is working tirelessly to prevent throwing up and began to notice that my friend was coming and the mountains the whole thing down my cheek, and wiped it away quickly. Because of this, our period of time I thought about it for me. These are questions worth answering on lap 4 went well in that narrow value range. At first glance, the unique aspects of life and had to be the sunniest yet, but a swamp, with broad leaf petals and a greater psychic sense. Lining up at me and there was no noticeable effect. Their shouts were nothing to fear, and everything had such an adequate body. What have I learned last year that being the constructive light side.

My confusion was regarding exactly what they were staring back. It was my initiation into the air. This all happened I would see a torus with lights ascending and descending an entire glass. All three of our thoughts. The peak of the race. I returned to the yellow gate.

We stopped to sleep.

\end{document}
